### 2020-08-14 outline/outline.tex
Initial commit.  Includes readme and proposed paper outline.

\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{nosep}

\title{Introductory Physics Labs:  A Tale of Two Transformations}
\author{Steven F.\ Wolf, Mark W.\ Sprague}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
  A key problem facing physics departments, especially given the current global pandemic, is
  how can we engage students in our laboratory courses while maintaining appropriate social
  distancing and hygiene standards.  One solution to this problem is to move the labs to an
  online format.  But how can we engage our students in online labs with a curriculum that
  privileges science practices?  We have created an intro physics lab curriculum that engages
  students in science practices and are implementing it online.
\end{abstract}

\section{Introduction}
\textcolor{blue}{SFW mostly writes this.}

Here we set up the rationale behind our initial transformation.  I see this as two-fold:
\begin{enumerate}
  \item We hadn't updated our labs in decades, and they utilized outdated technology and
  pedagogies.
  \item We wanted to give students an opportunity to delve into science practices.
\end{enumerate}
We have been seeking institutional (SFW's Teaching Grant) and national (NSF Award \#) resources
to support our initial transformation.

Then we've got a pandemic which means online labs were an immediate default. However, a lack of
online labs is also a barrier for DE students' completion of a degree.  So online lab curricula
would fill an institutional need.

\section{Instructional Context}
\textcolor{blue}{SFW mostly writes this.}

We should also talk about the specific context of our labs:
\begin{itemize}
  \item Discuss institutional profile.
  \item Discuss student population in labs/lecture courses served.
  \item Compare course demographics with university demographics.
\end{itemize}

\section{Transformation \#1: Argument Driven Inquiry}
\textcolor{blue}{SFW mostly writes this.}

Brief lit review of ADI, including some of our prior work (PERC 2019 proceedings paper).
Describe the stages of ADI and how we implement them.

\section{Transformation \#2: Online Adaptation}
\textcolor{blue}{MWS mostly writes this.}

How did we adapt the ADI curriculum to online formats?
\begin{itemize}
  \item Stage 1: Finishing Spring 2020 semester online
  \item Stage 2: Fall 2020 and beyond - lab kits
\end{itemize}
Lab kit composition

\section{Conclusion}
\textcolor{blue}{SFW and MWS write this together.}

We did it, and you can too!  We should have a resources page/EPAPS for this paper.

\section{Notes, not part of outline}
Most TPT papers are \emph{short}---on the order of 2000 words.  For example the following two
papers are 3 and 4 pages respectively:
\begin{itemize}
  \item \url{https://doi.org/10.1119/1.5145407}
  \item \url{https://doi.org/10.1119/1.5145524}
\end{itemize}
So we don't need to kill ourselves on a long-form manuscript.  I think we can turn this around
in a month or two and get this out.

Also, while I could see having Joi read this and give us some feedback, I'm not sure she needs
to be an author.  But this isn't a hard and fast stance that I have, and am willing to discuss
with you.  More to the point, I'm not sure how much she needs this paper.

\end{document}

### 2020-08-17 OnlineLabsSection4.tex

\documentclass[aip, preprint, numerical]{revtex4-2}   	
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{url}

%SetFonts

%SetFonts

\begin{document}
\setcounter{section}{3}
\section{Transformation \#2: Online Adaptation}

\subsection{Sudden Transition to Online Instruction--Spring 2020}

In March 2020 the COVID 19 pandemic forced most universities, including East Carolina University, to move all their classes online. Our General Physics I and II laboratories had completed two out of four full investigations and the pre-lab for the third investigation face-to-face. We were forced to find a way to engage students in an online format while preserving the nature of the ADI laboratory experience. The face-to-face activities that we moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam online. We required student investigation groups to find a method for online collaboration in which everyone in the group could participate. Some groups used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a group chat, and others used FaceTime or other online communication applications.

During the first week of online classes each group produced a proposal and posted a proposal form on a Canvas group discussion page for approval. The TA reviewed proposals a provided feedback or approval. Groups used the TA feedback to revise their proposals until they were approved. Most proposals obtained approval after two or three revisions, but some required as many as seven revisions to obtain approval. The TAs and students found communication about proposals much more difficult online than in face-to-face classes.

Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period. Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring. For this investigation we provided videos of various masses oscillating on springs (100 oscillations for 10 different masses and the spring oscillating with no mass) and a photograph of each spring on a balance. We posted data sets for six different springs so groups in the same lab section would each have different springs to study.

Investigation 3 for the General Physics Laboratory II course was a study of diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter. We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to use as a length scale. We also provided photographs of the positions of the holder and screen on the optics bench. We gave the students a tutorial on using the ImageJ application\citep{schrasetal12} to measure distances in a photograph.

When the TA approved a group's  proposal, they assigned the group a data set for the investigation, and the group began its measurements and analysis. We provided measurements to the students in the most raw form possible to require them to make decisions about data collection and analysis. Each group was required to complete its analysis and create a three-slide presentation for the argumentation session the following week. The first slide was a description of their measurements. Te second slide was a presentation of the results, including a graph or table, and the third slide was their argument, based on their result.

The argumentation session was held in a Cisco WebEx session during the lab session the week after the proposal session. One member of each group gave the presentation, which  was followed by questions. Students received credit for giving presentations, asking meaningful questions, and responding to questions.  Following the argumentation session students submitted individual draft reports, peer-reviewed each other's drafts, and submitted final reports in the same manner used for the face-to-face investigations.

Investigation 4 in the General Physics Laboratory I course was about collisions, and students were asked to determine whether a collision between two marbles was elastic. Our original plans were to have the students video marble collisions in lab and analyze them using the Tracker application\citep{bro2009}. When the labs went online, we provided the students with several videos of marble collisions and asked the students to install Tracker on their computers for analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own computers. The originally-planned pre-lab was an analysis of a video using Tracker. This activity required only a few changes from the face-to-face pre-lab assignment. We conducted the proposal session as described for Investigation 3 and assigned each group one of six videos of colliding marbles to analyze along with mass measurements of the marbles in the videos. The argumentation session and the remainder of the investigation were conducted in the same manner as Investigation 3.

Investigation 4 in the General Physics Laboratory II course was a study of radioactive decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice in which the students roll several dice and remove all the dice with one dot showing. We wrote a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could perform the same activity using this simulation on their computers. For the investigation the students were asked to determine which isotope was most common in the nuclear decay of a copper disk that had been exposed to low-energy neutron radiation. We measured radiation counts for several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time in CSV files for analysis. As in the other course, the investigation was conducted in the same manner as Investigation 3.

Practical exams go in this paragraph!!!

We encountered many problems with the move to online laboratories. Our students had not selected an online class, and many were not prepared for the sudden transition from face-to-face to online classes. Many students could not or did not attend the online WebEx sessions or participate with their assigned groups. Some students had to get jobs when they returned home, and others did not have access to high-speed internet. We removed non-participating students from groups and gave them an opportunity to make up their missed work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups completed their work. We resorted to dropping the lowest investigation for the course.

Some students in the course did not have access to computers capable of running Tracker or ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices such as smartphones or tablets. We discovered jsTrack\citep{jstrack}, an online Javascript web application for video analysis that runs on most computers including Chromebooks. Students using mobile devices were not able to use jsTrack either.

\subsection{Fully Online Laboratories--Fall 2020}

\begin{table}
    \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020 block schedule.}
    \begin{ruledtabular}
        \begin{tabular}{ccp{28em}}
            Investigation & Topic & Guiding Question\\
            \hline
            1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
            2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
            3 & 2-D collisions & Is the collision between two marbles elastic?
        \end{tabular}
    \end{ruledtabular}
\end{table}

We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester in order to preserve the group class interaction aspects of ADI, which would be difficult under the social distancing requirements in place due to the pandemic.\citep{mclber20}  Also our teaching laboratories would have to operate at half capacity to maintain social distancing, preventing us from offering the courses to the necessary number of students.  In addition to the social distancing requirements for face-to-face class meetings, our university adopted an eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses are scheduled for the second block. Course mapping between the originally scheduled 14-week semester and the two eight-week blocks was based on the originally scheduled class meeting time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per week. We determined that even though there were enough lab meetings for the synchronous activities of four full investigations, there was not enough time between lab meetings for the asynchronous components and timely grading for four investigations. We reduced the number of investigations to three and added an additional pre-lab activity to each investigation. The topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall} for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics Laboratory II.

\begin{table}
    \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020 block schedule.}
    \begin{ruledtabular}
        \begin{tabular}{ccp{26em}}
            Investigation & Topic & Guiding Question\\
            \hline
            1 & Current and resistance & Does a light bulb behave like a resistor? \\
            2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
            3 & Diffraction of light & Are hairs from different people the same diameter?
        \end{tabular}
    \end{ruledtabular}
\end{table}

We informed the students before the course began that internet connectivity was required and that they must have access to a computer capable of running Tracker (General Physics Laboratory I) or ImageJ (General Physics Laboratory II). We also included these statements in the course syllabus. Although the courses were online, most of the students were on campus allowing them to access campus computer laboratories if they did on a computer that met the course requirements.

 \begin{table}
    \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
        \begin{tabular}{clc}
            \hline\hline
            Quantity & Item & Investigation(s)\\
            \hline
            1 & Protractor & 1 \\
            2 & \SI{25}{mm} marble & 1, 3 \\
            1 & Tape measure with cm scale & 1, 2, 3\\
            1 & \SI{0.6}{m} threded rod & 2 \\
            1 & Eye nut & 2 \\
            3 & Nuts & 2 \\
            1 & Door hook & 2 \\
            1 & \SI{1}{m} string & 2 \\
            1 & \SI{16}{mm} marble & 3 \\
            \hline\hline
        \end{tabular}
\end{table}

We developed lab kits with supplies that allowed the students to perform the investigations outside the teaching laboratory. We purchased the lab kit items in collaboration with our campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab kit items in bulk and where possible directly from manufacturers to reduce the costs of the items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II kit cost ???. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics Laboratory II.

 \begin{table}
    \caption{\label{tab: 1261 lab kit} General Physics Laboratory II lab kit contents.}
        \begin{tabular}{clc}
            \hline\hline
            Quantity & Item & Investigation(s)\\
            \hline
            1 & \SI{100}{\ohm} resistor & 1 \\
            1 & \SI{330}{\ohm} resistor & 1 \\
            1 &  \SI{100}{\ohm} potentiometer & 1 \\
            1 & E10 light bulb holder & 1 \\
            1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
            1 & Breadboard & 1, 2, 3 \\
            1 & Breadboard power supply & 1, 2, 3 \\
            1 & USB power supply cable & 1, 2, 3 \\
            1 & Jumper wire set & 1, 2 \\
            2 & Multimeters & 1, 2 \\
            1 & Mini screwdriver for multimeters & 1,2 \\
            5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
            4 & Alligator clip leads & 1, 2 \\
            1 & \SI{1}{\mega\ohm} resistor & 2 \\
            2 & \SI{100}{\micro\farad} capacitor & 2 \\
            1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
            1 & Tape measure with cm scale & 3 \\            
            \hline\hline
        \end{tabular}
\end{table}

\bibliography{onlinelabs.bib}
\end{document}

### 2020-08-18 manuscript/onlineLabPaper.tex
Updated manuscript with material from Mark.

--- 2020-08-14 outline/outline.tex
@@
-\documentclass{article}
+\documentclass[aip, numerical, preprint]{revtex4-2}
 
-\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage{siunitx}
+
 \usepackage[colorlinks=true]{hyperref}
@@
 
+\begin{document}
 \title{Introductory Physics Labs:  A Tale of Two Transformations}
-\author{Steven F.\ Wolf, Mark W.\ Sprague}
+
+\author{Steven F.\ Wolf}
+\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
+  street, Greenville, NC 27858 USA}
+\author{Mark W.\ Sprague}
+\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
+  street, Greenville, NC 27858 USA}
+
 \date{\today}
-
-\begin{document}
-\maketitle
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 \section{Transformation \#2: Online Adaptation}
-\textcolor{blue}{MWS mostly writes this.}
+\subsection{Sudden Transition to Online Instruction--Spring 2020}
 
-How did we adapt the ADI curriculum to online formats?
-\begin{itemize}
-  \item Stage 1: Finishing Spring 2020 semester online
-  \item Stage 2: Fall 2020 and beyond - lab kits
-\end{itemize}
-Lab kit composition
+In March 2020 the COVID 19 pandemic forced most universities, including East Carolina University, to move all their classes online.
+Our General Physics I and II laboratories had completed two out of four full investigations and the pre-lab for the third investigation face-to-face.
+We were forced to find a way to engage students in an online format while preserving the nature of the ADI laboratory experience.
+The face-to-face activities that we moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation.
+In addition, we gave our laboratory practical exam online.
+We required student investigation groups to find a method for online collaboration in which everyone in the group could participate.
+Some groups used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a group chat, and others used FaceTime or other online communication applications.
+
+During the first week of online classes each group produced a proposal and posted a proposal form on a Canvas group discussion page for approval.
+The TA reviewed proposals a provided feedback or approval.
+Groups used the TA feedback to revise their proposals until they were approved.
+Most proposals obtained approval after two or three revisions, but some required as many as seven revisions to obtain approval.
+The TAs and students found communication about proposals much more difficult online than in face-to-face classes.
+
+Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
+Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring.
+For this investigation we provided videos of various masses oscillating on springs (100 oscillations for 10 different masses and the spring oscillating with no mass) and a photograph of each spring on a balance.
+We posted data sets for six different springs so groups in the same lab section would each have different springs to study.
+
+Investigation 3 for the General Physics Laboratory II course was a study of diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
+We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs.
+Each photograph had a ruler at the bottom for the students to use as a length scale.
+We also provided photographs of the positions of the holder and screen on the optics bench.
+We gave the students a tutorial on using the ImageJ application\citep{schrasetal12} to measure distances in a photograph.
+
+When the TA approved a group's  proposal, they assigned the group a data set for the investigation, and the group began its measurements and analysis.
+We provided measurements to the students in the most raw form possible to require them to make decisions about data collection and analysis.
+Each group was required to complete its analysis and create a three-slide presentation for the argumentation session the following week.
+The first slide was a description of their measurements.
+Te second slide was a presentation of the results, including a graph or table, and the third slide was their argument, based on their result.
+
+The argumentation session was held in a Cisco WebEx session during the lab session the week after the proposal session.
+One member of each group gave the presentation, which  was followed by questions.
+Students received credit for giving presentations, asking meaningful questions, and responding to questions.
+Following the argumentation session students submitted individual draft reports, peer-reviewed each other's drafts, and submitted final reports in the same manner used for the face-to-face investigations.
+
+Investigation 4 in the General Physics Laboratory I course was about collisions, and students were asked to determine whether a collision between two marbles was elastic.
+Our original plans were to have the students video marble collisions in lab and analyze them using the Tracker application\citep{bro2009}.
+When the labs went online, we provided the students with several videos of marble collisions and asked the students to install Tracker on their computers for analysis.
+We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own computers.
+The originally-planned pre-lab was an analysis of a video using Tracker.
+This activity required only a few changes from the face-to-face pre-lab assignment.
+We conducted the proposal session as described for Investigation 3 and assigned each group one of six videos of colliding marbles to analyze along with mass measurements of the marbles in the videos.
+The argumentation session and the remainder of the investigation were conducted in the same manner as Investigation 3.
+
+Investigation 4 in the General Physics Laboratory II course was a study of radioactive decay.
+The pre-lab for the face-to-face course is a simulation of radioactive decay using dice in which the students roll several dice and remove all the dice with one dot showing.
+We wrote a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could perform the same activity using this simulation on their computers.
+For the investigation the students were asked to determine which isotope was most common in the nuclear decay of a copper disk that had been exposed to low-energy neutron radiation.
+We measured radiation counts for several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time in CSV files for analysis.
+As in the other course, the investigation was conducted in the same manner as Investigation 3.
+
+Practical exams go in this paragraph!!!
+
+We encountered many problems with the move to online laboratories.
+Our students had not selected an online class, and many were not prepared for the sudden transition from face-to-face to online classes.
+Many students could not or did not attend the online WebEx sessions or participate with their assigned groups.
+Some students had to get jobs when they returned home, and others did not have access to high-speed internet.
+We removed non-participating students from groups and gave them an opportunity to make up their missed work asynchronously.
+Less than \SI{50}{\percent} of the students in the make-up groups completed their work.
+We resorted to dropping the lowest investigation for the course.
+
+Some students in the course did not have access to computers capable of running Tracker or ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices such as smartphones or tablets.
+We discovered jsTrack\citep{jstrack}, an online Javascript web application for video analysis that runs on most computers including Chromebooks.
+Students using mobile devices were not able to use jsTrack either.
+
+\subsection{Fully Online Laboratories--Fall 2020}
+
+\begin{table}
+    \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020 block schedule.}
+    \begin{ruledtabular}
+        \begin{tabular}{ccp{28em}}
+            Investigation & Topic & Guiding Question\\
+            \hline
+            1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
+            2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
+            3 & 2-D collisions & Is the collision between two marbles elastic?
+        \end{tabular}
+    \end{ruledtabular}
+\end{table}
+
+We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester in order to preserve the group class interaction aspects of ADI, which would be difficult under the social distancing requirements in place due to the pandemic.\citep{mclber20}  Also our teaching laboratories would have to operate at half capacity to maintain social distancing, preventing us from offering the courses to the necessary number of students.
+In addition to the social distancing requirements for face-to-face class meetings, our university adopted an eight-week block schedule, with the second block ending before the Thanksgiving holiday.
+Half of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses are scheduled for the second block.
+Course mapping between the originally scheduled 14-week semester and the two eight-week blocks was based on the originally scheduled class meeting time.
+In the block schedule, the one semester-hour lab courses have two two-hour meetings per week.
+We determined that even though there were enough lab meetings for the synchronous activities of four full investigations, there was not enough time between lab meetings for the asynchronous components and timely grading for four investigations.
+We reduced the number of investigations to three and added an additional pre-lab activity to each investigation.
+The topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall} for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics Laboratory II.
+
+\begin{table}
+    \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020 block schedule.}
+    \begin{ruledtabular}
+        \begin{tabular}{ccp{26em}}
+            Investigation & Topic & Guiding Question\\
+            \hline
+            1 & Current and resistance & Does a light bulb behave like a resistor? \\
+            2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
+            3 & Diffraction of light & Are hairs from different people the same diameter?
+        \end{tabular}
+    \end{ruledtabular}
+\end{table}
+
+We informed the students before the course began that internet connectivity was required and that they must have access to a computer capable of running Tracker (General Physics Laboratory I) or ImageJ (General Physics Laboratory II).
+We also included these statements in the course syllabus.
+Although the courses were online, most of the students were on campus allowing them to access campus computer laboratories if they did on a computer that met the course requirements.
+
+ \begin{table}
+    \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
+        \begin{tabular}{clc}
+            \hline\hline
+            Quantity & Item & Investigation(s)\\
+            \hline
+            1 & Protractor & 1 \\
+            2 & \SI{25}{mm} marble & 1, 3 \\
+            1 & Tape measure with cm scale & 1, 2, 3\\
+            1 & \SI{0.6}{m} threded rod & 2 \\
+            1 & Eye nut & 2 \\
+            3 & Nuts & 2 \\
+            1 & Door hook & 2 \\
+            1 & \SI{1}{m} string & 2 \\
+            1 & \SI{16}{mm} marble & 3 \\
+            \hline\hline
+        \end{tabular}
+\end{table}
+
+We developed lab kits with supplies that allowed the students to perform the investigations outside the teaching laboratory.
+We purchased the lab kit items in collaboration with our campus bookstore, and the students purchased the lab kits from the bookstore.
+We ordered lab kit items in bulk and where possible directly from manufacturers to reduce the costs of the items.
+Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II kit cost ???.
+Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics Laboratory II.
+
+ \begin{table}
+    \caption{\label{tab: 1261 lab kit} General Physics Laboratory II lab kit contents.}
+        \begin{tabular}{clc}
+            \hline\hline
+            Quantity & Item & Investigation(s)\\
+            \hline
+            1 & \SI{100}{\ohm} resistor & 1 \\
+            1 & \SI{330}{\ohm} resistor & 1 \\
+            1 &  \SI{100}{\ohm} potentiometer & 1 \\
+            1 & E10 light bulb holder & 1 \\
+            1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
+            1 & Breadboard & 1, 2, 3 \\
+            1 & Breadboard power supply & 1, 2, 3 \\
+            1 & USB power supply cable & 1, 2, 3 \\
+            1 & Jumper wire set & 1, 2 \\
+            2 & Multimeters & 1, 2 \\
+            1 & Mini screwdriver for multimeters & 1,2 \\
+            5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
+            4 & Alligator clip leads & 1, 2 \\
+            1 & \SI{1}{\mega\ohm} resistor & 2 \\
+            2 & \SI{100}{\micro\farad} capacitor & 2 \\
+            1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
+            1 & Tape measure with cm scale & 3 \\            
+            \hline\hline
+        \end{tabular}
+\end{table}
 
@@
 
-\section{Notes, not part of outline}
-Most TPT papers are \emph{short}---on the order of 2000 words.  For example the following two
-papers are 3 and 4 pages respectively:
-\begin{itemize}
-  \item \url{https://doi.org/10.1119/1.5145407}
-  \item \url{https://doi.org/10.1119/1.5145524}
-\end{itemize}
-So we don't need to kill ourselves on a long-form manuscript.  I think we can turn this around
-in a month or two and get this out.
-
-Also, while I could see having Joi read this and give us some feedback, I'm not sure she needs
-to be an author.  But this isn't a hard and fast stance that I have, and am willing to discuss
-with you.  More to the point, I'm not sure how much she needs this paper.
+\bibliography{onlinelabs.bib}
 

### 2020-08-18 OnlineLabsSection4.tex

@@
 
-During the first week of online classes each group produced a proposal and posted a proposal form on a Canvas group discussion page for approval.
-The TA reviewed proposals a provided feedback or approval.
+During the first week of online classes each group produced their proposal and it on a Canvas Discussion in a proposal form for approval.
+The teaching assistant (TA) reviewed proposals and provided feedback or approval.
 Groups used the TA feedback to revise their proposals until they were approved.
@@
 
-Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
+Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
 Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring.
-For this investigation we provided videos of various masses oscillating on springs (100 oscillations for 10 different masses and the spring oscillating with no mass) and a photograph of each spring on a balance.
-We posted data sets for six different springs so groups in the same lab section would each have different springs to study.
+For this investigation we provided videos of various masses oscillating on springs (100 oscillations each for 10 different masses and for the spring oscillating with no mass) and photographs of each spring and each mass on a balance.
+We posted video and photograph sets for six different springs so groups in the same lab section would each have different springs to study.
 
-Investigation 3 for the General Physics Laboratory II course was a study of diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
+Investigation 3 for the General Physics Laboratory II course was a study of light diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
+Before the transition to online classes, the students had completed a pre-lab activity in which they determined the width of a single slit by measuring the diffraction pattern.
 We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs.

### 2020-08-18 manuscript/onlineLabPaper.tex
Updated introduction section for the draft.  Will work on next two sections tomorrow.  I will note that we are running a bit long and will either have to cut or re-work.  Including texcount info for completeness:
$ texcount onlineLabPaper.tex
File: onlineLabPaper.tex
Encoding: ascii
Words in text: 2095
Words in headers: 34
Words outside text (captions, etc.): 34
Number of headers: 9
Number of floats/tables/figures: 4
Number of math inlines: 0
Number of math displayed: 0
Subcounts:
  text+headers+captions (#headers/#floats/#inlines/#displayed)
  114+9+0 (2/0/0/0) _top_
  378+1+0 (1/0/0/0) Secti

@@
 
-\usepackage[colorlinks=true]{hyperref}
+\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue]{hyperref}
 \usepackage{xcolor}
@@
 
-\author{Steven F.\ Wolf}
-\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
-  street, Greenville, NC 27858 USA}
-\author{Mark W.\ Sprague}
+\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
+  5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
 \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
@@
   distancing and hygiene standards.  One solution to this problem is to move the labs to an
-  online format.  But how can we engage our students in online labs with a curriculum that
-  privileges science practices?  We have created an intro physics lab curriculum that engages
-  students in science practices and are implementing it online.
+  online format.  But how can we do this while \textit{also} engaging our students in online
+  labs with a curriculum that privileges science practices?  We have created an intro physics
+  lab curriculum that engages students in science practices and are implementing it online.
 \end{abstract}
@@
 \section{Introduction}
-\textcolor{blue}{SFW mostly writes this.}
+Scientific truth is discovered through the practice of doing science.  In fact, the National
+Research Council in it's report on Discipline Based Education Research (DBER) states, ``Without
+[scientific] investigative practices, there would be no new scientific and engineering
+knowledge.''\cite{DBERreport} However, too often, laboratory courses do not meaningfully engage
+students in scientific practices, instead reproducing classical experiments.\cite{PCAST12} This
+is part of a long-standing tradition of calling for authentic engagement in scientific
+practices which pre-dates Lorentz transformations.\cite{AAAS1881} Indeed, the AAAS stated our
+goals quite succinctly, ``[Typical courses in t]he sciences\ldots are not made the means of
+cultivating the observing powers, stimulating inquiry, exercising the judgment in weighing
+evidence, nor of forming independent habits of thought.''\cite{AAAS1881}
 
-Here we set up the rationale behind our initial transformation.  I see this as two-fold:
-\begin{enumerate}
-  \item We hadn't updated our labs in decades, and they utilized outdated technology and
-  pedagogies.
-  \item We wanted to give students an opportunity to delve into science practices.
-\end{enumerate}
-We have been seeking institutional (SFW's Teaching Grant) and national (NSF Award \#) resources
-to support our initial transformation.
+The situation at our home institution in the Fall of 2016 very much mirrored the national
+narrative.  The lab curriculum had been largely unchanged for about 20 years, and followed the
+traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
+outdated -- triple beam balances and hand-drawn graphs were standard.  In this same year, as
+part of an interdisciplinary team interested in engaging students in scientific practices as
+well as assessing those scientific practices, we secured funding, both internally and from the
+NSF, to change this status quo in physics, biology, and chemistry.  All three departments
+transformed their labs using a pedagogical framework entitled, Argument Driven Inquiry
+(ADI),\cite{Sampson2011,Walker2011,Walker2016} which has been specifically designed to engage
+students in authentic science practices. We will focus on the physics transformation in this
+paper.
 
-Then we've got a pandemic which means online labs were an immediate default. However, a lack of
-online labs is also a barrier for DE students' completion of a degree.  So online lab curricula
-would fill an institutional need.
+We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
+shut-down due to the global pandemic.  With students off campus, we had to abruptly shift our
+delivery to an online format, and quickly realized that some of the activities that we utilized
+in the face-to-face sections had to be adapted to online use.  Going forward, we've further
+adapted what we are doing so that students can still participate in a hands-on laboratory
+experience.  We hope these changes will be meaningful long-term as a lack of online labs is
+also a barrier for DE students' completion of a degree.  So online lab curricula would fill an
+institutional need.  In the next sections, we will discuss our institutional and instructional
+contexts and describe each transformation in more detail.
 
@@
 
-In March 2020 the COVID 19 pandemic forced most universities, including East Carolina University, to move all their classes online.
-Our General Physics I and II laboratories had completed two out of four full investigations and the pre-lab for the third investigation face-to-face.
-We were forced to find a way to engage students in an online format while preserving the nature of the ADI laboratory experience.
-The face-to-face activities that we moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation.
-In addition, we gave our laboratory practical exam online.
-We required student investigation groups to find a method for online collaboration in which everyone in the group could participate.
-Some groups used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a group chat, and others used FaceTime or other online communication applications.
+In March 2020 the COVID 19 pandemic forced most universities, including East Carolina
+University, to move all their classes online. Our General Physics I and II laboratories had
+completed two out of four full investigations and the pre-lab for the third investigation
+face-to-face. We were forced to find a way to engage students in an online format while
+preserving the nature of the ADI laboratory experience. The face-to-face activities that we
+moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4
+Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam
+online. We required student investigation groups to find a method for online collaboration in
+which everyone in the group could participate. Some groups used Cisco WebEx (video interaction
+platform licensed by our university) sessions, some used a group chat, and others used FaceTime
+or other online communication applications.
 
-During the first week of online classes each group produced a proposal and posted a proposal form on a Canvas group discussion page for approval.
-The TA reviewed proposals a provided feedback or approval.
-Groups used the TA feedback to revise their proposals until they were approved.
-Most proposals obtained approval after two or three revisions, but some required as many as seven revisions to obtain approval.
-The TAs and students found communication about proposals much more difficult online than in face-to-face classes.
+During the first week of online classes each group produced a proposal and posted a proposal
+form on a Canvas group discussion page for approval. The TA reviewed proposals a provided
+feedback or approval. Groups used the TA feedback to revise their proposals until they were
+approved. Most proposals obtained approval after two or three revisions, but some required as
+many as seven revisions to obtain approval. The TAs and students found communication about
+proposals much more difficult online than in face-to-face classes.
 
-Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
-Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring.
-For this investigation we provided videos of various masses oscillating on springs (100 oscillations for 10 different masses and the spring oscillating with no mass) and a photograph of each spring on a balance.
-We posted data sets for six different springs so groups in the same lab section would each have different springs to study.
+Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass
+hanging from a spring in which the students were asked to determine when the spring's mass must
+be considered as a contribution to the period. Before the transition to online classes the
+students had completed a pre-lab activity in which they measured the period of a mass on a
+spring. For this investigation we provided videos of various masses oscillating on springs (100
+oscillations for 10 different masses and the spring oscillating with no mass) and a photograph
+of each spring on a balance. We posted data sets for six different springs so groups in the
+same lab section would each have different springs to study.
 
-Investigation 3 for the General Physics Laboratory II course was a study of diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
-We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs.
-Each photograph had a ruler at the bottom for the students to use as a length scale.
-We also provided photographs of the positions of the holder and screen on the optics bench.
-We gave the students a tutorial on using the ImageJ application\citep{schrasetal12} to measure distances in a photograph.
+Investigation 3 for the General Physics Laboratory II course was a study of diffraction in
+which the students were asked to determine whether hairs from two individuals had the same
+diameter. We collected hair samples from several people and posted photographs of the
+diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
+use as a length scale. We also provided photographs of the positions of the holder and screen
+on the optics bench. We gave the students a tutorial on using the ImageJ
+application\citep{schrasetal12} to measure distances in a photograph.
 
-When the TA approved a group's  proposal, they assigned the group a data set for the investigation, and the group began its measurements and analysis.
-We provided measurements to the students in the most raw form possible to require them to make decisions about data collection and analysis.
-Each group was required to complete its analysis and create a three-slide presentation for the argumentation session the following week.
-The first slide was a description of their measurements.
-Te second slide was a presentation of the results, including a graph or table, and the third slide was their argument, based on their result.
+When the TA approved a group's proposal, they assigned the group a data set for the
+investigation, and the group began its measurements and analysis. We provided measurements to
+the students in the most raw form possible to require them to make decisions about data
+collection and analysis. Each group was required to complete its analysis and create a
+three-slide presentation for the argumentation session the following week. The first slide was
+a description of their measurements. Te second slide was a presentation of the results,
+including a graph or table, and the third slide was their argument, based on their result.
 
-The argumentation session was held in a Cisco WebEx session during the lab session the week after the proposal session.
-One member of each group gave the presentation, which  was followed by questions.
-Students received credit for giving presentations, asking meaningful questions, and responding to questions.
-Following the argumentation session students submitted individual draft reports, peer-reviewed each other's drafts, and submitted final reports in the same manner used for the face-to-face investigations.
+The argumentation session was held in a Cisco WebEx session during the lab session the week
+after the proposal session. One member of each group gave the presentation, which was followed
+by questions. Students received credit for giving presentations, asking meaningful questions,
+and responding to questions.  Following the argumentation session students submitted individual
+draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
+manner used for the face-to-face investigations.
 
-Investigation 4 in the General Physics Laboratory I course was about collisions, and students were asked to determine whether a collision between two marbles was elastic.
-Our original plans were to have the students video marble collisions in lab and analyze them using the Tracker application\citep{bro2009}.
-When the labs went online, we provided the students with several videos of marble collisions and asked the students to install Tracker on their computers for analysis.
-We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own computers.
-The originally-planned pre-lab was an analysis of a video using Tracker.
-This activity required only a few changes from the face-to-face pre-lab assignment.
-We conducted the proposal session as described for Investigation 3 and assigned each group one of six videos of colliding marbles to analyze along with mass measurements of the marbles in the videos.
-The argumentation session and the remainder of the investigation were conducted in the same manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory I course was about collisions, and students
+were asked to determine whether a collision between two marbles was elastic. Our original plans
+were to have the students video marble collisions in lab and analyze them using the Tracker
+application\citep{bro2009}. When the labs went online, we provided the students with several
+videos of marble collisions and asked the students to install Tracker on their computers for
+analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
+their own computers. The originally-planned pre-lab was an analysis of a video using
+Tracker. This activity required only a few changes from the face-to-face pre-lab assignment. We
+conducted the proposal session as described for Investigation 3 and assigned each group one of
+six videos of colliding marbles to analyze along with mass measurements of the marbles in the
+videos. The argumentation session and the remainder of the investigation were conducted in the
+same manner as Investigation 3.
 
-Investigation 4 in the General Physics Laboratory II course was a study of radioactive decay.
-The pre-lab for the face-to-face course is a simulation of radioactive decay using dice in which the students roll several dice and remove all the dice with one dot showing.
-We wrote a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could perform the same activity using this simulation on their computers.
-For the investigation the students were asked to determine which isotope was most common in the nuclear decay of a copper disk that had been exposed to low-energy neutron radiation.
-We measured radiation counts for several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time in CSV files for analysis.
-As in the other course, the investigation was conducted in the same manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory II course was a study of radioactive
+decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
+in which the students roll several dice and remove all the dice with one dot showing. We wrote
+a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
+perform the same activity using this simulation on their computers. For the investigation the
+students were asked to determine which isotope was most common in the nuclear decay of a copper
+disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
+several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
+in CSV files for analysis. As in the other course, the investigation was conducted in the same
+manner as Investigation 3.
 
@@
 
-We encountered many problems with the move to online laboratories.
-Our students had not selected an online class, and many were not prepared for the sudden transition from face-to-face to online classes.
-Many students could not or did not attend the online WebEx sessions or participate with their assigned groups.
-Some students had to get jobs when they returned home, and others did not have access to high-speed internet.
-We removed non-participating students from groups and gave them an opportunity to make up their missed work asynchronously.
-Less than \SI{50}{\percent} of the students in the make-up groups completed their work.
-We resorted to dropping the lowest investigation for the course.
+We encountered many problems with the move to online laboratories. Our students had not
+selected an online class, and many were not prepared for the sudden transition from
+face-to-face to online classes. Many students could not or did not attend the online WebEx
+sessions or participate with their assigned groups. Some students had to get jobs when they
+returned home, and others did not have access to high-speed internet. We removed
+non-participating students from groups and gave them an opportunity to make up their missed
+work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
+completed their work. We resorted to dropping the lowest investigation for the course.
 
-Some students in the course did not have access to computers capable of running Tracker or ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices such as smartphones or tablets.
-We discovered jsTrack\citep{jstrack}, an online Javascript web application for video analysis that runs on most computers including Chromebooks.
-Students using mobile devices were not able to use jsTrack either.
+Some students in the course did not have access to computers capable of running Tracker or
+ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
+mobile devices such as smartphones or tablets. We discovered jsTrack\citep{jstrack}, an online
+Javascript web application for video analysis that runs on most computers including
+Chromebooks. Students using mobile devices were not able to use jsTrack either.
 
@@
 \begin{table}
-    \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020 block schedule.}
+  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
+    block schedule.}
   \begin{ruledtabular}
@@
 
-We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester in order to preserve the group class interaction aspects of ADI, which would be difficult under the social distancing requirements in place due to the pandemic.\citep{mclber20}  Also our teaching laboratories would have to operate at half capacity to maintain social distancing, preventing us from offering the courses to the necessary number of students.
-In addition to the social distancing requirements for face-to-face class meetings, our university adopted an eight-week block schedule, with the second block ending before the Thanksgiving holiday.
-Half of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses are scheduled for the second block.
-Course mapping between the originally scheduled 14-week semester and the two eight-week blocks was based on the originally scheduled class meeting time.
-In the block schedule, the one semester-hour lab courses have two two-hour meetings per week.
-We determined that even though there were enough lab meetings for the synchronous activities of four full investigations, there was not enough time between lab meetings for the asynchronous components and timely grading for four investigations.
-We reduced the number of investigations to three and added an additional pre-lab activity to each investigation.
-The topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall} for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics Laboratory II.
+We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester
+in order to preserve the group class interaction aspects of ADI, which would be difficult under
+the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
+teaching laboratories would have to operate at half capacity to maintain social distancing,
+preventing us from offering the courses to the necessary number of students.  In addition to
+the social distancing requirements for face-to-face class meetings, our university adopted an
+eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half
+of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses
+are scheduled for the second block. Course mapping between the originally scheduled 14-week
+semester and the two eight-week blocks was based on the originally scheduled class meeting
+time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per
+week. We determined that even though there were enough lab meetings for the synchronous
+activities of four full investigations, there was not enough time between lab meetings for the
+asynchronous components and timely grading for four investigations. We reduced the number of
+investigations to three and added an additional pre-lab activity to each investigation. The
+topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall}
+for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics
+Laboratory II.
 
 \begin{table}
-    \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020 block schedule.}
+  \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020
+    block schedule.}
   \begin{ruledtabular}
@@
 
-We informed the students before the course began that internet connectivity was required and that they must have access to a computer capable of running Tracker (General Physics Laboratory I) or ImageJ (General Physics Laboratory II).
-We also included these statements in the course syllabus.
-Although the courses were online, most of the students were on campus allowing them to access campus computer laboratories if they did on a computer that met the course requirements.
+We informed the students before the course began that internet connectivity was required and
+that they must have access to a computer capable of running Tracker (General Physics Laboratory
+I) or ImageJ (General Physics Laboratory II). We also included these statements in the course
+syllabus. Although the courses were online, most of the students were on campus allowing them
+to access campus computer laboratories if they did on a computer that met the course
+requirements.
 
@@
 
-We developed lab kits with supplies that allowed the students to perform the investigations outside the teaching laboratory.
-We purchased the lab kit items in collaboration with our campus bookstore, and the students purchased the lab kits from the bookstore.
-We ordered lab kit items in bulk and where possible directly from manufacturers to reduce the costs of the items.
-Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II kit cost ???.
-Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics Laboratory II.
+We developed lab kits with supplies that allowed the students to perform the investigations
+outside the teaching laboratory. We purchased the lab kit items in collaboration with our
+campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
+kit items in bulk and where possible directly from manufacturers to reduce the costs of the
+items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II
+kit cost ???. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
+Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics
+Laboratory II.
 
@@
 
+\begin{acknowledgments}
+  Redacted for review.% This work has been supported by the NSF (Award \# 1725655).
+\end{acknowledgments}
+
 \bibliography{onlinelabs.bib}

### 2020-08-18 manuscript/onlineLabPaper.tex
Moved all section 4 material into manuscript and added info about practical exam to MS.

@@
 
-\section{Transformation \#1: Argument Driven Inquiry}
-\textcolor{blue}{SFW mostly writes this.}
+\section{Transformation \#2: Online Adaptation}
 
-Brief lit review of ADI, including some of our prior work (PERC 2019 proceedings paper).
-Describe the stages of ADI and how we implement them.
-
-\section{Transformation \#2: Online Adaptation}
 \subsection{Sudden Transition to Online Instruction--Spring 2020}
 
-In March 2020 the COVID 19 pandemic forced most universities, including East Carolina
-University, to move all their classes online. Our General Physics I and II laboratories had
-completed two out of four full investigations and the pre-lab for the third investigation
-face-to-face. We were forced to find a way to engage students in an online format while
-preserving the nature of the ADI laboratory experience. The face-to-face activities that we
-moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4
-Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam
-online. We required student investigation groups to find a method for online collaboration in
-which everyone in the group could participate. Some groups used Cisco WebEx (video interaction
-platform licensed by our university) sessions, some used a group chat, and others used FaceTime
-or other online communication applications.
+In March 2020 the COVID 19 pandemic forced most universities, including East Carolina University, to move all their classes online.
+Our General Physics I and II laboratories had completed two out of four full investigations and the pre-lab for the third investigation face-to-face.
+We were forced to find a way to engage students in an online format while preserving the nature of the ADI laboratory experience.
+The face-to-face activities that we moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation.
+In addition, we gave our laboratory practical exam online.
+We required student investigation groups to find a method for online collaboration in which everyone in the group could participate.
+Some groups used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a group chat, and others used FaceTime or other online communication applications.
 
-During the first week of online classes each group produced a proposal and posted a proposal
-form on a Canvas group discussion page for approval. The TA reviewed proposals a provided
-feedback or approval. Groups used the TA feedback to revise their proposals until they were
-approved. Most proposals obtained approval after two or three revisions, but some required as
-many as seven revisions to obtain approval. The TAs and students found communication about
-proposals much more difficult online than in face-to-face classes.
+During the first week of online classes each group produced their proposal and it on a Canvas Discussion in a proposal form for approval.
+The teaching assistant (TA) reviewed proposals and provided feedback or approval.
+Groups used the TA feedback to revise their proposals until they were approved.
+Most proposals obtained approval after two or three revisions, but some required as many as seven revisions to obtain approval.
+The TAs and students found communication about proposals much more difficult online than in face-to-face classes.
 
-Investigation 3 in the General Physics Laboratory I course was a study of the period of a mass
-hanging from a spring in which the students were asked to determine when the spring's mass must
-be considered as a contribution to the period. Before the transition to online classes the
-students had completed a pre-lab activity in which they measured the period of a mass on a
-spring. For this investigation we provided videos of various masses oscillating on springs (100
-oscillations for 10 different masses and the spring oscillating with no mass) and a photograph
-of each spring on a balance. We posted data sets for six different springs so groups in the
-same lab section would each have different springs to study.
+Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
+Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring.
+For this investigation we provided videos of various masses oscillating on springs (100 oscillations each for 10 different masses and for the spring oscillating with no mass) and photographs of each spring and each mass on a balance.
+We posted video and photograph sets for six different springs so groups in the same lab section would each have different springs to study.
 
-Investigation 3 for the General Physics Laboratory II course was a study of diffraction in
-which the students were asked to determine whether hairs from two individuals had the same
-diameter. We collected hair samples from several people and posted photographs of the
-diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
-use as a length scale. We also provided photographs of the positions of the holder and screen
-on the optics bench. We gave the students a tutorial on using the ImageJ
-application\citep{schrasetal12} to measure distances in a photograph.
+Investigation 3 for the General Physics Laboratory II course was a study of light diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
+Before the transition to online classes, the students had completed a pre-lab activity in which they determined the width of a single slit by measuring the diffraction pattern.
+We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs.
+Each photograph had a ruler at the bottom for the students to use as a length scale.
+We also provided photographs of the positions of the holder and screen on the optics bench.
+We gave the students a tutorial on using the ImageJ application\citep{schrasetal12} to measure distances in a photograph.
 
-When the TA approved a group's proposal, they assigned the group a data set for the
-investigation, and the group began its measurements and analysis. We provided measurements to
-the students in the most raw form possible to require them to make decisions about data
-collection and analysis. Each group was required to complete its analysis and create a
-three-slide presentation for the argumentation session the following week. The first slide was
-a description of their measurements. Te second slide was a presentation of the results,
-including a graph or table, and the third slide was their argument, based on their result.
+When the TA approved a group's  proposal, they assigned the group a data set for the investigation, and the group began its measurements and analysis.
+We provided measurements to the students in the most raw form possible to require them to make decisions about data collection and analysis.
+Each group was required to complete its analysis and create a three-slide presentation for the argumentation session the following week.
+The first slide was a description of their measurements.
+Te second slide was a presentation of the results, including a graph or table, and the third slide was their argument, based on their result.
 
-The argumentation session was held in a Cisco WebEx session during the lab session the week
-after the proposal session. One member of each group gave the presentation, which was followed
-by questions. Students received credit for giving presentations, asking meaningful questions,
-and responding to questions.  Following the argumentation session students submitted individual
-draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
-manner used for the face-to-face investigations.
+The argumentation session was held in a Cisco WebEx session during the lab session the week after the proposal session.
+One member of each group gave the presentation, which  was followed by questions.
+Students received credit for giving presentations, asking meaningful questions, and responding to questions.
+Following the argumentation session students submitted individual draft reports, peer-reviewed each other's drafts, and submitted final reports in the same manner used for the face-to-face investigations.
 
-Investigation 4 in the General Physics Laboratory I course was about collisions, and students
-were asked to determine whether a collision between two marbles was elastic. Our original plans
-were to have the students video marble collisions in lab and analyze them using the Tracker
-application\citep{bro2009}. When the labs went online, we provided the students with several
-videos of marble collisions and asked the students to install Tracker on their computers for
-analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
-their own computers. The originally-planned pre-lab was an analysis of a video using
-Tracker. This activity required only a few changes from the face-to-face pre-lab assignment. We
-conducted the proposal session as described for Investigation 3 and assigned each group one of
-six videos of colliding marbles to analyze along with mass measurements of the marbles in the
-videos. The argumentation session and the remainder of the investigation were conducted in the
-same manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory I course was about collisions, and students were asked to determine whether a collision between two marbles was elastic.
+Our original plans were to have the students video marble collisions in lab and analyze them using the Tracker application\citep{bro2009}.
+When the labs went online, we provided the students with several videos of marble collisions and asked the students to install Tracker on their computers for analysis.
+We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own computers.
+The originally-planned pre-lab was an analysis of a video using Tracker.
+This activity required only a few changes from the face-to-face pre-lab assignment.
+We conducted the proposal session as described for Investigation 3 and assigned each group one of six videos of colliding marbles to analyze along with mass measurements of the marbles in the videos.
+The argumentation session and the remainder of the investigation were conducted in the same manner as Investigation 3.
 
-Investigation 4 in the General Physics Laboratory II course was a study of radioactive
-decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
-in which the students roll several dice and remove all the dice with one dot showing. We wrote
-a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
-perform the same activity using this simulation on their computers. For the investigation the
-students were asked to determine which isotope was most common in the nuclear decay of a copper
-disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
-several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
-in CSV files for analysis. As in the other course, the investigation was conducted in the same
-manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory II course was a study of radioactive decay.
+The pre-lab for the face-to-face course is a simulation of radioactive decay using dice in which the students roll several dice and remove all the dice with one dot showing.
+We wrote a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could perform the same activity using this simulation on their computers.
+For the investigation the students were asked to determine which isotope was most common in the nuclear decay of a copper disk that had been exposed to low-energy neutron radiation.
+We measured radiation counts for several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time in CSV files for analysis.
+As in the other course, the investigation was conducted in the same manner as Investigation 3.
 
-Practical exams go in this paragraph!!!
+We administered the lab practical exams for both courses in Canvas using GlowScript simulations embedded in Canvas assignments.
+Students made measurements on the simulation and used their results to make an argument answering a guiding question.
 
-We encountered many problems with the move to online laboratories. Our students had not
-selected an online class, and many were not prepared for the sudden transition from
-face-to-face to online classes. Many students could not or did not attend the online WebEx
-sessions or participate with their assigned groups. Some students had to get jobs when they
-returned home, and others did not have access to high-speed internet. We removed
-non-participating students from groups and gave them an opportunity to make up their missed
-work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
-completed their work. We resorted to dropping the lowest investigation for the course.
+We encountered many problems with the move to online laboratories.
+Our students had not selected an online class, and many were not prepared for the sudden transition from face-to-face to online classes.
+Many students could not or did not attend the online WebEx sessions or participate with their assigned groups.
+Some students had to get jobs when they returned home, and others did not have access to high-speed internet.
+We removed non-participating students from groups and gave them an opportunity to make up their missed work asynchronously.
+Less than \SI{50}{\percent} of the students in the make-up groups completed their work.
+We resorted to dropping the lowest investigation for the course.
 
-Some students in the course did not have access to computers capable of running Tracker or
-ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
-mobile devices such as smartphones or tablets. We discovered jsTrack\citep{jstrack}, an online
-Javascript web application for video analysis that runs on most computers including
-Chromebooks. Students using mobile devices were not able to use jsTrack either.
+Some students in the course did not have access to computers capable of running Tracker or ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices such as smartphones or tablets.
+We discovered jsTrack\citep{jstrack}, an online Javascript web application for video analysis that runs on most computers including Chromebooks.
+Students using mobile devices were not able to use jsTrack either.
 
@@
 \begin{table}
-  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
-    block schedule.}
+    \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020 block schedule.}
     \begin{ruledtabular}
@@
 
-We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester
-in order to preserve the group class interaction aspects of ADI, which would be difficult under
-the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
-teaching laboratories would have to operate at half capacity to maintain social distancing,
-preventing us from offering the courses to the necessary number of students.  In addition to
-the social distancing requirements for face-to-face class meetings, our university adopted an
-eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half
-of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses
-are scheduled for the second block. Course mapping between the originally scheduled 14-week
-semester and the two eight-week blocks was based on the originally scheduled class meeting
-time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per
-week. We determined that even though there were enough lab meetings for the synchronous
-activities of four full investigations, there was not enough time between lab meetings for the
-asynchronous components and timely grading for four investigations. We reduced the number of
-investigations to three and added an additional pre-lab activity to each investigation. The
-topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall}
-for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics
-Laboratory II.
+We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester in order to preserve the group class interaction aspects of ADI, which would be difficult under the social distancing requirements in place due to the pandemic.\citep{mclber20}  Also our teaching laboratories would have to operate at half capacity to maintain social distancing, preventing us from offering the courses to the necessary number of students.
+In addition to the social distancing requirements for face-to-face class meetings, our university adopted an eight-week block schedule, with the second block ending before the Thanksgiving holiday.
+Half of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses are scheduled for the second block.
+Course mapping between the originally scheduled 14-week semester and the two eight-week blocks was based on the originally scheduled class meeting time.
+In the block schedule, the one semester-hour lab courses have two two-hour meetings per week.
+We determined that even though there were enough lab meetings for the synchronous activities of four full investigations, there was not enough time between lab meetings for the asynchronous components and timely grading for four investigations.
+We reduced the number of investigations to three and added an additional pre-lab activity to each investigation.
+The topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall} for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics Laboratory II.
 
 \begin{table}
-  \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020
-    block schedule.}
+    \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020 block schedule.}
     \begin{ruledtabular}
@@
 
-We informed the students before the course began that internet connectivity was required and
-that they must have access to a computer capable of running Tracker (General Physics Laboratory
-I) or ImageJ (General Physics Laboratory II). We also included these statements in the course
-syllabus. Although the courses were online, most of the students were on campus allowing them
-to access campus computer laboratories if they did on a computer that met the course
-requirements.
+We informed the students before the course began that internet connectivity was required and that they must have access to a computer capable of running Tracker (General Physics Laboratory I) or ImageJ (General Physics Laboratory II).
+We also included these statements in the course syllabus.
+Although the courses were online, most of the students were on campus allowing them to access campus computer laboratories if they did on a computer that met the course requirements.
 
@@
 
-We developed lab kits with supplies that allowed the students to perform the investigations
-outside the teaching laboratory. We purchased the lab kit items in collaboration with our
-campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
-kit items in bulk and where possible directly from manufacturers to reduce the costs of the
-items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II
-kit cost ???. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
-Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics
-Laboratory II.
+We developed lab kits with supplies that allowed the students to perform the investigations outside the teaching laboratory.
+We purchased the lab kit items in collaboration with our campus bookstore, and the students purchased the lab kits from the bookstore.
+We ordered lab kit items in bulk and where possible directly from manufacturers to reduce the costs of the items.
+Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II kit cost ???.
+Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics Laboratory II.
 

### 2020-08-25 manuscript/onlineLabPaper.tex
Recovered section 3, which was inadvertently deleted.
Updated draft with Instructional context and pedagogical changes.  Ready for meeting.  We aren't massively over on word count... $ texcount onlineLabPaper.tex File: onlineLabPaper.tex Encoding: ascii Words in text: 3371 Words in headers: 50 Words outside text (captions, etc.): 73 Number of headers: 12 Number of floats/tables/figures: 5 Number of math inlines: 2 Number of math displayed: 0 Subcounts:   text+headers+captions (#headers/#floats/#inlines/#displayed)   88+9+0 (2/0/0/0) _top_   378+1+0 (1/0/0/0) Section: Introduction   366+2+39 (1

@@
 
-\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
-  5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
-\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
-  street, Greenville, NC 27858 USA}
+% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
+% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
+% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
+% street, Greenville, NC 27858 USA}
+
+\author{First Author} \affiliation{Masked Institution} \author{Second Author}
+\affiliation{Masked Institution}
 
@@
 \section{Instructional Context}
-\textcolor{blue}{SFW mostly writes this.}
+\textcolor{red}{This section needs to have the institution masked before we send it in.}
 
-We should also talk about the specific context of our labs:
+East Carolina University is a regional master's university in a rural, economically depressed
+part of our state.  The university mission is focused on regional transformation and service to
+this region.  The total student population in Fall 2019 was 23k.  Our physics labs (Physics 1
+lab and Physics 2 lab) are each 1 credit courses that meet for 2 hours per week. These courses
+serve both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$
+of the students who take our lab course are in (or have taken) the Algebra-based physics
+lecture course. It also fulfills the general education requirement for science lab courses at
+our university.  Table \ref{tab:gender} compares the gender of students in these lab courses
+compared to the university population.  We note that the gender distribution of students in the
+Physics 2 lab generally matches the university population, while the Physics 1 lab skews more
+heavily male than the university population.  We also compare the race of students in these
+contexts in Table \textcolor{red}{not ready yet}\ldots
+
+Students who take these labs are most often science majors, especially in the health sciences
+(e.g., Biology, Exercise Science), but this lab is also taken by our majors.  In Fall 2019 we
+had 409 students in the Physics 1 lab, and in Spring 2020 (at Census Day, before the pandemic
+changed enrollments) we had 256 students in the Physics 2 lab.  In both labs, our enrollment is
+capped at 22 students, due to the constraints of our laboratory classroom.
+
+Labs are supervised by MWS, but each section is run by Graduate TAs (GTAs). The transformed
+curriculum was jointly written by both of the authors.  TA training was greatly enhanced when
+the new lab curriculum was put in place.  SFW and MWS, along with colleagues in Biology and
+Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics as these
+disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
+meeting with the TAs, and SFW and the research team have supervised various aspects of the
+transformation especially important for research such as curricular implementation \cite{AL's
+  paper} and assessment practices \cite{Wolf2019}.
+
+\begin{table}
+  \centering
+  \begin{tabular}{l|ll|l}
+    \hline \hline							
+    &	\multicolumn{2}{c|}{Course}\\
+    Gender	&	Physics 1	&	Physics 2	&	University	\\ \hline
+    Female	&	41.8\%	&	60.9\%	&	57.1\%	\\
+    Male	&	58.2\%	&	39.1\%	&	42.9\%	\\
+    \hline \hline							
+  \end{tabular}
+  \caption{Gender breakdown of students in the Fall 2019 of the Physics 1 lab, the Spring 2020
+    Physics 1 lab, and the undergraduate poplulation of the university at large in Fall 2019.
+    Note: The university only collected binary gender data }
+  \label{tab:gender}
+\end{table}
+
+\section{Transformation \#1: Argument Driven Inquiry}
+Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
+in school better match what actually transpires in authentic research settings
+\cite{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to answer
+questions, or measure quantities, that are well-known using procedures that have been refined
+over time.  For example, in physics we often have students measure $g$ using a well-known
+method (such as a spark timer).  In ADI labs, we give students a question to answer (e.g.,
+``Does the force a fan exerts on a cart depend on the mass of the cart?''), allow them to
+design a procedure for an experiment that will answer that question, collect and analyze their
+data, and make claims based on their data.  We accomplish this by having students engage in a
+three-part cycle:
 \begin{itemize}
-  \item Discuss institutional profile.
-  \item Discuss student population in labs/lecture courses served.
-  \item Compare course demographics with university demographics.
+  \item Pre-Lab - Introducing the context
+  \item Proposal Development and Data Collection
+  \item Argumentation and Peer Review
 \end{itemize}
+In the sections below, we will comment on each part of the cycle, focusing on both students and
+GTAs.
+
+\subsection{Week 1: Pre-Lab}
+Part of the goal of any laboratory is to help students develop a familiarity with certain tools
+and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
+students familiarity with the equipment they will be using.  For the investigation that I
+described previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''
+we need students to become familiar with a few things, such as what we mean by a cart, and give
+them some tools that they need to be able to answer this question.  As a part of the pre-lab
+reading, students are given reading about linear regression---both how to run it in Excel, and
+how to interpret the output, and how we can estimate instantaneous velocity given position
+vs. time data. For this experiment, we give them a cart (leaving the fan off for now) and have
+them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
+collect position vs.\ time data for this motion.  Students work in pairs to do this work, and
+turn in a brief summary of this work on the course management system.  For this investigation,
+it is the first time that they create graphs, so we set norms for graphing such as helping them
+decide which variable to put on the x-axis and the y-axis as well as including units.  Pre-lab
+assignments are designed to be graded in less than 1 minute/paper based on a rubric we provide
+to both students and GTAs.
+
+\subsection{Week 2: Proposal Development and Data Collection}
+During this week, students work in groups of 4 to develop a proposal, get it approved by a GTA,
+and then collect and analyze their data.  We have a format for proposal development that asks
+students to link the scientific concept being studied---in this example case, Newton's Second
+Law---to the data that they will collect.  Students also need to propose a plan for analyzing
+their data and minimizing potential sources of error (such as friction).  Once students have an
+approved proposal, they begin collecting and analyzing their data.  This may lead them to
+refine or revise their method (which they are encouraged to do).  Grading for the GTAs this
+week is minimal (full credit for completing the proposal).  However, this is the most critical
+week's for GTA training.  GTAs have to be clear that the goal is to allow a diverse number of
+ways of collecting/analyzing this data.  How much does the mass of the cart need to vary?  How
+many different cart masses do the students need to take?  How should students deal with
+friction? All of these are questions that we want the \textit{students} to answer.  And in some
+sense, we will be disappointed if all of the students come up with the same answer.
+Experimental methods certainly have an impact on experimental results.
+
+\subsection{Week 3: Argumentation and Peer Review}
+During this week, the students begin by sharing their results.  Students finish analyzing their
+data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from the
+group stays at the whiteboard while the other group members (travelers) go to other groups.
+The travelers learn what other groups did, and compare to their results in a structured
+argumentation setting.  Groups spend about 3-5 minutes at a poster, and rotate so that they see
+at least 3 other posters.  After the travelers return, critically, the groups spend time
+discussing what they saw and reflecting on their own results.  What is exciting is that
+sometimes, these interactions actually drive groups to change their claims \cite{Walker2019}.
+
+Students write a shortened lab report consisting of three sections: An introduction to the
+scientific concept, a description of the experimental method or procedure, and a discussion
+section laying out their results, and the evidence and justification supporting their results. 
+The authors have created different peer review calibration videos for the students to watch, so
+that they can look for the same things that we are going to be grading them on when we get
+their final reports.  Students complete their lab report and turn it in by the end of the day.
+Then, students take part in double-confidential peer review.  We facilitate this online.  They
+read and reply to two different lab reports.  Finally, they get their feedback and use this to
+revise their own lab report.  At the end of this week, students turn in their revised,
+peer-reviewed final lab report.  This is the heaviest week of GTA grading.  We provide a rubric
+for lab report grading, and each lab report generally takes about 3-5 minutes to grade.
 
@@
 
-In March 2020 the COVID 19 pandemic forced most universities, including East Carolina University, to move all their classes online.
-Our General Physics I and II laboratories had completed two out of four full investigations and the pre-lab for the third investigation face-to-face.
-We were forced to find a way to engage students in an online format while preserving the nature of the ADI laboratory experience.
-The face-to-face activities that we moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation.
-In addition, we gave our laboratory practical exam online.
-We required student investigation groups to find a method for online collaboration in which everyone in the group could participate.
-Some groups used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a group chat, and others used FaceTime or other online communication applications.
+In March 2020 the COVID 19 pandemic forced most universities, including East Carolina
+University, to move all their classes online. Our General Physics I and II laboratories had
+completed two out of four full investigations and the pre-lab for the third investigation
+face-to-face. We were forced to find a way to engage students in an online format while
+preserving the nature of the ADI laboratory experience. The face-to-face activities that we
+moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4
+Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam
+online. We required student investigation groups to find a method for online collaboration in
+which everyone in the group could participate. Some groups used Cisco WebEx (video interaction
+platform licensed by our university) sessions, some used a group chat, and others used FaceTime
+or other online communication applications.
 
-During the first week of online classes each group produced their proposal and it on a Canvas Discussion in a proposal form for approval.
-The teaching assistant (TA) reviewed proposals and provided feedback or approval.
-Groups used the TA feedback to revise their proposals until they were approved.
-Most proposals obtained approval after two or three revisions, but some required as many as seven revisions to obtain approval.
-The TAs and students found communication about proposals much more difficult online than in face-to-face classes.
+During the first week of online classes each group produced their proposal and it on a Canvas
+Discussion in a proposal form for approval. The teaching assistant (TA) reviewed proposals and
+provided feedback or approval. Groups used the TA feedback to revise their proposals until they
+were approved. Most proposals obtained approval after two or three revisions, but some required
+as many as seven revisions to obtain approval. The TAs and students found communication about
+proposals much more difficult online than in face-to-face classes.
 
-Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion of a mass hanging from a spring in which the students were asked to determine when the spring's mass must be considered as a contribution to the period.
-Before the transition to online classes the students had completed a pre-lab activity in which they measured the period of a mass on a spring.
-For this investigation we provided videos of various masses oscillating on springs (100 oscillations each for 10 different masses and for the spring oscillating with no mass) and photographs of each spring and each mass on a balance.
-We posted video and photograph sets for six different springs so groups in the same lab section would each have different springs to study.
+Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion
+of a mass hanging from a spring in which the students were asked to determine when the spring's
+mass must be considered as a contribution to the period. Before the transition to online
+classes the students had completed a pre-lab activity in which they measured the period of a
+mass on a spring. For this investigation we provided videos of various masses oscillating on
+springs (100 oscillations each for 10 different masses and for the spring oscillating with no
+mass) and photographs of each spring and each mass on a balance. We posted video and photograph
+sets for six different springs so groups in the same lab section would each have different
+springs to study.
 
-Investigation 3 for the General Physics Laboratory II course was a study of light diffraction in which the students were asked to determine whether hairs from two individuals had the same diameter.
-Before the transition to online classes, the students had completed a pre-lab activity in which they determined the width of a single slit by measuring the diffraction pattern.
-We collected hair samples from several people and posted photographs of the diffraction pattens of the hairs.
-Each photograph had a ruler at the bottom for the students to use as a length scale.
-We also provided photographs of the positions of the holder and screen on the optics bench.
-We gave the students a tutorial on using the ImageJ application\citep{schrasetal12} to measure distances in a photograph.
+Investigation 3 for the General Physics Laboratory II course was a study of light diffraction
+in which the students were asked to determine whether hairs from two individuals had the same
+diameter. Before the transition to online classes, the students had completed a pre-lab
+activity in which they determined the width of a single slit by measuring the diffraction
+pattern. We collected hair samples from several people and posted photographs of the
+diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
+use as a length scale. We also provided photographs of the positions of the holder and screen
+on the optics bench. We gave the students a tutorial on using the ImageJ
+application\citep{schrasetal12} to measure distances in a photograph.
 
-When the TA approved a group's  proposal, they assigned the group a data set for the investigation, and the group began its measurements and analysis.
-We provided measurements to the students in the most raw form possible to require them to make decisions about data collection and analysis.
-Each group was required to complete its analysis and create a three-slide presentation for the argumentation session the following week.
-The first slide was a description of their measurements.
-Te second slide was a presentation of the results, including a graph or table, and the third slide was their argument, based on their result.
+When the TA approved a group's proposal, they assigned the group a data set for the
+investigation, and the group began its measurements and analysis. We provided measurements to
+the students in the most raw form possible to require them to make decisions about data
+collection and analysis. Each group was required to complete its analysis and create a
+three-slide presentation for the argumentation session the following week. The first slide was
+a description of their measurements. Te second slide was a presentation of the results,
+including a graph or table, and the third slide was their argument, based on their result.
 
-The argumentation session was held in a Cisco WebEx session during the lab session the week after the proposal session.
-One member of each group gave the presentation, which  was followed by questions.
-Students received credit for giving presentations, asking meaningful questions, and responding to questions.
-Following the argumentation session students submitted individual draft reports, peer-reviewed each other's drafts, and submitted final reports in the same manner used for the face-to-face investigations.
+The argumentation session was held in a Cisco WebEx session during the lab session the week
+after the proposal session. One member of each group gave the presentation, which was followed
+by questions. Students received credit for giving presentations, asking meaningful questions,
+and responding to questions.  Following the argumentation session students submitted individual
+draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
+manner used for the face-to-face investigations.
 
-Investigation 4 in the General Physics Laboratory I course was about collisions, and students were asked to determine whether a collision between two marbles was elastic.
-Our original plans were to have the students video marble collisions in lab and analyze them using the Tracker application\citep{bro2009}.
-When the labs went online, we provided the students with several videos of marble collisions and asked the students to install Tracker on their computers for analysis.
-We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own computers.
-The originally-planned pre-lab was an analysis of a video using Tracker.
-This activity required only a few changes from the face-to-face pre-lab assignment.
-We conducted the proposal session as described for Investigation 3 and assigned each group one of six videos of colliding marbles to analyze along with mass measurements of the marbles in the videos.
-The argumentation session and the remainder of the investigation were conducted in the same manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory I course was about collisions, and students
+were asked to determine whether a collision between two marbles was elastic. Our original plans
+were to have the students video marble collisions in lab and analyze them using the Tracker
+application\citep{bro2009}. When the labs went online, we provided the students with several
+videos of marble collisions and asked the students to install Tracker on their computers for
+analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
+their own computers. The originally-planned pre-lab was an analysis of a video using
+Tracker. This activity required only a few changes from the face-to-face pre-lab assignment. We
+conducted the proposal session as described for Investigation 3 and assigned each group one of
+six videos of colliding marbles to analyze along with mass measurements of the marbles in the
+videos. The argumentation session and the remainder of the investigation were conducted in the
+same manner as Investigation 3.
 
-Investigation 4 in the General Physics Laboratory II course was a study of radioactive decay.
-The pre-lab for the face-to-face course is a simulation of radioactive decay using dice in which the students roll several dice and remove all the dice with one dot showing.
-We wrote a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could perform the same activity using this simulation on their computers.
-For the investigation the students were asked to determine which isotope was most common in the nuclear decay of a copper disk that had been exposed to low-energy neutron radiation.
-We measured radiation counts for several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time in CSV files for analysis.
-As in the other course, the investigation was conducted in the same manner as Investigation 3.
+Investigation 4 in the General Physics Laboratory II course was a study of radioactive
+decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
+in which the students roll several dice and remove all the dice with one dot showing. We wrote
+a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
+perform the same activity using this simulation on their computers. For the investigation the
+students were asked to determine which isotope was most common in the nuclear decay of a copper
+disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
+several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
+in CSV files for analysis. As in the other course, the investigation was conducted in the same
+manner as Investigation 3.
 
-We administered the lab practical exams for both courses in Canvas using GlowScript simulations embedded in Canvas assignments.
-Students made measurements on the simulation and used their results to make an argument answering a guiding question.
+We administered the lab practical exams for both courses in Canvas using GlowScript simulations
+embedded in Canvas assignments. Students made measurements on the simulation and used their
+results to make an argument answering a guiding question.
 
-We encountered many problems with the move to online laboratories.
-Our students had not selected an online class, and many were not prepared for the sudden transition from face-to-face to online classes.
-Many students could not or did not attend the online WebEx sessions or participate with their assigned groups.
-Some students had to get jobs when they returned home, and others did not have access to high-speed internet.
-We removed non-participating students from groups and gave them an opportunity to make up their missed work asynchronously.
-Less than \SI{50}{\percent} of the students in the make-up groups completed their work.
-We resorted to dropping the lowest investigation for the course.
+We encountered many problems with the move to online laboratories. Our students had not
+selected an online class, and many were not prepared for the sudden transition from
+face-to-face to online classes. Many students could not or did not attend the online WebEx
+sessions or participate with their assigned groups. Some students had to get jobs when they
+returned home, and others did not have access to high-speed internet. We removed
+non-participating students from groups and gave them an opportunity to make up their missed
+work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
+completed their work. We resorted to dropping the lowest investigation for the course.
 
-Some students in the course did not have access to computers capable of running Tracker or ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices such as smartphones or tablets.
-We discovered jsTrack\citep{jstrack}, an online Javascript web application for video analysis that runs on most computers including Chromebooks.
-Students using mobile devices were not able to use jsTrack either.
+Some students in the course did not have access to computers capable of running Tracker or
+ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
+mobile devices such as smartphones or tablets. We discovered jsTrack\citep{jstrack}, an online
+Javascript web application for video analysis that runs on most computers including
+Chromebooks. Students using mobile devices were not able to use jsTrack either.
 

### 2020-08-25 demographics/makeGenderTable.R

@@ -1,0 +1,44 @@
+##################################################################
+##
+## makeGenderTable.R
+## Author: SFW
+##
+## This takes the master roster from the XLABs project and makes a table of genders and majors
+##
+##################################################################
+
+library(tables)
+
+master.dat = read.csv('./data/masterRoster.csv')
+
+p1251f19 = master.dat[master.dat$Course=='PHYS1251' & master.dat$Semester=='F19', ]
+p1261s20 = master.dat[master.dat$Course=='PHYS1261' & master.dat$Semester=='S20', ]
+physDat = master.dat[master.dat$Course=='PHYS1251' | master.dat$Course=='PHYS1261', ]
+physDat$Course = factor(physDat$Course)
+
+
+tabular( (Gender + 1) ~ ((n=1) + Percent("col"))*Course, data=physDat)
+
+gender.tab = tabular( (Gender + 1) ~ (Percent("col"))*Course, data=physDat)
+
+write.csv.tabular(gender.tab, file='./data/physLabGender.csv')
+
+
+## This makes tables of all of our majors in PHYS 1251/1261
+data = c('p1251f19','p1261s20')
+for(d in data){
+    dat = eval(as.symbol(d))
+    major.mat = as.matrix(tabular( (MAJOR + 1) ~ Percent("col"), data=dat))
+    major.df = as.data.frame(major.mat[-1, ])
+    names(major.df) = major.mat[1, ]
+
+    ## Sort ascending
+    major.df = major.df[order(major.df$Percent), ]
+    ## Now flip the order
+    major.df = major.df[nrow(major.df):1, ]
+
+    ## Write this to a spreadsheet
+    fName = paste0(d,'major.csv')
+    write.csv(major.df, file=fName)
+}
+

### 2020-08-25 manuscript/onlineLabPaper.tex
Revisions to paper prior to meeting with SFW and MWS.

@@
 
-\begin{abstract}
+% There is no abstract in a TPT paper.
+%\begin{abstract}
+%  A key problem facing physics departments, especially given the current global pandemic, is
+%  how can we engage students in our laboratory courses while maintaining appropriate social
+%  distancing and hygiene standards.  One solution to this problem is to move the labs to an
+%  online format.  But how can we do this while \textit{also} engaging our students in online
+%  labs with a curriculum that privileges science practices?  We have created an intro physics
+%  lab curriculum that engages students in science practices and are implementing it online.
+%\end{abstract}
+
+\maketitle
+
+\section{Introduction}
  A key problem facing physics departments, especially given the current global pandemic, is
@@
   lab curriculum that engages students in science practices and are implementing it online.
-\end{abstract}
 
-\maketitle
-
-\section{Introduction}
 Scientific truth is discovered through the practice of doing science.  In fact, the National
@@
 traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
-outdated -- triple beam balances and hand-drawn graphs were standard.  In this same year, as
-part of an interdisciplinary team interested in engaging students in scientific practices as
+xxpart of an interdisciplinary team interested in engaging students in scientific practices as
 well as assessing those scientific practices, we secured funding, both internally and from the
@@
 We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
-shut-down due to the global pandemic.  With students off campus, we had to abruptly shift our
-delivery to an online format, and quickly realized that some of the activities that we utilized
-in the face-to-face sections had to be adapted to online use.  Going forward, we've further
+shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly shift our
+delivery to an online format and quickly realized that some of the activities that we utilized
+in the face-to-face sections had to be adapted to online use.  Going forward, we have further
 adapted what we are doing so that students can still participate in a hands-on laboratory
-experience.  We hope these changes will be meaningful long-term as a lack of online labs is
-also a barrier for DE students' completion of a degree.  So online lab curricula would fill an
+experience in an online laboratory course.  We hope these changes will be meaningful long-term as a lack of online labs is
+also a barrier for distance education students' completion of a degree.  So online lab curricula would fill an
 institutional need.  In the next sections, we will discuss our institutional and instructional
@@
 part of our state.  The university mission is focused on regional transformation and service to
-this region.  The total student population in Fall 2019 was 23k.  Our physics labs (Physics 1
+this region.  The total student population in Fall 2019 was 29k.  Our physics labs (Physics 1
 lab and Physics 2 lab) are each 1 credit courses that meet for 2 hours per week. These courses
@@
 
-Labs are supervised by MWS, but each section is run by Graduate TAs (GTAs). The transformed
-curriculum was jointly written by both of the authors.  TA training was greatly enhanced when
+Labs are supervised by MWS, but each section is run by Graduate GTAs (GTAs). The transformed
+curriculum was jointly written by both of the authors.  GTA training was greatly enhanced when
 the new lab curriculum was put in place.  SFW and MWS, along with colleagues in Biology and
@@
 disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
-meeting with the TAs, and SFW and the research team have supervised various aspects of the
+meeting with the GTAs, and SFW and the research team have supervised various aspects of the
 transformation especially important for research such as curricular implementation \cite{AL's
@@
 
-\subsection{Week 1: Pre-Lab}
+\subsection{Session 1: Pre-Lab}
 Part of the goal of any laboratory is to help students develop a familiarity with certain tools
 and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
-students familiarity with the equipment they will be using.  For the investigation that I
+students familiarity with the equipment they will be using.  For the investigation 
 described previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''
@@
 them some tools that they need to be able to answer this question.  As a part of the pre-lab
-reading, students are given reading about linear regression---both how to run it in Excel, and
+reading, students are given information about linear regression---both how to run it in Excel, and
 how to interpret the output, and how we can estimate instantaneous velocity given position
-vs. time data. For this experiment, we give them a cart (leaving the fan off for now) and have
+vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
 them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
@@
 
-\subsection{Week 2: Proposal Development and Data Collection}
-During this week, students work in groups of 4 to develop a proposal, get it approved by a GTA,
+\subsection{Session 2: Proposal Development and Data Collection}
+During this session, students work in groups of 4 to develop a proposal, get it approved by a GTA,
 and then collect and analyze their data.  We have a format for proposal development that asks
@@
 
-\subsection{Week 3: Argumentation and Peer Review}
-During this week, the students begin by sharing their results.  Students finish analyzing their
+\subsection{Session 3: Argumentation and Peer Review}
+During this session, the students begin by sharing their results.  Students finish analyzing their
 data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from the
@@
 The travelers learn what other groups did, and compare to their results in a structured
-argumentation setting.  Groups spend about 3-5 minutes at a poster, and rotate so that they see
+argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they see
 at least 3 other posters.  After the travelers return, critically, the groups spend time
@@
 
-Students write a shortened lab report consisting of three sections: An introduction to the
+Each student writes a shortened lab report consisting of three sections: an introduction to the
 scientific concept, a description of the experimental method or procedure, and a discussion
-section laying out their results, and the evidence and justification supporting their results. 
-The authors have created different peer review calibration videos for the students to watch, so
-that they can look for the same things that we are going to be grading them on when we get
-their final reports.  Students complete their lab report and turn it in by the end of the day.
+section laying out their results and the evidence and justification supporting their results. 
+The authors have created different peer review calibration videos for the students to watch so
+they can look for the same things that we are going to be grading them on when we get
+their final reports.  Students complete their lab report and submit it by the end of the day.
 Then, students take part in double-confidential peer review.  We facilitate this online.  They
@@
 
-In March 2020 the COVID 19 pandemic forced most universities, including East Carolina
-University, to move all their classes online. Our General Physics I and II laboratories had
+In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their classes online. Our General Physics I and II laboratories had
 completed two out of four full investigations and the pre-lab for the third investigation
@@
 
-During the first week of online classes each group produced their proposal and it on a Canvas
-Discussion in a proposal form for approval. The teaching assistant (TA) reviewed proposals and
-provided feedback or approval. Groups used the TA feedback to revise their proposals until they
+During the first week of online classes each group produced their proposal and posted a proposal form on a Canvas
+Discussion for approval. The GTA reviewed proposals and
+provided feedback or approval. Groups used the GTA feedback to revise their proposals until they
 were approved. Most proposals obtained approval after two or three revisions, but some required
-as many as seven revisions to obtain approval. The TAs and students found communication about
-proposals much more difficult online than in face-to-face classes.
+as many as seven revisions to obtain approval. The GTAs and students found communication about
+proposals much more difficult online than in face-to-face classes. When the GTA approved a group's proposal, they assigned the group a data set for the
+investigation, and the group began its measurements and analysis. We provided measurements to
+the students in the most raw form possible to require them to make decisions about data
+collection and analysis.
 
@@
 use as a length scale. We also provided photographs of the positions of the holder and screen
-on the optics bench. We gave the students a tutorial on using the ImageJ
+on the optics bench. We gave the students a tutorial on using the \emph{ImageJ}
 application\citep{schrasetal12} to measure distances in a photograph.
 
-When the TA approved a group's proposal, they assigned the group a data set for the
-investigation, and the group began its measurements and analysis. We provided measurements to
-the students in the most raw form possible to require them to make decisions about data
-collection and analysis. Each group was required to complete its analysis and create a
+Each group was required to complete its analysis and create a
 three-slide presentation for the argumentation session the following week. The first slide was
@@
 were asked to determine whether a collision between two marbles was elastic. Our original plans
-were to have the students video marble collisions in lab and analyze them using the Tracker
-application\citep{bro2009}. When the labs went online, we provided the students with several
-videos of marble collisions and asked the students to install Tracker on their computers for
+were to have the students video marble collisions in lab and analyze them using the \emph{Tracker}
+application\citep{bro2009}, which is installed on the computers in the laboratory. When the labs went online, we provided the students with several
+videos of marble collisions and asked the students to install \emph{Tracker} on their computers for
 analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
 their own computers. The originally-planned pre-lab was an analysis of a video using
-Tracker. This activity required only a few changes from the face-to-face pre-lab assignment. We
+\emph{Tracker}. This activity required only a few changes from the face-to-face pre-lab assignment. We
 conducted the proposal session as described for Investigation 3 and assigned each group one of
@@
 We encountered many problems with the move to online laboratories. Our students had not
-selected an online class, and many were not prepared for the sudden transition from
+registered for an online class, and many were not prepared for the sudden transition from
 face-to-face to online classes. Many students could not or did not attend the online WebEx
 sessions or participate with their assigned groups. Some students had to get jobs when they
-returned home, and others did not have access to high-speed internet. We removed
+returned home, and many students did not have access to high-speed internet. We removed
 non-participating students from groups and gave them an opportunity to make up their missed
@@
 
-Some students in the course did not have access to computers capable of running Tracker or
-ImageJ, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
-mobile devices such as smartphones or tablets. We discovered jsTrack\citep{jstrack}, an online
+Some students in the course did not have access to computers capable of running \emph{Tracker} or
+\emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
+mobile devices such as smartphones or tablets. We discovered \emph{jsTrack}\citep{jstrack}, an online
 Javascript web application for video analysis that runs on most computers including
-Chromebooks. Students using mobile devices were not able to use jsTrack either.
+Chromebooks. Students using mobile devices were not able to use \emph{jsTrack} either.
 
@@
 the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
-teaching laboratories would have to operate at half capacity to maintain social distancing,
+teaching laboratories would have to operate at half-capacity face-to-face to maintain social distancing,
 preventing us from offering the courses to the necessary number of students.  In addition to
@@
 eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half
-of the Fall 2020 courses are scheduled for the first eight-week block, and half of the courses
-are scheduled for the second block. Course mapping between the originally scheduled 14-week
+of the Fall 2020 courses were scheduled for the first eight-week block, and half of the courses
+were scheduled for the second block. Course mapping between the originally scheduled 14-week
 semester and the two eight-week blocks was based on the originally scheduled class meeting
 time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per
-week. We determined that even though there were enough lab meetings for the synchronous
+week. We determined that, even though there were enough lab meetings for the synchronous
 activities of four full investigations, there was not enough time between lab meetings for the
@@
 We informed the students before the course began that internet connectivity was required and
-that they must have access to a computer capable of running Tracker (General Physics Laboratory
-I) or ImageJ (General Physics Laboratory II). We also included these statements in the course
+that they must have access to a computer capable of running \emph{Tracker} (General Physics Laboratory
+I) or \emph{ImageJ} (General Physics Laboratory II). We also included these statements in the course
 syllabus. Although the courses were online, most of the students were on campus allowing them
@@
 items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II
-kit cost ???. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
+kit cost \$39.00. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
 Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics

### 2020-08-27 manuscript/onlineLabPaper.tex
Draft is still long, but I have to give it a break.  I think that we should work to shorten my description of the ADI curriculum.  I've started an addendum, but only just started it.  It will need some significant work (as it is essentially just the previous revision of the paper dumped into a tex file.

@@
 
-\author{First Author} \affiliation{Masked Institution} \author{Second Author}
-\affiliation{Masked Institution}
+\author{First Author} \affiliation{Masked Institution}
+
+\author{Second Author} \affiliation{Masked Institution}
 
@@
 % There is no abstract in a TPT paper.
-%\begin{abstract}
+% \begin{abstract}
 %   A key problem facing physics departments, especially given the current global pandemic, is
@@
 %   lab curriculum that engages students in science practices and are implementing it online.
-%\end{abstract}
+% \end{abstract}
 
@@
 \section{Introduction}
- A key problem facing physics departments, especially given the current global pandemic, is
-  how can we engage students in our laboratory courses while maintaining appropriate social
-  distancing and hygiene standards.  One solution to this problem is to move the labs to an
-  online format.  But how can we do this while \textit{also} engaging our students in online
-  labs with a curriculum that privileges science practices?  We have created an intro physics
-  lab curriculum that engages students in science practices and are implementing it online.
+There are many challenges that physics faculty face when teaching introductory labs. One of
+these challenges is engaging students in authentic science practices.  Another has been
+highlighted given the current global pandemic---specifically how to engage students in our
+laboratory courses while maintaining appropriate social distancing and hygiene standards. We
+have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
+rationale behind the first transformation to a practice-focused curriculum.  When March 2020
+rolled around we needed to transform our labs again, this time to accommodate online
+learning. This paper discusses two chief questions: ``What are we doing to engage students in
+science practices?'' and ``How did we make all of this work online?''
 
-Scientific truth is discovered through the practice of doing science.  In fact, the National
-Research Council in it's report on Discipline Based Education Research (DBER) states, ``Without
-[scientific] investigative practices, there would be no new scientific and engineering
-knowledge.''\cite{DBERreport} However, too often, laboratory courses do not meaningfully engage
-students in scientific practices, instead reproducing classical experiments.\cite{PCAST12} This
-is part of a long-standing tradition of calling for authentic engagement in scientific
-practices which pre-dates Lorentz transformations.\cite{AAAS1881} Indeed, the AAAS stated our
-goals quite succinctly, ``[Typical courses in t]he sciences\ldots are not made the means of
-cultivating the observing powers, stimulating inquiry, exercising the judgment in weighing
-evidence, nor of forming independent habits of thought.''\cite{AAAS1881}
+% Scientific truth is discovered through the practice of doing science.  \citeauthor{DBERreport}
+% state, ``Without [scientific] investigative practices, there would be no new scientific and
+% engineering knowledge.''\citep{DBERreport} Too often, our laboratory courses do not
+% meaningfully engage students in scientific practices, instead reproducing classical
+% experiments.\citep{PCAST12} This is part of a long-standing tradition of calling for authentic
+% engagement in scientific practices which pre-dates Lorentz transformations.\citep{AAAS1881}
+% Indeed, back in \citeyear{AAAS1881}, the AAAS stated our goals quite succinctly, ``[Typical
+% courses in t]he sciences\ldots are not made the means of cultivating the observing powers,
+% stimulating inquiry, exercising the judgment in weighing evidence, nor of forming independent
+% habits of thought.''\citep{AAAS1881}
 
-The situation at our home institution in the Fall of 2016 very much mirrored the national
-narrative.  The lab curriculum had been largely unchanged for about 20 years, and followed the
-traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
-xxpart of an interdisciplinary team interested in engaging students in scientific practices as
-well as assessing those scientific practices, we secured funding, both internally and from the
-NSF, to change this status quo in physics, biology, and chemistry.  All three departments
-transformed their labs using a pedagogical framework entitled, Argument Driven Inquiry
-(ADI),\cite{Sampson2011,Walker2011,Walker2016} which has been specifically designed to engage
-students in authentic science practices. We will focus on the physics transformation in this
-paper.
+The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
+The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment
+commonly used by students was outdated---triple beam balances and hand-drawn graphs were
+standard.  In the same year, as part of an interdisciplinary team interested in engaging
+students in scientific practices as well as assessing those scientific practices, we secured
+funding, both internally and from the NSF, to change this status quo in physics, biology, and
+chemistry.  All three departments transformed their labs using a pedagogical framework
+entitled, Argument Driven Inquiry (ADI),\citep{Sampson2011,Walker2011,Walker2016} which has
+been specifically designed to engage students in authentic science practices. In physics, we
+also utilized the AAPT Lab Recommendations to guide our transformation.\citep{kozminski2014aapt}
 
 We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
-shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly shift our
-delivery to an online format and quickly realized that some of the activities that we utilized
-in the face-to-face sections had to be adapted to online use.  Going forward, we have further
-adapted what we are doing so that students can still participate in a hands-on laboratory
-experience in an online laboratory course.  We hope these changes will be meaningful long-term as a lack of online labs is
-also a barrier for distance education students' completion of a degree.  So online lab curricula would fill an
-institutional need.  In the next sections, we will discuss our institutional and instructional
-contexts and describe each transformation in more detail.
+shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly
+shift our delivery to an online format and quickly realized that some of the activities that we
+utilized in the face-to-face sections had to be adapted to online use.  Going forward, we have
+further adapted what we are doing so that students can still participate in a hands-on
+laboratory experience in an online laboratory course.
 
 \section{Instructional Context}
-\textcolor{red}{This section needs to have the institution masked before we send it in.}
 
-East Carolina University is a regional master's university in a rural, economically depressed
-part of our state.  The university mission is focused on regional transformation and service to
-this region.  The total student population in Fall 2019 was 29k.  Our physics labs (Physics 1
-lab and Physics 2 lab) are each 1 credit courses that meet for 2 hours per week. These courses
-serve both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$
-of the students who take our lab course are in (or have taken) the Algebra-based physics
-lecture course. It also fulfills the general education requirement for science lab courses at
-our university.  Table \ref{tab:gender} compares the gender of students in these lab courses
-compared to the university population.  We note that the gender distribution of students in the
-Physics 2 lab generally matches the university population, while the Physics 1 lab skews more
-heavily male than the university population.  We also compare the race of students in these
-contexts in Table \textcolor{red}{not ready yet}\ldots
+Regional State University is a public doctoral granting university in a rural, economically
+depressed part of our state.  The university mission is focused on regional transformation and
+service to this region.  The total combined student population in Fall 2019 was 28,651 largely
+comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and Physics
+\textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These courses serve
+both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of
+the students who take our lab course are in (or have taken) the corresponding Algebra-based
+physics lecture course. These labs also fulfill the general education requirement for science
+lab courses at our university.
 
-Students who take these labs are most often science majors, especially in the health sciences
-(e.g., Biology, Exercise Science), but this lab is also taken by our majors.  In Fall 2019 we
-had 409 students in the Physics 1 lab, and in Spring 2020 (at Census Day, before the pandemic
-changed enrollments) we had 256 students in the Physics 2 lab.  In both labs, our enrollment is
-capped at 22 students, due to the constraints of our laboratory classroom.
-
-Labs are supervised by MWS, but each section is run by Graduate GTAs (GTAs). The transformed
-curriculum was jointly written by both of the authors.  GTA training was greatly enhanced when
-the new lab curriculum was put in place.  SFW and MWS, along with colleagues in Biology and
-Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics as these
-disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
-meeting with the GTAs, and SFW and the research team have supervised various aspects of the
-transformation especially important for research such as curricular implementation \cite{AL's
-  paper} and assessment practices \cite{Wolf2019}.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|ll|l}
-    \hline \hline							
-    &	\multicolumn{2}{c|}{Course}\\
-    Gender	&	Physics 1	&	Physics 2	&	University	\\ \hline
-    Female	&	41.8\%	&	60.9\%	&	57.1\%	\\
-    Male	&	58.2\%	&	39.1\%	&	42.9\%	\\
-    \hline \hline							
-  \end{tabular}
-  \caption{Gender breakdown of students in the Fall 2019 of the Physics 1 lab, the Spring 2020
-    Physics 1 lab, and the undergraduate poplulation of the university at large in Fall 2019.
-    Note: The university only collected binary gender data }
-  \label{tab:gender}
-\end{table}
+Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
+transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
+enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
+Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
+as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
+weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
+aspects of the transformation especially important for research such as curricular
+implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.
 
@@
 in school better match what actually transpires in authentic research settings
-\cite{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to answer
-questions, or measure quantities, that are well-known using procedures that have been refined
-over time.  For example, in physics we often have students measure $g$ using a well-known
-method (such as a spark timer).  In ADI labs, we give students a question to answer (e.g.,
-``Does the force a fan exerts on a cart depend on the mass of the cart?''), allow them to
-design a procedure for an experiment that will answer that question, collect and analyze their
-data, and make claims based on their data.  We accomplish this by having students engage in a
-three-part cycle:
+\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
+answer questions, or measure quantities, that are well-known using procedures that have been
+refined over time.  In ADI labs, we give students a guiding question to answer experimentally
+(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
+students to design a procedure for an experiment that will answer that question, collect and
+analyze their data, and make claims based on their data.  We accomplish this by having students
+engage in a three-part cycle:
 \begin{itemize}
@@
 In the sections below, we will comment on each part of the cycle, focusing on both students and
-GTAs.
+GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
+and the semester ends with a practical exam where students engage in this process on a
+shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental materials
+with more details about each of the labs in our curriculum.
 
@@
 and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
-students familiarity with the equipment they will be using.  For the investigation 
-described previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''
-we need students to become familiar with a few things, such as what we mean by a cart, and give
-them some tools that they need to be able to answer this question.  As a part of the pre-lab
-reading, students are given information about linear regression---both how to run it in Excel, and
-how to interpret the output, and how we can estimate instantaneous velocity given position
+students familiarity with the equipment they will be using.  For the investigation described
+previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  we need
+students to become familiar with a few things, such as what we mean by a cart, and give them
+some tools that they need to be able to answer this question.  As a part of the pre-lab
+reading, students are given information about linear regression---both how to run it in Excel,
+and how to interpret the output, and how we can estimate instantaneous velocity given position
 vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
 them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
-collect position vs.\ time data for this motion.  Students work in pairs to do this work, and
-turn in a brief summary of this work on the course management system.  For this investigation,
-it is the first time that they create graphs, so we set norms for graphing such as helping them
-decide which variable to put on the x-axis and the y-axis as well as including units.  Pre-lab
-assignments are designed to be graded in less than 1 minute/paper based on a rubric we provide
-to both students and GTAs.
+collect position vs.\ time data for this motion.  Students work in pairs and turn in a brief
+summary of this work on the course management system.  For this investigation, it is the first
+time that they create graphs, so we set norms for graphing such as helping them decide which
+variable to put on the x-axis and the y-axis as well as including units.  Pre-lab assignments
+are designed to be graded in less than 1 minute/paper based on a rubric we provide to both
+students and GTAs.
 
 \subsection{Session 2: Proposal Development and Data Collection}
-During this session, students work in groups of 4 to develop a proposal, get it approved by a GTA,
-and then collect and analyze their data.  We have a format for proposal development that asks
-students to link the scientific concept being studied---in this example case, Newton's Second
-Law---to the data that they will collect.  Students also need to propose a plan for analyzing
-their data and minimizing potential sources of error (such as friction).  Once students have an
-approved proposal, they begin collecting and analyzing their data.  This may lead them to
-refine or revise their method (which they are encouraged to do).  Grading for the GTAs this
-week is minimal (full credit for completing the proposal).  However, this is the most critical
-week's for GTA training.  GTAs have to be clear that the goal is to allow a diverse number of
-ways of collecting/analyzing this data.  How much does the mass of the cart need to vary?  How
-many different cart masses do the students need to take?  How should students deal with
-friction? All of these are questions that we want the \textit{students} to answer.  And in some
-sense, we will be disappointed if all of the students come up with the same answer.
-Experimental methods certainly have an impact on experimental results.
+During this session, students work in groups of 3-4 on the guiding question.  They develop a
+proposal, get it approved by a GTA, and then collect and analyze their data.  We have a format
+for proposal development that asks students to link the scientific concept being studied---in
+this example case, Newton's Second Law---to the data that they will collect.  Students also
+need to propose a plan for analyzing their data and minimizing potential sources of error (such
+as friction).  Once students have an approved proposal, they begin collecting and analyzing
+their data.  This may lead them to refine or revise their method (which they are encouraged to
+do).  Grading for the GTAs this week is minimal (students get full credit for getting their
+proposal approved).  However, this is the most critical week for GTA training.  GTAs have to be
+clear that the goal is to allow a diverse number of ways of collecting/analyzing this
+data. This can be uncomfortable for the GTAs and students alike.  Students want ``the answer,''
+and GTAs want to provide one to them.  However, experimental methods certainly have an impact
+on experimental results. One of the goals of this curriculum is to get students to understand
+this and apply it as they develop their experimental procedures and evaluate their results.
 
 \subsection{Session 3: Argumentation and Peer Review}
-During this session, the students begin by sharing their results.  Students finish analyzing their
-data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from the
-group stays at the whiteboard while the other group members (travelers) go to other groups.
+During this session, the students begin by sharing their results.  Students finish analyzing
+their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
+the group stays at the whiteboard while the other group members (travelers) go to other groups.
 The travelers learn what other groups did, and compare to their results in a structured
-argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they see
-at least 3 other posters.  After the travelers return, critically, the groups spend time
+argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they
+see at least 3 other posters.  After the travelers return, critically, the groups spend time
 discussing what they saw and reflecting on their own results.  What is exciting is that
-sometimes, these interactions actually drive groups to change their claims \cite{Walker2019}.
+sometimes, these interactions actually drive groups to change their claims.\citep{Walker2019}
 
@@
 The authors have created different peer review calibration videos for the students to watch so
-they can look for the same things that we are going to be grading them on when we get
-their final reports.  Students complete their lab report and submit it by the end of the day.
-Then, students take part in double-confidential peer review.  We facilitate this online.  They
-read and reply to two different lab reports.  Finally, they get their feedback and use this to
-revise their own lab report.  At the end of this week, students turn in their revised,
-peer-reviewed final lab report.  This is the heaviest week of GTA grading.  We provide a rubric
-for lab report grading, and each lab report generally takes about 3-5 minutes to grade.
+they can look for the same things that we are going to be grading them on when we get their
+final reports.  Students complete their lab report and submit it by the end of the day.  Then,
+students take part in double-confidential peer review that we facilitate online.  They read and
+review two different lab reports using the same rubric as we do on their final drafts.
+Finally, they get their feedback and use this to revise their own lab report.  At the end of
+this week, students turn in their revised, peer-reviewed final lab report.  This is the
+heaviest week of GTA grading, each lab report generally takes about 3-5 minutes to grade.
 
@@
 
-In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their classes online. Our General Physics I and II laboratories had
-completed two out of four full investigations and the pre-lab for the third investigation
-face-to-face. We were forced to find a way to engage students in an online format while
-preserving the nature of the ADI laboratory experience. The face-to-face activities that we
-moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4
-Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam
-online. We required student investigation groups to find a method for online collaboration in
-which everyone in the group could participate. Some groups used Cisco WebEx (video interaction
-platform licensed by our university) sessions, some used a group chat, and others used FaceTime
-or other online communication applications.
+In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their
+classes online. Our Physics \textrm{I} and \textrm{II} laboratories had completed two out of
+four full investigations and the pre-lab for the third investigation face-to-face. We were
+forced to find a way to engage students in an online format while preserving the nature of the
+ADI laboratory experience. In addition, we gave the laboratory practical exam online. We
+required student investigation groups to find a method for online collaboration in which
+everyone in the group could participate. Tools students used were the Course Management System
+communication tools (Canvas), WebEx (video interaction platform licensed by our university),
+and other online communication applications not managed by the university (e.g., group
+chats). We have detailed the adaptations we made to the curriculum in the supplementary
+materials.  One of the principles that we used while making these adaptations is that students
+should exclusively use university-supported (Microsoft Office) or open source resources.
 
-During the first week of online classes each group produced their proposal and posted a proposal form on a Canvas
-Discussion for approval. The GTA reviewed proposals and
-provided feedback or approval. Groups used the GTA feedback to revise their proposals until they
-were approved. Most proposals obtained approval after two or three revisions, but some required
-as many as seven revisions to obtain approval. The GTAs and students found communication about
-proposals much more difficult online than in face-to-face classes. When the GTA approved a group's proposal, they assigned the group a data set for the
-investigation, and the group began its measurements and analysis. We provided measurements to
-the students in the most raw form possible to require them to make decisions about data
-collection and analysis.
+The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab
+and intended to introduce students to data collection and analysis techniques, in-person
+activities were modified for online use by creating (or using) videos or simulated using
+\emph{Glowscript}.\citep{glowscript} Students could collaborate with a partner asynchronously
+for this part of the project.
 
-Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion
-of a mass hanging from a spring in which the students were asked to determine when the spring's
-mass must be considered as a contribution to the period. Before the transition to online
-classes the students had completed a pre-lab activity in which they measured the period of a
-mass on a spring. For this investigation we provided videos of various masses oscillating on
-springs (100 oscillations each for 10 different masses and for the spring oscillating with no
-mass) and photographs of each spring and each mass on a balance. We posted video and photograph
-sets for six different springs so groups in the same lab section would each have different
-springs to study.
+Proposal development also occurred online asynchronously.  Each group produced their proposal
+and posted a proposal form on a discussion board for approval. The GTA reviewed proposals and
+provided feedback or approval. Groups used the GTA feedback to revise their proposals until
+they were approved. Most proposals obtained approval after two or three revisions, but some
+required as many as seven revisions to obtain approval. When the GTA approved a group's
+proposal, they assigned the group a data set for the investigation, and the group began its
+measurements and analysis. Based on our prior experience running the class, we prepared some
+data sets appropriate to the different proposals that previous students had produced and
+provided measurements to the current students in the most raw form possible to require them to
+make decisions about data collection and analysis.
 
-Investigation 3 for the General Physics Laboratory II course was a study of light diffraction
-in which the students were asked to determine whether hairs from two individuals had the same
-diameter. Before the transition to online classes, the students had completed a pre-lab
-activity in which they determined the width of a single slit by measuring the diffraction
-pattern. We collected hair samples from several people and posted photographs of the
-diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
-use as a length scale. We also provided photographs of the positions of the holder and screen
-on the optics bench. We gave the students a tutorial on using the \emph{ImageJ}
-application\citep{schrasetal12} to measure distances in a photograph.
-
-Each group was required to complete its analysis and create a
-three-slide presentation for the argumentation session the following week. The first slide was
-a description of their measurements. Te second slide was a presentation of the results,
-including a graph or table, and the third slide was their argument, based on their result.
-
-The argumentation session was held in a Cisco WebEx session during the lab session the week
-after the proposal session. One member of each group gave the presentation, which was followed
-by questions. Students received credit for giving presentations, asking meaningful questions,
-and responding to questions.  Following the argumentation session students submitted individual
+The argumentation session was held in a scheduled Cisco WebEx session during the lab session
+the week after the proposal session. Before this session, each group was required to complete
+its analysis and create a three-slide presentation for the argumentation session. The first
+slide was a description of their measurements. The second slide was a presentation of the
+results, including a graph or table, and the third slide was their argument, based on their
+result.  One member of each group gave the presentation, which was followed by
+questions. Students received credit for giving presentations, asking meaningful questions, and
+responding to questions.  Following the argumentation session students submitted individual
 draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
 manner used for the face-to-face investigations.
-
-Investigation 4 in the General Physics Laboratory I course was about collisions, and students
-were asked to determine whether a collision between two marbles was elastic. Our original plans
-were to have the students video marble collisions in lab and analyze them using the \emph{Tracker}
-application\citep{bro2009}, which is installed on the computers in the laboratory. When the labs went online, we provided the students with several
-videos of marble collisions and asked the students to install \emph{Tracker} on their computers for
-analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
-their own computers. The originally-planned pre-lab was an analysis of a video using
-\emph{Tracker}. This activity required only a few changes from the face-to-face pre-lab assignment. We
-conducted the proposal session as described for Investigation 3 and assigned each group one of
-six videos of colliding marbles to analyze along with mass measurements of the marbles in the
-videos. The argumentation session and the remainder of the investigation were conducted in the
-same manner as Investigation 3.
-
-Investigation 4 in the General Physics Laboratory II course was a study of radioactive
-decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
-in which the students roll several dice and remove all the dice with one dot showing. We wrote
-a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
-perform the same activity using this simulation on their computers. For the investigation the
-students were asked to determine which isotope was most common in the nuclear decay of a copper
-disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
-several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
-in CSV files for analysis. As in the other course, the investigation was conducted in the same
-manner as Investigation 3.
 
@@
 
-We encountered many problems with the move to online laboratories. Our students had not
-registered for an online class, and many were not prepared for the sudden transition from
-face-to-face to online classes. Many students could not or did not attend the online WebEx
-sessions or participate with their assigned groups. Some students had to get jobs when they
-returned home, and many students did not have access to high-speed internet. We removed
-non-participating students from groups and gave them an opportunity to make up their missed
-work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
-completed their work. We resorted to dropping the lowest investigation for the course.
-
-Some students in the course did not have access to computers capable of running \emph{Tracker} or
-\emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
-mobile devices such as smartphones or tablets. We discovered \emph{jsTrack}\citep{jstrack}, an online
-Javascript web application for video analysis that runs on most computers including
-Chromebooks. Students using mobile devices were not able to use \emph{jsTrack} either.
-
 \subsection{Fully Online Laboratories--Fall 2020}
 
-\begin{table}
-  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
-    block schedule.}
-  \begin{ruledtabular}
-    \begin{tabular}{ccp{28em}}
-      Investigation & Topic & Guiding Question\\
-      \hline
-      1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
-      2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
-      3 & 2-D collisions & Is the collision between two marbles elastic?
-    \end{tabular}
-  \end{ruledtabular}
-\end{table}
+Early on, we decided to hold our introductory physics laboratory courses online in the Fall
+2020 semester in order to preserve the group class interaction aspects of ADI, which would be
+difficult under the social distancing requirements in place due to the
+pandemic.\citep{mclber20} Learning from some of the challenges we faced in the Spring, we
+informed the students before the course began that internet connectivity was required and that
+they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}.\citep{schrasetal12} We also included these statements in the course
+syllabus. Although we began the semester with the university open for socially distant
+face-to-face learning, that has since ended and we have pivoted to online instruction only for
+our undergraduate students.
 
-We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester
-in order to preserve the group class interaction aspects of ADI, which would be difficult under
-the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
-teaching laboratories would have to operate at half-capacity face-to-face to maintain social distancing,
-preventing us from offering the courses to the necessary number of students.  In addition to
-the social distancing requirements for face-to-face class meetings, our university adopted an
-eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half
-of the Fall 2020 courses were scheduled for the first eight-week block, and half of the courses
-were scheduled for the second block. Course mapping between the originally scheduled 14-week
-semester and the two eight-week blocks was based on the originally scheduled class meeting
-time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per
-week. We determined that, even though there were enough lab meetings for the synchronous
-activities of four full investigations, there was not enough time between lab meetings for the
-asynchronous components and timely grading for four investigations. We reduced the number of
-investigations to three and added an additional pre-lab activity to each investigation. The
-topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall}
-for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics
-Laboratory II.
+Furthermore, so that we could provide students with a hands-on experience, we developed lab
+kits with supplies that allowed the students to perform the investigations outside the teaching
+laboratory. We purchased the lab kit items in collaboration with our campus bookstore, and the
+students purchased the lab kits from the bookstore. We ordered lab kit items in bulk and where
+possible directly from manufacturers to reduce the costs of the items. Each General Physics
+Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each General Physics Laboratory II
+kit costs \$39.00. And we have students paying for these kits in place of a physical lab
+manual, which we provide online for this course.  The online adaptation of the face-to-face ADI
+curriculum has remained unchanged --- pre-labs are done in small groups asynchronously,
+proposals are developed in larger groups asynchronously, and argumentation sessions are
+scheduled and occur via WebEx.
 
-\begin{table}
-  \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020
-    block schedule.}
-  \begin{ruledtabular}
-    \begin{tabular}{ccp{26em}}
-      Investigation & Topic & Guiding Question\\
-      \hline
-      1 & Current and resistance & Does a light bulb behave like a resistor? \\
-      2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
-      3 & Diffraction of light & Are hairs from different people the same diameter?
-    \end{tabular}
-  \end{ruledtabular}
-\end{table}
+\section{Discussion}
+We have observed a great number of successes for these transformations.  First and foremost, is
+that we indeed have a lab curriculum that is aligned with national goals and
+standards. Furthermore, we have successfully deployed this online with both short and longer
+planning times.  Students are indeed engaging with science practices as determined by our
+practical assessments, and our department culture around laboratory course instruction is
+invigorated. Psychometric assessment of our students engagement with science practices is
+ongoing.
 
-We informed the students before the course began that internet connectivity was required and
-that they must have access to a computer capable of running \emph{Tracker} (General Physics Laboratory
-I) or \emph{ImageJ} (General Physics Laboratory II). We also included these statements in the course
-syllabus. Although the courses were online, most of the students were on campus allowing them
-to access campus computer laboratories if they did on a computer that met the course
-requirements.
+The transition to online learning has not gone without hiccups.  Technology and access are two
+key factors for success in online learning environments, which were a barrier for many of our
+students.  Indeed our institution's center for survey research has published some findings that
+explain some of our observed issues.\citep{ECUcovidSurvey} The GTAs and students found
+communication about proposals much more difficult online than in face-to-face classes.  Indeed,
+about 10-20\% of our students did not have reliable internet access after the transition to
+online learning in the spring.\citep{ECUcovidSurvey} Also, up to 8\% of students did not have
+access to a computer once they left campus.\citep{ECUcovidSurvey} Additionally, we noticed that
+some students in the course did not have access to computers capable of running \emph{Tracker}
+or \emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not
+Chromebooks or mobile devices. We discovered \emph{jsTrack}\citep{jstrack}, an online
+Javascript web application for video analysis that runs on most computers including
+Chromebooks, but not mobile devices.
 
-\begin{table}
-  \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
-  \begin{tabular}{clc}
-    \hline\hline
-    Quantity & Item & Investigation(s)\\
-    \hline
-    1 & Protractor & 1 \\
-    2 & \SI{25}{mm} marble & 1, 3 \\
-    1 & Tape measure with cm scale & 1, 2, 3\\
-    1 & \SI{0.6}{m} threded rod & 2 \\
-    1 & Eye nut & 2 \\
-    3 & Nuts & 2 \\
-    1 & Door hook & 2 \\
-    1 & \SI{1}{m} string & 2 \\
-    1 & \SI{16}{mm} marble & 3 \\
-    \hline\hline
-  \end{tabular}
-\end{table}
+Many students could not or did not attend the online WebEx sessions or participate with their
+assigned groups.  Once they left campus, many students found they had increased work or school
+responsibilities (42.1\%) or additional family responsibilities (59.0\%).\citep{ECUcovidSurvey}
+We removed non-participating students from groups and gave them an opportunity to make up their
+missed work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
+completed their work.
 
-We developed lab kits with supplies that allowed the students to perform the investigations
-outside the teaching laboratory. We purchased the lab kit items in collaboration with our
-campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
-kit items in bulk and where possible directly from manufacturers to reduce the costs of the
-items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II
-kit cost \$39.00. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
-Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics
-Laboratory II.
-
-\begin{table}
-  \caption{\label{tab: 1261 lab kit} General Physics Laboratory II lab kit contents.}
-  \begin{tabular}{clc}
-    \hline\hline
-    Quantity & Item & Investigation(s)\\
-    \hline
-    1 & \SI{100}{\ohm} resistor & 1 \\
-    1 & \SI{330}{\ohm} resistor & 1 \\
-    1 &  \SI{100}{\ohm} potentiometer & 1 \\
-    1 & E10 light bulb holder & 1 \\
-    1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
-    1 & Breadboard & 1, 2, 3 \\
-    1 & Breadboard power supply & 1, 2, 3 \\
-    1 & USB power supply cable & 1, 2, 3 \\
-    1 & Jumper wire set & 1, 2 \\
-    2 & Multimeters & 1, 2 \\
-    1 & Mini screwdriver for multimeters & 1,2 \\
-    5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
-    4 & Alligator clip leads & 1, 2 \\
-    1 & \SI{1}{\mega\ohm} resistor & 2 \\
-    2 & \SI{100}{\micro\farad} capacitor & 2 \\
-    1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
-    1 & Tape measure with cm scale & 3 \\            
-    \hline\hline
-  \end{tabular}
-\end{table}
-
-\section{Conclusion}
-\textcolor{blue}{SFW and MWS write this together.}
-
-We did it, and you can too!  We should have a resources page/EPAPS for this paper.
+Finally, we hope these changes will be meaningful long-term as a lack of online labs is also a
+barrier for distance education students' completion of a degree.  So online lab curricula would
+fill an institutional need.
 
 \begin{acknowledgments}
-  Redacted for review.% This work has been supported by the NSF (Award \# 1725655).
+  Redacted for review.% This work has been supported by the NSF (Award \# 1725655). We would
+                      % also like to thank the Physics GTAs who have helped us develop
+                      % resources and tutorials for students during this transition.
 \end{acknowledgments}

### 2020-08-27 outline/onlineLabsOutline.tex
Draft is still long, but I have to give it a break.  I think that we should work to shorten my description of the ADI curriculum.  I've started an addendum, but only just started it.  It will need some significant work (as it is essentially just the previous revision of the paper dumped into a tex file.

--- 2020-08-14 outline/outline.tex
@@
 
-\begin{abstract}
-  A key problem facing physics departments, especially given the current global pandemic, is
-  how can we engage students in our laboratory courses while maintaining appropriate social
-  distancing and hygiene standards.  One solution to this problem is to move the labs to an
-  online format.  But how can we engage our students in online labs with a curriculum that
-  privileges science practices?  We have created an intro physics lab curriculum that engages
-  students in science practices and are implementing it online.
-\end{abstract}
+\section{Introduction}
 
-\section{Introduction}
-\textcolor{blue}{SFW mostly writes this.}
-
-Here we set up the rationale behind our initial transformation.  I see this as two-fold:
-\begin{enumerate}
-  \item We hadn't updated our labs in decades, and they utilized outdated technology and
-  pedagogies.
-  \item We wanted to give students an opportunity to delve into science practices.
-\end{enumerate}
-We have been seeking institutional (SFW's Teaching Grant) and national (NSF Award \#) resources
-to support our initial transformation.
-
-Then we've got a pandemic which means online labs were an immediate default. However, a lack of
-online labs is also a barrier for DE students' completion of a degree.  So online lab curricula
-would fill an institutional need.
+Here we set up the rationale behind our initial transformation, specifically, we wanted our
+labs to engage students in Scientific Practices.  Then, when COVID came here, we didn't want to
+lose the progress we made with this transformation, so we describe our need to develop an
+online curriculum that accommodates our students while duplicating many of the face-to-face
+elements that we found essential to this curriculum.
 
 \section{Instructional Context}
-\textcolor{blue}{SFW mostly writes this.}
 
-We should also talk about the specific context of our labs:
 \begin{itemize}
-  \item Discuss institutional profile.
-  \item Discuss student population in labs/lecture courses served.
+  \item Institutional profile.
+  \begin{itemize}
+    \item Student gender and demographics
+    \item University environment: rural, many communities without high speed internet
+  \end{itemize}
+  \item Describe student population in labs/lecture courses served.  Our lab sequence is at the
+  intro level, serving both Algebra-based and Calculus-based physics lecture courses.
   \item Compare course demographics with university demographics.
@@
 \section{Transformation \#1: Argument Driven Inquiry}
-\textcolor{blue}{SFW mostly writes this.}
 
-Brief lit review of ADI, including some of our prior work (PERC 2019 proceedings paper).
-Describe the stages of ADI and how we implement them.
+Brief lit review of Argument Driven Inquiry (ADI), including some of our prior work (PERC 2019
+proceedings paper).  Describe the stages of ADI and how we implement them.
 
 \section{Transformation \#2: Online Adaptation}
-\textcolor{blue}{MWS mostly writes this.}
 
@@
 \end{itemize}
-Lab kit composition
 
 \section{Conclusion}
-\textcolor{blue}{SFW and MWS write this together.}
-
-We did it, and you can too!  We should have a resources page/EPAPS for this paper.
-
-\section{Notes, not part of outline}
-Most TPT papers are \emph{short}---on the order of 2000 words.  For example the following two
-papers are 3 and 4 pages respectively:
-\begin{itemize}
-  \item \url{https://doi.org/10.1119/1.5145407}
-  \item \url{https://doi.org/10.1119/1.5145524}
-\end{itemize}
-So we don't need to kill ourselves on a long-form manuscript.  I think we can turn this around
-in a month or two and get this out.
-
-Also, while I could see having Joi read this and give us some feedback, I'm not sure she needs
-to be an author.  But this isn't a hard and fast stance that I have, and am willing to discuss
-with you.  More to the point, I'm not sure how much she needs this paper.
+We plan to highlight some of our successes and challenges that we have encountered, as well as
+discuss our outlook for online labs in a post-pandemic world.
 

### 2020-08-27 supplement/supplement.tex
Draft is still long, but I have to give it a break.  I think that we should work to shorten my description of the ADI curriculum.  I've started an addendum, but only just started it.  It will need some significant work (as it is essentially just the previous revision of the paper dumped into a tex file.

\documentclass[aip, numerical, preprint]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{siunitx}

\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\setlist{nosep}

\begin{document}
\title{Supplementary Materials: Introductory Physics Labs: A Tale of Two Transformations}

% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
% street, Greenville, NC 27858 USA}

\author{First Author} \affiliation{Masked Institution}

\author{Second Author} \affiliation{Masked Institution}

\date{\today}

\maketitle

\section{Curriculum development timeline}
Talk about the curriculum development, and how departmental culture around the labs changed as
a part of this transformation.

\section{Face-to-face implementation}

Activities and basic equipment.

Assessment practices and discussion of results.

\section{Online implementation}

Curricular adaptation.

Kit contents.

\section{Introduction}
There are many challenges that physics faculty face when teaching introductory labs. One of
these challenges is engaging students in authentic science practices.  Another has been
highlighted given the current global pandemic---specifically how to engage students in our
laboratory courses while maintaining appropriate social distancing and hygiene standards. We
have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
rationale behind the first transformation to a practice-focused curriculum.  However, when
March 2020 rolled around we needed to transform our labs again, this time to accommodate online
learning. This paper discusses three chief questions: ``Why did we change?'' ``What are we
doing to engage students in science practices?'' and ``How did we make all of this work
online?''

Scientific truth is discovered through the practice of doing science.  \citeauthor{DBERreport}
state, ``Without [scientific] investigative practices, there would be no new scientific and
engineering knowledge.''\citep{DBERreport} Too often, our laboratory courses do not
meaningfully engage students in scientific practices, instead reproducing classical
experiments.\citep{PCAST12} This is part of a long-standing tradition of calling for authentic
engagement in scientific practices which pre-dates Lorentz transformations.\citep{AAAS1881}
Indeed, back in \citeyear{AAAS1881}, the AAAS stated our goals quite succinctly, ``[Typical
courses in t]he sciences\ldots are not made the means of cultivating the observing powers,
stimulating inquiry, exercising the judgment in weighing evidence, nor of forming independent
habits of thought.''\citep{AAAS1881}

The physics labs at our institution in the Fall of 2016 very much mirrored the national
narrative.  The lab curriculum had been largely unchanged for about 20 years, and followed the
traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
outdated---triple beam balances and hand-drawn graphs were standard.  In the same year, as part
of an interdisciplinary team interested in engaging students in scientific practices as well as
assessing those scientific practices, we secured funding, both internally and from the NSF, to
change this status quo in physics, biology, and chemistry.  All three departments transformed
their labs using a pedagogical framework entitled, Argument Driven Inquiry
(ADI),\citep{Sampson2011,Walker2011,Walker2016} which has been specifically designed to engage
students in authentic science practices. We will focus on the physics transformation in this
paper.

We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly
shift our delivery to an online format and quickly realized that some of the activities that we
utilized in the face-to-face sections had to be adapted to online use.  Going forward, we have
further adapted what we are doing so that students can still participate in a hands-on
laboratory experience in an online laboratory course.  We hope these changes will be meaningful
long-term as a lack of online labs is also a barrier for distance education students'
completion of a degree.  So online lab curricula would fill an institutional need.  In the next
sections, we will discuss our institutional and instructional contexts and describe each
transformation in more detail.

\section{Instructional Context}

Regional State University is a public doctoral granting university in a rural, economically
depressed part of our state.  The university mission is focused on regional transformation and
service to this region.  The total combined student population in Fall 2019 was 28,651 largely
comprised of undergraduates (23,081).Our physics labs (Physics 1 lab and Physics 2 lab) are
each 1 credit courses that meet for 2 hours per week. These courses serve both of our
Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of the students
who take our lab course are in (or have taken) the Algebra-based physics lecture course. It
also fulfills the general education requirement for science lab courses at our university.
Table \ref{tab:gender} compares the gender of students in these lab courses compared to the
university population.  We note that the gender distribution of students in the Physics 2 lab
generally matches the university population, while the Physics 1 lab skews more heavily male
than the university population.  We also compare the race of students in these contexts in
Table \ref{tab:race}.  The racial and ethnic profile of students in our lab courses is similar
to the university.

Students who take these labs are most often science majors, especially in the health sciences
(e.g., Biology, Exercise Science), but this lab is also taken by our physics majors.  In Fall
2019 we had 409 students in the Physics 1 lab, and in Spring 2020 (at Census Day, before the
pandemic changed enrollments) we had 256 students in the Physics 2 lab.  In both labs, our
enrollment is capped at 22 students, due to the constraints of our laboratory classroom.

Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and SFW and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \hline \hline
                &\multicolumn{2}{c}{Course}\\
    Gender	&Physics 1 &Physics 2 &University\\
    \hline
    Female	&41.8\%	   &60.9\%    &57.1\%\\
    Male	&58.2\%	   &39.1\%    &42.9\%\\
    \hline \hline
  \end{tabular}
  \caption{Gender breakdown of students in the Fall 2019 of the Physics 1 lab, the Spring 2020
    Physics 1 lab, and the undergraduate poplulation of the university at large in Fall 2019.
    Note: The university only collected binary gender data.}
  \label{tab:gender}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \hline\hline
                                            &\multicolumn{2}{c}{Course}\\
    Race/Ethnicity                          &Physics 1  &Physics 2 &University\\
    \hline
    White                                   &60.8\%     &60.8\%    &65.3\%\\
    Black or African American               &17.1\%     &15.5\%    &16.3\%\\
    Hispanic                                &7.5\%      &8.7\%     &7.5\%\\
    Two or More Races                       &7.3\%      &5.3\%     &3.8\%\\
    Unknown                                 &2.9\%      &3.0\%     &3.4\%\\
    Asian                                   &4.0\%      &6.4\%     &2.4\%\\
    American Indian or Alaska Native        &.	        &.         &0.6\%\\
    Non-Resident Alien	                    &0.4\%      &0.4\%     &0.6\%\\
    Native Hawaiian/Other Pacific Islander  &.	        &.         &0.1\%\\
    \hline\hline
  \end{tabular}
  \caption{Race/Ethnicity breakdown of students inthe Fall 2019 semester of the Physics 1 lab,
    the Spring 2020 semester of the Physics 2 lab, and the undergraduate population of the
    university at large in Fall 2019.}
  \label{tab:race}
\end{table}

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
in school better match what actually transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  For example, in physics we often have students measure $g$ using a
well-known method (such as a spark timer).  In ADI labs, we give students a question to answer
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''), allow them
to design a procedure for an experiment that will answer that question, collect and analyze
their data, and make claims based on their data.  We accomplish this by having students engage
in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs.

\subsection{Session 1: Pre-Lab}
Part of the goal of any laboratory is to help students develop a familiarity with certain tools
and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
students familiarity with the equipment they will be using.  For the investigation described
previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  we need
students to become familiar with a few things, such as what we mean by a cart, and give them
some tools that they need to be able to answer this question.  As a part of the pre-lab
reading, students are given information about linear regression---both how to run it in Excel,
and how to interpret the output, and how we can estimate instantaneous velocity given position
vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
collect position vs.\ time data for this motion.  Students work in pairs to do this work, and
turn in a brief summary of this work on the course management system.  For this investigation,
it is the first time that they create graphs, so we set norms for graphing such as helping them
decide which variable to put on the x-axis and the y-axis as well as including units.  Pre-lab
assignments are designed to be graded in less than 1 minute/paper based on a rubric we provide
to both students and GTAs.

\subsection{Session 2: Proposal Development and Data Collection}
During this session, students work in groups of 4 to develop a proposal, get it approved by a
GTA, and then collect and analyze their data.  We have a format for proposal development that
asks students to link the scientific concept being studied---in this example case, Newton's
Second Law---to the data that they will collect.  Students also need to propose a plan for
analyzing their data and minimizing potential sources of error (such as friction).  Once
students have an approved proposal, they begin collecting and analyzing their data.  This may
lead them to refine or revise their method (which they are encouraged to do).  Grading for the
GTAs this week is minimal (full credit for completing the proposal).  However, this is the most
critical week's for GTA training.  GTAs have to be clear that the goal is to allow a diverse
number of ways of collecting/analyzing this data.  How much does the mass of the cart need to
vary?  How many different cart masses do the students need to take?  How should students deal
with friction? All of these are questions that we want the \textit{students} to answer.  And in
some sense, we will be disappointed if all of the students come up with the same answer.
Experimental methods certainly have an impact on experimental results.

\subsection{Session 3: Argumentation and Peer Review}
During this session, the students begin by sharing their results.  Students finish analyzing
their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
the group stays at the whiteboard while the other group members (travelers) go to other groups.
The travelers learn what other groups did, and compare to their results in a structured
argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they
see at least 3 other posters.  After the travelers return, critically, the groups spend time
discussing what they saw and reflecting on their own results.  What is exciting is that
sometimes, these interactions actually drive groups to change their claims \citep{Walker2019}.

Each student writes a shortened lab report consisting of three sections: an introduction to the
scientific concept, a description of the experimental method or procedure, and a discussion
section laying out their results and the evidence and justification supporting their results.
The authors have created different peer review calibration videos for the students to watch so
they can look for the same things that we are going to be grading them on when we get their
final reports.  Students complete their lab report and submit it by the end of the day.  Then,
students take part in double-confidential peer review.  We facilitate this online.  They read
and reply to two different lab reports.  Finally, they get their feedback and use this to
revise their own lab report.  At the end of this week, students turn in their revised,
peer-reviewed final lab report.  This is the heaviest week of GTA grading.  We provide a rubric
for lab report grading, and each lab report generally takes about 3-5 minutes to grade.

\section{Transformation \#2: Online Adaptation}

\subsection{Sudden Transition to Online Instruction--Spring 2020}

In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their
classes online. Our General Physics I and II laboratories had completed two out of four full
investigations and the pre-lab for the third investigation face-to-face. We were forced to find
a way to engage students in an online format while preserving the nature of the ADI laboratory
experience. The face-to-face activities that we moved online were the Investigation 3 Proposal
and Argumentation and the Investigation 4 Pre-Lab, Proposal, and Argumentation. In addition, we
gave our laboratory practical exam online. We required student investigation groups to find a
method for online collaboration in which everyone in the group could participate. Some groups
used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a
group chat, and others used FaceTime or other online communication applications.

During the first week of online classes each group produced their proposal and posted a
proposal form on a Canvas Discussion for approval. The GTA reviewed proposals and provided
feedback or approval. Groups used the GTA feedback to revise their proposals until they were
approved. Most proposals obtained approval after two or three revisions, but some required as
many as seven revisions to obtain approval. The GTAs and students found communication about
proposals much more difficult online than in face-to-face classes. When the GTA approved a
group's proposal, they assigned the group a data set for the investigation, and the group began
its measurements and analysis. We provided measurements to the students in the most raw form
possible to require them to make decisions about data collection and analysis.

Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion
of a mass hanging from a spring in which the students were asked to determine when the spring's
mass must be considered as a contribution to the period. Before the transition to online
classes the students had completed a pre-lab activity in which they measured the period of a
mass on a spring. For this investigation we provided videos of various masses oscillating on
springs (100 oscillations each for 10 different masses and for the spring oscillating with no
mass) and photographs of each spring and each mass on a balance. We posted video and photograph
sets for six different springs so groups in the same lab section would each have different
springs to study.

Investigation 3 for the General Physics Laboratory II course was a study of light diffraction
in which the students were asked to determine whether hairs from two individuals had the same
diameter. Before the transition to online classes, the students had completed a pre-lab
activity in which they determined the width of a single slit by measuring the diffraction
pattern. We collected hair samples from several people and posted photographs of the
diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
use as a length scale. We also provided photographs of the positions of the holder and screen
on the optics bench. We gave the students a tutorial on using the \emph{ImageJ}
application\citep{schrasetal12} to measure distances in a photograph.

Each group was required to complete its analysis and create a three-slide presentation for the
argumentation session the following week. The first slide was a description of their
measurements. Te second slide was a presentation of the results, including a graph or table,
and the third slide was their argument, based on their result.

The argumentation session was held in a Cisco WebEx session during the lab session the week
after the proposal session. One member of each group gave the presentation, which was followed
by questions. Students received credit for giving presentations, asking meaningful questions,
and responding to questions.  Following the argumentation session students submitted individual
draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
manner used for the face-to-face investigations.

Investigation 4 in the General Physics Laboratory I course was about collisions, and students
were asked to determine whether a collision between two marbles was elastic. Our original plans
were to have the students video marble collisions in lab and analyze them using the
\emph{Tracker} application\citep{bro2009}, which is installed on the computers in the
laboratory. When the labs went online, we provided the students with several videos of marble
collisions and asked the students to install \emph{Tracker} on their computers for analysis.
We adapted the Investigation 4 Pre-Lab assignment so students could perform them on their own
computers. The originally-planned pre-lab was an analysis of a video using \emph{Tracker}. This
activity required only a few changes from the face-to-face pre-lab assignment. We conducted the
proposal session as described for Investigation 3 and assigned each group one of six videos of
colliding marbles to analyze along with mass measurements of the marbles in the videos. The
argumentation session and the remainder of the investigation were conducted in the same manner
as Investigation 3.

Investigation 4 in the General Physics Laboratory II course was a study of radioactive
decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
in which the students roll several dice and remove all the dice with one dot showing. We wrote
a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
perform the same activity using this simulation on their computers. For the investigation the
students were asked to determine which isotope was most common in the nuclear decay of a copper
disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
in CSV files for analysis. As in the other course, the investigation was conducted in the same
manner as Investigation 3.

We administered the lab practical exams for both courses in Canvas using GlowScript simulations
embedded in Canvas assignments. Students made measurements on the simulation and used their
results to make an argument answering a guiding question.

We encountered many problems with the move to online laboratories. Our students had not
registered for an online class, and many were not prepared for the sudden transition from
face-to-face to online classes. Many students could not or did not attend the online WebEx
sessions or participate with their assigned groups. Some students had to get jobs when they
returned home, and many students did not have access to high-speed internet. We removed
non-participating students from groups and gave them an opportunity to make up their missed
work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
completed their work. We resorted to dropping the lowest investigation for the course.

Some students in the course did not have access to computers capable of running \emph{Tracker}
or \emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not
Chromebooks or mobile devices such as smartphones or tablets. We discovered
\emph{jsTrack}\citep{jstrack}, an online Javascript web application for video analysis that
runs on most computers including Chromebooks. Students using mobile devices were not able to
use \emph{jsTrack} either.

\subsection{Fully Online Laboratories--Fall 2020}

\begin{table}
  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
    block schedule.}
  \begin{ruledtabular}
    \begin{tabular}{ccp{28em}}
      Investigation & Topic & Guiding Question\\
      \hline
      1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
      2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
      3 & 2-D collisions & Is the collision between two marbles elastic?
    \end{tabular}
  \end{ruledtabular}
\end{table}

We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester
in order to preserve the group class interaction aspects of ADI, which would be difficult under
the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
teaching laboratories would have to operate at half-capacity face-to-face to maintain social
distancing, preventing us from offering the courses to the necessary number of students.  In
addition to the social distancing requirements for face-to-face class meetings, our university
adopted an eight-week block schedule, with the second block ending before the Thanksgiving
holiday. Half of the Fall 2020 courses were scheduled for the first eight-week block, and half
of the courses were scheduled for the second block. Course mapping between the originally
scheduled 14-week semester and the two eight-week blocks was based on the originally scheduled
class meeting time. In the block schedule, the one semester-hour lab courses have two two-hour
meetings per week. We determined that, even though there were enough lab meetings for the
synchronous activities of four full investigations, there was not enough time between lab
meetings for the asynchronous components and timely grading for four investigations. We reduced
the number of investigations to three and added an additional pre-lab activity to each
investigation. The topics for the three investigations and the guiding questions are in Table
\ref{tab: 1251 fall} for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for
General Physics Laboratory II.

\begin{table}
  \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020
    block schedule.}
  \begin{ruledtabular}
    \begin{tabular}{ccp{26em}}
      Investigation & Topic & Guiding Question\\
      \hline
      1 & Current and resistance & Does a light bulb behave like a resistor? \\
      2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
      3 & Diffraction of light & Are hairs from different people the same diameter?
    \end{tabular}
  \end{ruledtabular}
\end{table}

We informed the students before the course began that internet connectivity was required and
that they must have access to a computer capable of running \emph{Tracker} (General Physics
Laboratory I) or \emph{ImageJ} (General Physics Laboratory II). We also included these
statements in the course syllabus. Although the courses were online, most of the students were
on campus allowing them to access campus computer laboratories if they did on a computer that
met the course requirements.

\begin{table}
  \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & Protractor & 1 \\
    2 & \SI{25}{mm} marble & 1, 3 \\
    1 & Tape measure with cm scale & 1, 2, 3\\
    1 & \SI{0.6}{m} threded rod & 2 \\
    1 & Eye nut & 2 \\
    3 & Nuts & 2 \\
    1 & Door hook & 2 \\
    1 & \SI{1}{m} string & 2 \\
    1 & \SI{16}{mm} marble & 3 \\
    \hline\hline
  \end{tabular}
\end{table}

We developed lab kits with supplies that allowed the students to perform the investigations
outside the teaching laboratory. We purchased the lab kit items in collaboration with our
campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
kit items in bulk and where possible directly from manufacturers to reduce the costs of the
items. Each General Physics Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each
General Physics Laboratory II kit costs \$39.00. Table \ref{tab: 1251 lab kit} shows the lab
kit contents for General Physics Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab
kit contents for General Physics Laboratory II.

\begin{table}
  \caption{\label{tab: 1261 lab kit} General Physics Laboratory II lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & \SI{100}{\ohm} resistor & 1 \\
    1 & \SI{330}{\ohm} resistor & 1 \\
    1 &  \SI{100}{\ohm} potentiometer & 1 \\
    1 & E10 light bulb holder & 1 \\
    1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
    1 & Breadboard & 1, 2, 3 \\
    1 & Breadboard power supply & 1, 2, 3 \\
    1 & USB power supply cable & 1, 2, 3 \\
    1 & Jumper wire set & 1, 2 \\
    2 & Multimeters & 1, 2 \\
    1 & Mini screwdriver for multimeters & 1,2 \\
    5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
    4 & Alligator clip leads & 1, 2 \\
    1 & \SI{1}{\mega\ohm} resistor & 2 \\
    2 & \SI{100}{\micro\farad} capacitor & 2 \\
    1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
    1 & Tape measure with cm scale & 3 \\            
    \hline\hline
  \end{tabular}
\end{table}

\section{Conclusion}
Discussion Points:
\begin{itemize}
  \item What have been our successes?  (Related to both Transformations)
  \item What have been our challenges?
  \item What plans do we have for online labs in the future?
\end{itemize}

\begin{acknowledgments}
  Redacted for review.% This work has been supported by the NSF (Award \# 1725655).
\end{acknowledgments}

\bibliography{onlinelabs.bib}

\end{document}

### 2020-08-28 manuscript/onlineLabPaper.tex
Cut the word count by almost 90 words. I am not sure how much more is possible. I also made a redacted version of the Center for Survey Research reference.

@@
 \section{Introduction}
-There are many challenges that physics faculty face when teaching introductory labs. One of
-these challenges is engaging students in authentic science practices.  Another has been
-highlighted given the current global pandemic---specifically how to engage students in our
+A significant challenge facing physics faculty face teaching introductory labs is engaging students in authentic science practices.  Another has been
+highlighted given the current global pandemic---how to engage students in our
 laboratory courses while maintaining appropriate social distancing and hygiene standards. We
 have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
-rationale behind the first transformation to a practice-focused curriculum.  When March 2020
-rolled around we needed to transform our labs again, this time to accommodate online
+rationale behind the first transformation to a practice-focused curriculum.  In March 2020
+we needed to transform our labs again, this time to accommodate online
 learning. This paper discusses two chief questions: ``What are we doing to engage students in
@@
 The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
-The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment
-commonly used by students was outdated---triple beam balances and hand-drawn graphs were
-standard.  In the same year, as part of an interdisciplinary team interested in engaging
-students in scientific practices as well as assessing those scientific practices, we secured
-funding, both internally and from the NSF, to change this status quo in physics, biology, and
-chemistry.  All three departments transformed their labs using a pedagogical framework
-entitled, Argument Driven Inquiry (ADI),\citep{Sampson2011,Walker2011,Walker2016} which has
+The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment and techniques used by students was outdated---triple beam balances and hand-drawn graphs were
+standard.  That same year, as part of an interdisciplinary team interested in engaging
+students in and assessing scientific practices, we secured
+funding, both internally and from the NSF, to change this \emph{status quo} in physics, biology, and
+chemistry.  All three departments transformed their labs using the Argument Driven Inquiry (ADI),\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has
 been specifically designed to engage students in authentic science practices. In physics, we
@@
 
-We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
-shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly
-shift our delivery to an online format and quickly realized that some of the activities that we
-utilized in the face-to-face sections had to be adapted to online use.  Going forward, we have
+We were satisfied with our progress when the global COVID-19 pandemic forced a shutdown in March 2020.  With students off campus, we had to abruptly
+shift our delivery to an online format and quickly realized that many of the face-to-face activities  had to be adapted to online use.  Going forward, we have
 further adapted what we are doing so that students can still participate in a hands-on
@@
 
-Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
+Labs are supervised by Author 2, but sections are run by Graduate GTAs (GTAs). The
 transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
 enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
-Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
+Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
 as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
@@
 \section{Transformation \#1: Argument Driven Inquiry}
-Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
-in school better match what actually transpires in authentic research settings
+Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs
+in school better match what transpires in authentic research settings
 \citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
@@
 students familiarity with the equipment they will be using.  For the investigation described
-previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  we need
-students to become familiar with a few things, such as what we mean by a cart, and give them
-some tools that they need to be able to answer this question.  As a part of the pre-lab
-reading, students are given information about linear regression---both how to run it in Excel,
-and how to interpret the output, and how we can estimate instantaneous velocity given position
+previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  students must become familiar with a few things, such as what we mean by a cart and also obtain some tools to be able to answer this question.
+As a part of the pre-lab
+reading, students learn about linear regression---both how to run it in Excel,
+how to interpret the output, and how we can estimate instantaneous velocity given position
 vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
 them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
-collect position vs.\ time data for this motion.  Students work in pairs and turn in a brief
-summary of this work on the course management system.  For this investigation, it is the first
-time that they create graphs, so we set norms for graphing such as helping them decide which
-variable to put on the x-axis and the y-axis as well as including units.  Pre-lab assignments
-are designed to be graded in less than 1 minute/paper based on a rubric we provide to both
+collect position vs.\ time data.  Students work in pairs and submit a brief
+summary of this work on the learning management system (LMS). This investigation is the first
+time the students create graphs, so we set norms for graphing such as helping them decide which
+variable to put on the $x$-axis and the $y$-axis as well as including units.  Pre-lab assignments
+are designed to be graded in less than 1 minute/submission based on a rubric we provide to both
 students and GTAs.
@@
 During this session, students work in groups of 3-4 on the guiding question.  They develop a
-proposal, get it approved by a GTA, and then collect and analyze their data.  We have a format
-for proposal development that asks students to link the scientific concept being studied---in
+proposal, get it approved by a GTA, and then collect and analyze data.  Our proposal development format asks students to link the scientific concept being studied---in
 this example case, Newton's Second Law---to the data that they will collect.  Students also
-need to propose a plan for analyzing their data and minimizing potential sources of error (such
+must propose a plan for analyzing their data and minimizing potential sources of error (such
 as friction).  Once students have an approved proposal, they begin collecting and analyzing
-their data.  This may lead them to refine or revise their method (which they are encouraged to
-do).  Grading for the GTAs this week is minimal (students get full credit for getting their
+their data.  This may lead them to refine or revise their method (which is encouraged).  Grading for the GTAs this week is minimal (students get full credit for getting their
 proposal approved).  However, this is the most critical week for GTA training.  GTAs have to be
@@
 data. This can be uncomfortable for the GTAs and students alike.  Students want ``the answer,''
-and GTAs want to provide one to them.  However, experimental methods certainly have an impact
+and GTAs want to provide one for them.  However, experimental methods certainly have an impact
 on experimental results. One of the goals of this curriculum is to get students to understand
@@
 \subsection{Session 3: Argumentation and Peer Review}
-During this session, the students begin by sharing their results.  Students finish analyzing
+During this session, the students share their results in a poster session.  Students finish analyzing
 their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
@@
 
-Each student writes a shortened lab report consisting of three sections: an introduction to the
+After the session, each student submits a draft report consisting of three sections: an introduction to the
 scientific concept, a description of the experimental method or procedure, and a discussion
-section laying out their results and the evidence and justification supporting their results.
+section laying out their results and the evidence and justification supporting their results by the end of the next day.
 The authors have created different peer review calibration videos for the students to watch so
-they can look for the same things that we are going to be grading them on when we get their
-final reports.  Students complete their lab report and submit it by the end of the day.  Then,
-students take part in double-confidential peer review that we facilitate online.  They read and
-review two different lab reports using the same rubric as we do on their final drafts.
-Finally, they get their feedback and use this to revise their own lab report.  At the end of
+they can look for the same things that we will grade when we get their
+final reports.
+After watching the video, students take part in online, double-confidential peer reviews of two different lab reports using a simplified rubric based on the grading rubric for final drafts.
+Finally, students use their feedback to revise their own lab reports.  At the end of
 this week, students turn in their revised, peer-reviewed final lab report.  This is the
@@
 
-In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their
-classes online. Our Physics \textrm{I} and \textrm{II} laboratories had completed two out of
+In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all
+classes online. Our Physics 1 and 2 laboratories had completed two out of
 four full investigations and the pre-lab for the third investigation face-to-face. We were
@@
 required student investigation groups to find a method for online collaboration in which
-everyone in the group could participate. Tools students used were the Course Management System
-communication tools (Canvas), WebEx (video interaction platform licensed by our university),
-and other online communication applications not managed by the university (e.g., group
+everyone in the group could participate. Tools students used were the LMS (Canvas)
+communication tools, WebEx (video interaction platform licensed by our university),
+and other online communication applications not managed by the university (\emph{e.g.}, group
 chats). We have detailed the adaptations we made to the curriculum in the supplementary
@@
 
-The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab
-and intended to introduce students to data collection and analysis techniques, in-person
+The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab intended to introduce students to data collection and analysis techniques, in-person
 activities were modified for online use by creating (or using) videos or simulated using
@@
 required as many as seven revisions to obtain approval. When the GTA approved a group's
-proposal, they assigned the group a data set for the investigation, and the group began its
+proposal, they assigned the group a data set for the investigation, and the group began
 measurements and analysis. Based on our prior experience running the class, we prepared some
@@
 
-The argumentation session was held in a scheduled Cisco WebEx session during the lab session
+The argumentation session was held in a scheduled Cisco WebEx session
 the week after the proposal session. Before this session, each group was required to complete
-its analysis and create a three-slide presentation for the argumentation session. The first
-slide was a description of their measurements. The second slide was a presentation of the
-results, including a graph or table, and the third slide was their argument, based on their
-result.  One member of each group gave the presentation, which was followed by
+its analysis and create a three-slide presentation for the argumentation session: (1) a description of their measurements, (2) a presentation of the
+results, including a graph or table, and (3) their argument based on their
+results.  One member of each group gave the presentation, which was followed by
 questions. Students received credit for giving presentations, asking meaningful questions, and
@@
 
-We administered the lab practical exams for both courses in Canvas using GlowScript simulations
-embedded in Canvas assignments. Students made measurements on the simulation and used their
+We administered the lab practical exams for both courses in the LMS using GlowScript simulations
+embedded in LMS assignments. Students made measurements on the simulation and used their
 results to make an argument answering a guiding question.
@@
 Early on, we decided to hold our introductory physics laboratory courses online in the Fall
-2020 semester in order to preserve the group class interaction aspects of ADI, which would be
-difficult under the social distancing requirements in place due to the
+2020 semester to preserve the group class interaction aspects of ADI, which would be
+difficult under social distancing requirements in place due to the
 pandemic.\citep{mclber20} Learning from some of the challenges we faced in the Spring, we
 informed the students before the course began that internet connectivity was required and that
-they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}.\citep{schrasetal12} We also included these statements in the course
+they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}\citep{schrasetal12} (used in the course). We also included these statements in the course
 syllabus. Although we began the semester with the university open for socially distant
-face-to-face learning, that has since ended and we have pivoted to online instruction only for
+face-to-face learning, that has since ended, and we have pivoted to online instruction only for
 our undergraduate students.
 
-Furthermore, so that we could provide students with a hands-on experience, we developed lab
-kits with supplies that allowed the students to perform the investigations outside the teaching
-laboratory. We purchased the lab kit items in collaboration with our campus bookstore, and the
+We developed lab kits with supplies that allowed students to perform the investigations outside the teaching
+laboratory so we could provide students with a hands-on experience. We purchased the lab kit items in collaboration with our campus bookstore, and the
 students purchased the lab kits from the bookstore. We ordered lab kit items in bulk and where
-possible directly from manufacturers to reduce the costs of the items. Each General Physics
-Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each General Physics Laboratory II
-kit costs \$39.00. And we have students paying for these kits in place of a physical lab
+possible directly from manufacturers to reduce the costs of the items. Each Physics 1
+kit cost \$20.60 and each Physics 2
+kit cost \$39.00. Students payed for these kits in place of a lab
 manual, which we provide online for this course.  The online adaptation of the face-to-face ADI
-curriculum has remained unchanged --- pre-labs are done in small groups asynchronously,
-proposals are developed in larger groups asynchronously, and argumentation sessions are
-scheduled and occur via WebEx.
+curriculum has changed slightly. Pre-labs are done in groups asynchronously.
+Proposals are developed in groups during the lab period, and scheduled argumentation sessions occur via WebEx during the lab period.
 
 \section{Discussion}
-We have observed a great number of successes for these transformations.  First and foremost, is
-that we indeed have a lab curriculum that is aligned with national goals and
+We have observed a great number of successes for these transformations.  First and foremost, we indeed have a lab curriculum that is aligned with national goals and
 standards. Furthermore, we have successfully deployed this online with both short and longer
-planning times.  Students are indeed engaging with science practices as determined by our
+planning times.  Students are engaging with science practices as determined by our
 practical assessments, and our department culture around laboratory course instruction is
@@
 key factors for success in online learning environments, which were a barrier for many of our
-students.  Indeed our institution's center for survey research has published some findings that
-explain some of our observed issues.\citep{ECUcovidSurvey} The GTAs and students found
-communication about proposals much more difficult online than in face-to-face classes.  Indeed,
-about 10-20\% of our students did not have reliable internet access after the transition to
-online learning in the spring.\citep{ECUcovidSurvey} Also, up to 8\% of students did not have
-access to a computer once they left campus.\citep{ECUcovidSurvey} Additionally, we noticed that
+students.  Our institution's Center for Survey Research has published some findings that
+explain some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
+communication about proposals much more difficult online than in face-to-face classes.
+About \SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access after the transition to
+online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up to \SI{8}{\percent} of students did not have
+access to a computer once they left campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that
 some students in the course did not have access to computers capable of running \emph{Tracker}
@@
 assigned groups.  Once they left campus, many students found they had increased work or school
-responsibilities (42.1\%) or additional family responsibilities (59.0\%).\citep{ECUcovidSurvey}
+responsibilities (\SI{42.1}{\percent}) or additional family responsibilities (\SI{59.0}{\percent}).\citep{ECUcovidSurveyRedacted}
 We removed non-participating students from groups and gave them an opportunity to make up their
@@
 Finally, we hope these changes will be meaningful long-term as a lack of online labs is also a
-barrier for distance education students' completion of a degree.  So online lab curricula would
+barrier for distance education students' completion of a degree so online lab curricula would
 fill an institutional need.

### 2020-09-04 manuscript/onlineLabPaper.tex
Minor changes to mask self references.

@@
 \section{Introduction}
-A significant challenge facing physics faculty face teaching introductory labs is engaging students in authentic science practices.  Another has been
-highlighted given the current global pandemic---how to engage students in our
-laboratory courses while maintaining appropriate social distancing and hygiene standards. We
-have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
-rationale behind the first transformation to a practice-focused curriculum.  In March 2020
-we needed to transform our labs again, this time to accommodate online
-learning. This paper discusses two chief questions: ``What are we doing to engage students in
-science practices?'' and ``How did we make all of this work online?''
+A significant challenge facing physics faculty face teaching introductory labs is engaging
+students in authentic science practices.  Another has been highlighted given the current global
+pandemic---how to engage students in our laboratory courses while maintaining appropriate
+social distancing and hygiene standards. We have chosen to answer these challenges by
+transforming our labs\ldots\ twice. We discuss the rationale behind the first transformation to
+a practice-focused curriculum.  In March 2020 we needed to transform our labs again, this time
+to accommodate online learning. This paper discusses two chief questions: ``What are we doing
+to engage students in science practices?'' and ``How did we make all of this work online?''
 
@@
 aspects of the transformation especially important for research such as curricular
-implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.
+implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.
 
@@
 and the semester ends with a practical exam where students engage in this process on a
-shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental materials
+shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental materials
 with more details about each of the labs in our curriculum.

### 2020-09-26 manuscript/onlineLabPaper.tex
Updated manuscript draft, and edited the supplement.  Needs more work, but should be ready for review in the next few days.

@@
 A significant challenge facing physics faculty face teaching introductory labs is engaging
-students in authentic science practices.  Another has been highlighted given the current global
-pandemic---how to engage students in our laboratory courses while maintaining appropriate
-social distancing and hygiene standards. We have chosen to answer these challenges by
-transforming our labs\ldots\ twice. We discuss the rationale behind the first transformation to
-a practice-focused curriculum.  In March 2020 we needed to transform our labs again, this time
-to accommodate online learning. This paper discusses two chief questions: ``What are we doing
-to engage students in science practices?'' and ``How did we make all of this work online?''
+students in authentic science practices.\citep{national2007Rising,PCAST12,kozminski2014aapt}
+Another has been highlighted given the current global pandemic---how to engage students in our
+laboratory courses while maintaining appropriate social distancing and hygiene standards. We
+have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
+rationale behind the first transformation to a practice-focused curriculum.  In March 2020 we
+needed to transform our labs again, this time to accommodate online learning. This paper
+discusses two chief questions: ``What are we doing to engage students in science practices?''
+and ``How did we make all of this work online?''
 
@@
 The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
-The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment and techniques used by students was outdated---triple beam balances and hand-drawn graphs were
-standard.  That same year, as part of an interdisciplinary team interested in engaging
-students in and assessing scientific practices, we secured
-funding, both internally and from the NSF, to change this \emph{status quo} in physics, biology, and
-chemistry.  All three departments transformed their labs using the Argument Driven Inquiry (ADI),\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has
-been specifically designed to engage students in authentic science practices. In physics, we
-also utilized the AAPT Lab Recommendations to guide our transformation.\citep{kozminski2014aapt}
+The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment and
+techniques used by students was outdated---triple beam balances and hand-drawn graphs were
+standard.  That same year, as part of an interdisciplinary team interested in engaging students
+in and assessing scientific practices, we secured funding, both internally and from the NSF, to
+change this \emph{status quo} in physics, biology, and chemistry.  All three departments
+transformed their labs using the Argument Driven Inquiry
+(ADI)\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has been
+specifically designed to engage students in authentic science practices. In physics, we also
+utilized the AAPT Lab Recommendations to guide our transformation.\citep{kozminski2014aapt}
 
-We were satisfied with our progress when the global COVID-19 pandemic forced a shutdown in March 2020.  With students off campus, we had to abruptly
-shift our delivery to an online format and quickly realized that many of the face-to-face activities  had to be adapted to online use.  Going forward, we have
-further adapted what we are doing so that students can still participate in a hands-on
-laboratory experience in an online laboratory course.
+We were satisfied with our progress when the global COVID-19 pandemic forced a shutdown in
+March 2020.  With students off campus, we had to abruptly shift our delivery to an online
+format and quickly realized that many of the face-to-face activities had to be adapted to
+online use.  Going forward, we have further adapted what we are doing so that students can
+still participate in a hands-on laboratory experience in an online laboratory course.
 
@@
 
-Regional State University is a public doctoral granting university in a rural, economically
-depressed part of our state.  The university mission is focused on regional transformation and
-service to this region.  The total combined student population in Fall 2019 was 28,651 largely
-comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and Physics
-\textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These courses serve
-both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of
-the students who take our lab course are in (or have taken) the corresponding Algebra-based
-physics lecture course. These labs also fulfill the general education requirement for science
-lab courses at our university.
+% Regional State University is a public doctoral granting university in a rural, economically
+% depressed part of our state.  The university mission is focused on regional transformation and
+% service to this region.  The total combined student population in Fall 2019 was 28,651 largely
+% comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and Physics
+% \textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These courses serve
+% both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of
+% the students who take our lab course are in (or have taken) the corresponding Algebra-based
+% physics lecture course. These labs also fulfill the general education requirement for science
+% lab courses at our university.
 
@@
 questions. Students received credit for giving presentations, asking meaningful questions, and
-responding to questions.  Following the argumentation session students submitted individual
+responding to questions.  Following the argumentation session, students submitted individual
 draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
@@
 
-We developed lab kits with supplies that allowed students to perform the investigations outside the teaching
-laboratory so we could provide students with a hands-on experience. We purchased the lab kit items in collaboration with our campus bookstore, and the
-students purchased the lab kits from the bookstore. We ordered lab kit items in bulk and where
-possible directly from manufacturers to reduce the costs of the items. Each Physics 1
-kit cost \$20.60 and each Physics 2
-kit cost \$39.00. Students payed for these kits in place of a lab
-manual, which we provide online for this course.  The online adaptation of the face-to-face ADI
-curriculum has changed slightly. Pre-labs are done in groups asynchronously.
-Proposals are developed in groups during the lab period, and scheduled argumentation sessions occur via WebEx during the lab period.
+We developed lab kits with supplies that allowed students to perform the investigations outside
+the teaching laboratory so we could provide students with a hands-on experience. We purchased
+the lab kit items in collaboration with our campus bookstore, and the students purchased the
+lab kits from the bookstore. We ordered lab kit items in bulk and where possible directly from
+manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
+Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
+provide online for this course.  The online adaptation of the face-to-face ADI curriculum has
+changed slightly. Pre-labs are done in groups asynchronously.  Proposals are developed in
+groups during the lab period, and scheduled argumentation sessions occur via WebEx during the
+lab period.
 
 \section{Discussion}
-We have observed a great number of successes for these transformations.  First and foremost, we indeed have a lab curriculum that is aligned with national goals and
-standards. Furthermore, we have successfully deployed this online with both short and longer
-planning times.  Students are engaging with science practices as determined by our
-practical assessments, and our department culture around laboratory course instruction is
-invigorated. Psychometric assessment of our students engagement with science practices is
-ongoing.
+We have observed a great number of successes for these transformations.  First and foremost, we
+indeed have a lab curriculum that is aligned with national goals and standards. Furthermore, we
+have successfully deployed this online.  Students are engaging with science practices as
+determined by our practical assessments, and our department culture around laboratory course
+instruction is invigorated. Psychometric assessment of our students engagement with science
+practices is ongoing.
 
@@
 explain some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
-communication about proposals much more difficult online than in face-to-face classes.
-About \SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access after the transition to
-online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up to \SI{8}{\percent} of students did not have
-access to a computer once they left campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that
-some students in the course did not have access to computers capable of running \emph{Tracker}
-or \emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not
-Chromebooks or mobile devices. We discovered \emph{jsTrack}\citep{jstrack}, an online
-Javascript web application for video analysis that runs on most computers including
-Chromebooks, but not mobile devices.
+communication about proposals much more difficult online than in face-to-face classes.  About
+\SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
+after the transition to online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up
+to \SI{8}{\percent} of students did not have access to a computer once they left
+campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that some students in the course
+did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of
+which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices. We
+discovered \emph{jsTrack}\citep{jstrack}, an online Javascript web application for video
+analysis that runs on most computers including Chromebooks, but not mobile devices.
 
@@
 assigned groups.  Once they left campus, many students found they had increased work or school
-responsibilities (\SI{42.1}{\percent}) or additional family responsibilities (\SI{59.0}{\percent}).\citep{ECUcovidSurveyRedacted}
-We removed non-participating students from groups and gave them an opportunity to make up their
-missed work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
-completed their work.
+responsibilities (\SI{42.1}{\percent}) or additional family responsibilities
+(\SI{59.0}{\percent}).\citep{ECUcovidSurveyRedacted} We removed non-participating students from
+groups and gave them an opportunity to make up their missed work asynchronously. Less than
+\SI{50}{\percent} of the students in the make-up groups completed their work.
 

### 2020-09-26 supplement/supplement.tex
Updated manuscript draft, and edited the supplement.  Needs more work, but should be ready for review in the next few days.

@@
 
-\section{Face-to-face implementation}
-
-Activities and basic equipment.
-
-Assessment practices and discussion of results.
-
-\section{Online implementation}
-
-Curricular adaptation.
-
-Kit contents.
-
-\section{Introduction}
-There are many challenges that physics faculty face when teaching introductory labs. One of
-these challenges is engaging students in authentic science practices.  Another has been
-highlighted given the current global pandemic---specifically how to engage students in our
-laboratory courses while maintaining appropriate social distancing and hygiene standards. We
-have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
-rationale behind the first transformation to a practice-focused curriculum.  However, when
-March 2020 rolled around we needed to transform our labs again, this time to accommodate online
-learning. This paper discusses three chief questions: ``Why did we change?'' ``What are we
-doing to engage students in science practices?'' and ``How did we make all of this work
-online?''
-
-Scientific truth is discovered through the practice of doing science.  \citeauthor{DBERreport}
-state, ``Without [scientific] investigative practices, there would be no new scientific and
-engineering knowledge.''\citep{DBERreport} Too often, our laboratory courses do not
-meaningfully engage students in scientific practices, instead reproducing classical
-experiments.\citep{PCAST12} This is part of a long-standing tradition of calling for authentic
-engagement in scientific practices which pre-dates Lorentz transformations.\citep{AAAS1881}
-Indeed, back in \citeyear{AAAS1881}, the AAAS stated our goals quite succinctly, ``[Typical
-courses in t]he sciences\ldots are not made the means of cultivating the observing powers,
-stimulating inquiry, exercising the judgment in weighing evidence, nor of forming independent
-habits of thought.''\citep{AAAS1881}
-
-The physics labs at our institution in the Fall of 2016 very much mirrored the national
-narrative.  The lab curriculum had been largely unchanged for about 20 years, and followed the
-traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
-outdated---triple beam balances and hand-drawn graphs were standard.  In the same year, as part
-of an interdisciplinary team interested in engaging students in scientific practices as well as
-assessing those scientific practices, we secured funding, both internally and from the NSF, to
-change this status quo in physics, biology, and chemistry.  All three departments transformed
-their labs using a pedagogical framework entitled, Argument Driven Inquiry
-(ADI),\citep{Sampson2011,Walker2011,Walker2016} which has been specifically designed to engage
-students in authentic science practices. We will focus on the physics transformation in this
-paper.
-
-We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
-shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly
-shift our delivery to an online format and quickly realized that some of the activities that we
-utilized in the face-to-face sections had to be adapted to online use.  Going forward, we have
-further adapted what we are doing so that students can still participate in a hands-on
-laboratory experience in an online laboratory course.  We hope these changes will be meaningful
-long-term as a lack of online labs is also a barrier for distance education students'
-completion of a degree.  So online lab curricula would fill an institutional need.  In the next
-sections, we will discuss our institutional and instructional contexts and describe each
-transformation in more detail.
-
-\section{Instructional Context}
+\section{Additional instructional context}
 
@@
 \section{Transformation \#1: Argument Driven Inquiry}
-Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
-in school better match what actually transpires in authentic research settings
-\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
-answer questions, or measure quantities, that are well-known using procedures that have been
-refined over time.  For example, in physics we often have students measure $g$ using a
-well-known method (such as a spark timer).  In ADI labs, we give students a question to answer
-(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''), allow them
-to design a procedure for an experiment that will answer that question, collect and analyze
-their data, and make claims based on their data.  We accomplish this by having students engage
-in a three-part cycle:
-\begin{itemize}
-  \item Pre-Lab - Introducing the context
-  \item Proposal Development and Data Collection
-  \item Argumentation and Peer Review
-\end{itemize}
-In the sections below, we will comment on each part of the cycle, focusing on both students and
-GTAs.
+\subsection{Physics \textrm{I} Investigation 1}
 
-\subsection{Session 1: Pre-Lab}
-Part of the goal of any laboratory is to help students develop a familiarity with certain tools
-and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
-students familiarity with the equipment they will be using.  For the investigation described
-previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  we need
-students to become familiar with a few things, such as what we mean by a cart, and give them
-some tools that they need to be able to answer this question.  As a part of the pre-lab
-reading, students are given information about linear regression---both how to run it in Excel,
-and how to interpret the output, and how we can estimate instantaneous velocity given position
-vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
-them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
-collect position vs.\ time data for this motion.  Students work in pairs to do this work, and
-turn in a brief summary of this work on the course management system.  For this investigation,
-it is the first time that they create graphs, so we set norms for graphing such as helping them
-decide which variable to put on the x-axis and the y-axis as well as including units.  Pre-lab
-assignments are designed to be graded in less than 1 minute/paper based on a rubric we provide
-to both students and GTAs.
+\subsection{Physics \textrm{I} Investigation 2}
 
-\subsection{Session 2: Proposal Development and Data Collection}
-During this session, students work in groups of 4 to develop a proposal, get it approved by a
-GTA, and then collect and analyze their data.  We have a format for proposal development that
-asks students to link the scientific concept being studied---in this example case, Newton's
-Second Law---to the data that they will collect.  Students also need to propose a plan for
-analyzing their data and minimizing potential sources of error (such as friction).  Once
-students have an approved proposal, they begin collecting and analyzing their data.  This may
-lead them to refine or revise their method (which they are encouraged to do).  Grading for the
-GTAs this week is minimal (full credit for completing the proposal).  However, this is the most
-critical week's for GTA training.  GTAs have to be clear that the goal is to allow a diverse
-number of ways of collecting/analyzing this data.  How much does the mass of the cart need to
-vary?  How many different cart masses do the students need to take?  How should students deal
-with friction? All of these are questions that we want the \textit{students} to answer.  And in
-some sense, we will be disappointed if all of the students come up with the same answer.
-Experimental methods certainly have an impact on experimental results.
+\subsection{Physics \textrm{I} Investigation 3}
 
-\subsection{Session 3: Argumentation and Peer Review}
-During this session, the students begin by sharing their results.  Students finish analyzing
-their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
-the group stays at the whiteboard while the other group members (travelers) go to other groups.
-The travelers learn what other groups did, and compare to their results in a structured
-argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they
-see at least 3 other posters.  After the travelers return, critically, the groups spend time
-discussing what they saw and reflecting on their own results.  What is exciting is that
-sometimes, these interactions actually drive groups to change their claims \citep{Walker2019}.
+\subsection{Physics \textrm{I} Investigation 4}
 
-Each student writes a shortened lab report consisting of three sections: an introduction to the
-scientific concept, a description of the experimental method or procedure, and a discussion
-section laying out their results and the evidence and justification supporting their results.
-The authors have created different peer review calibration videos for the students to watch so
-they can look for the same things that we are going to be grading them on when we get their
-final reports.  Students complete their lab report and submit it by the end of the day.  Then,
-students take part in double-confidential peer review.  We facilitate this online.  They read
-and reply to two different lab reports.  Finally, they get their feedback and use this to
-revise their own lab report.  At the end of this week, students turn in their revised,
-peer-reviewed final lab report.  This is the heaviest week of GTA grading.  We provide a rubric
-for lab report grading, and each lab report generally takes about 3-5 minutes to grade.
+\subsection{Physics \textrm{II} Investigation 1}
+
+\subsection{Physics \textrm{II} Investigation 2}
+
+\subsection{Physics \textrm{II} Investigation 3}
+
+\subsection{Physics \textrm{II} Investigation 4}
 
@@
     block schedule.}
-  \begin{ruledtabular}
   \begin{tabular}{ccp{28em}}
+    \hline\hline
     Investigation & Topic & Guiding Question\\
@@
     2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
-      3 & 2-D collisions & Is the collision between two marbles elastic?
+    3 & 2-D collisions & Is the collision between two marbles elastic? \\
+    \hline\hline
   \end{tabular}
-  \end{ruledtabular}
 \end{table}
@@
     block schedule.}
-  \begin{ruledtabular}
   \begin{tabular}{ccp{26em}}
+    \hline\hline
     Investigation & Topic & Guiding Question\\
@@
     2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
-      3 & Diffraction of light & Are hairs from different people the same diameter?
+    3 & Diffraction of light & Are hairs from different people the same diameter? \\
+    \hline\hline
   \end{tabular}
-  \end{ruledtabular}
 \end{table}
@@
     1 & Mini screwdriver for multimeters & 1,2 \\
-    5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
+    5 & \SI{500}{mA} fuses for multimeters & 1,2 \\
     4 & Alligator clip leads & 1, 2 \\
@@
 
-\section{Conclusion}
-Discussion Points:
-\begin{itemize}
-  \item What have been our successes?  (Related to both Transformations)
-  \item What have been our challenges?
-  \item What plans do we have for online labs in the future?
-\end{itemize}
-
-\begin{acknowledgments}
-  Redacted for review.% This work has been supported by the NSF (Award \# 1725655).
-\end{acknowledgments}
+\clearpage
 

### 2020-10-02 supplement/supplement.tex
Finished experiment summaries for supplement.  Needs another set of eyes before sending off to TPT.

@@
 
-\section{Curriculum development timeline}
-Talk about the curriculum development, and how departmental culture around the labs changed as
-a part of this transformation.
+This supplement is meant to accompany the paper, \textit{Introductory Physics Labs: A Tale of
+  Two Transformations} being submitted to \textit{The Physics Teacher}.  It is divided into the
+following sections:
+\begin{description}
+  \item[Additional Instructional Context] discusses some particulars of our department and
+  institution that can help the reader put the scope and population of the intervention into
+  context.
+  \item[Transformation \#1: Argument Driven Inquiry] provides a brief summary of each of the
+  experiments done in the face-to-face version of this lab course.
+  \item[Transformation \#2: Online delivery] provides a summary of how we adapted or created
+  new activities for students to do their labs online, and discusses some of the ways that we
+  supported authentic experimentation in this online environment.
+\end{description}
 
@@
 \section{Transformation \#1: Argument Driven Inquiry}
+In each of the sections below, we provide a brief summary of the ADI curriculum that we have
+implemented in our physics labs.  We will discuss the pre-lab reading, which students are
+expected to complete before they arrive in lab.  We also discuss the supplies that we use,
+especially when they are novel.  Every experiment requires a computer for data analysis.
+However, most supplies that we use are found in a typical college physics lab, although this
+isn't universally true.  (We do a radioactive decay lab that utilizes a PuBe neutron source.)
+We will also discuss some common approaches used by students in the activity.
+
+One last thing of note: Oftentimes, we have made choices that give students a significant
+hurdle to overcome (e.g., you can't neglect friction).  Student data should be messy.  There
+should be some things that are unclear.  When we teach physics labs, we can give our students
+the illusion that lab science is done by following well-known procedures and produce pristine
+data. However, the opposite can often be true. As you read some of these descriptions, you
+probably will think of 10 ways that the experiments could be done, ``better''---be it with
+different techniques or equipment.  That is the point.  We want to give students an idea to
+start with, and then give them the freedom to make changes, try things out, and figure out
+their own way of knowing.
+
 \subsection{Physics \textrm{I} Investigation 1}
+\begin{description}
+  \item[Pre-lab reading] We provide a brief introduction to statistics, defining the terms
+  average, standard deviation, and standard error.  We also discuss how to calculate those
+  quantities in Excel.  We have a traditional discussion of how to use a ruler to measure
+  distances, and end with a brief introduction to free-fall.
+  \item[Pre-lab activity] We divide the room in half and have them measure the heights of all
+  students, comparing the average heights of the students on the ``right'' and on the ``left''
+  of the room.  We have them use a simple rule to compare their measurements, if the value
+  $\pm$ uncertainty (standard error) overlaps for these measurements, then the measurements
+  agree, otherwise, they disagree.
+  \item[Supplies of note] Meter sticks and 2-meter sticks.
+  \item[Argumentation Question] Do two people have the same reaction time?
+  \item[Common student approaches] Most students drop meter sticks and catch them.  They
+  measure the distance that the stick falls, and use the free-fall equation to relate distance
+  fallen to time in free-fall.  Some find one of the myriad apps out there that will measure
+  reaction time, such as the one at \url{https://humanbenchmark.com/}.  Note, not all apps are
+  created equal.  
+\end{description}
 
 \subsection{Physics \textrm{I} Investigation 2}
+\begin{description}
+  \item[Pre-lab reading] We talk about how ultrasonic motion detectors work (schematically, not
+  technically, and discuss how to calculate velocity from discrete position vs. time data. We
+  finally discuss linear regression, how to interpret it on a basic level, and how it can be
+  calculated in Excel.\footnote{Because we want our fit values to have uncertainties, we have
+    our students install the \textit{Data Analysis Toolpack} if they are using Excel.}
+  \item[Pre-lab activity] We give the students a cart and a track, have them incline that
+  track, and have them measure the net force on the cart as it moves on the track.
+  \item[Supplies of note] Ultrasonic motion detector, various masses, carts (with fan
+  attachments), and a track.
+  \item[Argumentation Question] Does the force that the fan exerts depend on the mass of the
+  cart?
+  \item[Common student approaches] Students measure the net force of a cart moving on a flat
+  track under the influence of a fan several times, changing the mass of the cart each time.
+  One particular struggle that students have is that they do not take friction into account,
+  which is not negligible on this setup.
+\end{description}
 
 \subsection{Physics \textrm{I} Investigation 3}
+\begin{description}
+  \item[Pre-lab reading] We discuss strategies for linearizing non-linear data for well-known
+  cases.
+  \item[Pre-lab activity] We have the students measure the period of oscillation for a mass
+  spring system, linearizing the data two ways, and comparing the spring constant for each of
+  these analyses.
+  \item[Supplies of note] Masses, springs, hangars, and a coiled snake (a spring with a
+  non-negligible mass).
+  \item[Argumentation Question] When does the spring's mass matter?
+  \item[Common student approaches] Students use the traditional measure the time of 10
+  oscillations and divide approach.  Other than that, experimental approaches are fairly
+  uniform.  Different approaches to student analysis techniques are common and encouraged.
+\end{description}
 
 \subsection{Physics \textrm{I} Investigation 4}
+\begin{description}
+  \item[Pre-lab reading] We discuss collisions, and define momentum and kinetic energy.
+  \item[Pre-lab activity] We have students analyze the motion of two objects on a video.  We
+  have students use \textit{Tracker}\citep{bro2009} to quantify that motion.  Students then
+  compare the motion of those two objects.
+  \item[Supplies of note] Marbles and a meter stick.  And the students phones.  (We thought
+  about getting a video camera for students to use, but realized that students already had one,
+  and that camera already has a number of features built into it---such as picture
+  steadying---that getting our own wasn't worth the effort.)
+  \item[Argumentation Question] Is the collision between two marbles elastic?
+  \item[Common student approaches] Students simply let marbles collide and videotape the
+  action. Many of the problems here are on the data analysis end.  Friction is a killer here,
+  and is an issue that students deal with differently in their data analyses.
+\end{description}
 
 \subsection{Physics \textrm{II} Investigation 1}
+\begin{description}
+  \item[Pre-lab reading] We review current, voltage, and resistance.  We also discuss how to
+  use a multimeter.
+  \item[Pre-lab activity] Measure the I-V curve of a resistor.
+  \item[Supplies of note] Multimeters (2), lightbulb, resistor, power supply.
+  \item[Argumentation Question] Does a lightbulb behave like a resistor?
+  \item[Common student approaches] Students measure an I-V curve.  Sometimes the data is
+  sort-of linear $(R^2\sim 0.9)$, and students have to deal with that.
+\end{description}
 
 \subsection{Physics \textrm{II} Investigation 2}
+\begin{description}
+  \item[Pre-lab reading] Students read about capacitance and voltage and are reminded
+  \item[Pre-lab activity] Students measure the time constant for a RC circuit.
+  \item[Supplies of note] We have created several RC circuit kits that are integrated so that
+  the time constant is similar for all of the circuits without the bulb, then students can
+  throw a switch to add a bulb to the circuit in series.  When added into the circuit, some of
+  the bulbs light up, others do not. Multimeter, timer, power supply.
+  \item[Argumentation Question] How does adding a light bulb in series change the behavior of a
+  RC circuit?
+  \item[Common student approaches] Measure the time constant for their kit.  See if $\tau$
+  changes from the prelab.
+\end{description}
 
 \subsection{Physics \textrm{II} Investigation 3}
+\begin{description}
+  \item[Pre-lab reading] Students get a reading about diffraction and Babinet's principle.
+  \item[Pre-lab activity] Students use one laser of known wavelength to measure a slit's width,
+  then they use the same slit to measure the wavelength of an unknown laser.
+  \item[Supplies of note] Optical bench, slit, lasers, screen.
+  \item[Argumentation Question] Are hairs from different people the same diameter?
+  \item[Common student approaches] Measure diffraction pattern of two hairs, use that to find
+  the thickness of each and compare.
+\end{description}
 
 \subsection{Physics \textrm{II} Investigation 4}
+\begin{description}
+  \item[Pre-lab reading] Discussion of nuclear decay and Geiger counters.
+  \item[Pre-lab activity] Students measure the ``decay constant'' of dice.
+  \item[Supplies of note] We use a PuBe source to irradiate some copper pennies, and a geiger
+  counter to measure the decay.
+  \item[Argumentation Question] What isotope is most common in the nuclear decay of a penny?
+  \item[Common student approaches] Students set up an appropriate enclosure and collect nuclear
+  activity data.  The issue here is that copper has a double decay (two common isotopes), and
+  the answer isn't straightforward.
+\end{description}
 
@@
 argumentation session the following week. The first slide was a description of their
-measurements. Te second slide was a presentation of the results, including a graph or table,
+measurements. The second slide was a presentation of the results, including a graph or table,
 and the third slide was their argument, based on their result.

### 2020-10-07 manuscript/onlineLabPaper.tex
Small typographic changes to main MS

@@
 
-Labs are supervised by Author 2, but sections are run by Graduate GTAs (GTAs). The
+Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The
 transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
@@
 
-The argumentation session was held in a scheduled Cisco WebEx session
+The argumentation session was held in a scheduled WebEx session
 the week after the proposal session. Before this session, each group was required to complete
@@
 the lab kit items in collaboration with our campus bookstore, and the students purchased the
-lab kits from the bookstore. We ordered lab kit items in bulk and where possible directly from
+lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly from
 manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each

### 2020-10-07 supplement/supplement.tex
Edits to supplement.

@@
 service to this region.  The total combined student population in Fall 2019 was 28,651 largely
-comprised of undergraduates (23,081).Our physics labs (Physics 1 lab and Physics 2 lab) are
+comprised of undergraduates (23,081).  Our physics labs (Physics 1 lab and Physics 2 lab) are
 each 1 credit courses that meet for 2 hours per week. These courses serve both of our
@@
 
-Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
+Labs are supervised by Author 2, but each section is run by Graduate TAs (GTAs). The
 transformed curriculum was jointly written by both of the authors.  GTA training was greatly
@@
 as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
-weekly prep meeting with the GTAs, and SFW and the research team have supervised various
+weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
 aspects of the transformation especially important for research such as curricular
@@
     1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
-    2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
-    3 & 2-D collisions & Is the collision between two marbles elastic? \\
+    2 & 2-D collisions & Is the collision between two marbles elastic? \\
+    3 & Periodic motion & What is the nut position for which the physical pendulum small-angle period is minimum, and what is the power-law regression equation for the period of the system? \\
     \hline\hline
@@
     1 & Protractor & 1 \\
-    2 & \SI{25}{mm} marble & 1, 3 \\
+    2 & \SI{25}{mm} marble & 1, 2 \\
     1 & Tape measure with cm scale & 1, 2, 3\\
-    1 & \SI{0.6}{m} threded rod & 2 \\
-    1 & Eye nut & 2 \\
-    3 & Nuts & 2 \\
-    1 & Door hook & 2 \\
-    1 & \SI{1}{m} string & 2 \\
-    1 & \SI{16}{mm} marble & 3 \\
+    1 & \SI{0.6}{m} threded rod & 3 \\
+    1 & Eye nut & 3 \\
+    3 & Nuts & 3 \\
+    1 & Door hook & 3 \\
+    1 & \SI{1}{m} string & 3 \\
+    1 & \SI{16}{mm} marble & 2 \\
     \hline\hline
@@
 kit items in bulk and where possible directly from manufacturers to reduce the costs of the
-items. Each General Physics Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each
+items. Each General Physics Laboratory I kit costs \$20.60, and each
 General Physics Laboratory II kit costs \$39.00. Table \ref{tab: 1251 lab kit} shows the lab

### 2020-10-07 supplement/supplement.tex
Fixed self citation and removed Cisco from WebEx.

@@
 method for online collaboration in which everyone in the group could participate. Some groups
-used Cisco WebEx (video interaction platform licensed by our university) sessions, some used a
+used WebEx (video interaction platform licensed by our university) sessions, some used a
 group chat, and others used FaceTime or other online communication applications.
@@
 
-The argumentation session was held in a Cisco WebEx session during the lab session the week
+The argumentation session was held in a WebEx session during the lab session the week
 after the proposal session. One member of each group gave the presentation, which was followed

### 2020-10-29 planning/PhysicsOnlineLabPlan.tex
Added PICUP slides to this repository and updated readme to reflect the more general nature of items in this repository.

\documentclass[11pt, oneside]{article}   	
\usepackage[letterpaper, margin=1in]{geometry}  
\usepackage[parfill]{parskip}  
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}

%SetFonts

%SetFonts

\begin{document}
\begin{center}
{\Large Plan for PHYS 1251 and PHYS 1261 Online Labs}\\
Spring 2020
\end{center}

\section{Introduction}

Due to the Coronavirus pandemic, ECU has added an additional week to spring break and moved classes online indefinitely.  The introductory physics laboratories are no exception to this.  This document contains plans to move the remainder of the Spring 2020 labs online and to make up for a lost week of instruction.

The PHYS 1251 and 1261 laboratories have completed the Investigation 3 (I-3) Pre-Lab.  This means there are six remaining in-class activities in the semester: the I-3 Proposal, I-3 Argumentation, I-4 Pre-Lab, I-4 Proposal, I-4 Argumentation, and the Practical Exam.  After the extended spring break, there are five weeks remaining in the semester.  This means that we must either compress the schedule by combining activities or reduce the number of activities.

Online activities can be synchronous, where the students interact in real time, or asynchronous, where the students must complete tasks or assignments by a deadline on their own.  This plan consists of a combination of synchronous and asynchronous activities to allow the students to interact in the ADI format online.

\section{Investigations}

Under normal circumstances, each investigation consists of three face-to-face sessions---Pre-Lab, Proposal, and Argumentation---followed by an online peer review. Following the peer review, students submit their final reports for grading.

\subsection{Pre-Lab}

There is one remaining Pre-Lab in the semester.  The I-4 Pre-Labs in both PHYS 1251 and PHYS 1261 could be completed online.

In PHYS 1251, the Pre-Lab is a video analysis problem that uses the Tracker program to determine the velocity of a cart.  Since the Tracker program is available on most computer platforms, students could complete this outside the laboratory and submit their Pre-Lab reports online.  The Pre-Lab groups should coordinate this activity, but it could be completed asynchronously.

In PHYS 1261, the Pre-Lab is a simulation of radioactive decay using dice.  A Trinket simulation of the dice rolling activity has been developed and added to the course Canvas.  Students can run the simulation on any standards-compliant browser, including browsers on mobile devices.  The Pre-Lab groups should coordinate this activity, but it could be completed asynchronously.

\subsection{Proposal/Data Collection}

During the proposal session the lab groups must develop a proposal that must be approved by the TA before they can begin collecting data.  It is important for the students to interact with each other to form the proposal and then receive feedback form the TA about what the proposal lacks.  In the end, each group should have an approved proposal that serves as a roadmap for the rest of the investigation.

Most of the proposal development can occur asynchronously with timely TA interaction.  These are the suggested steps.

\begin{enumerate}
\item Each investigation group participates in a group discussion on Canvas to develop the proposal.  The group must form a draft proposal by a certain deadline (1 hour after the start of the lab period).

\item At that proposal draft deadline time the TA will read the proposals from each group and offer feedback in the discussion. The TA will give the groups without approved proposals 15 minutes to revise their proposals.

\item The TA will revisit the group discussions to either approve or suggest revisions to the proposals (using guiding questions).  Each group must have an approved proposal before they can continue to the data collection phase.

\item Each group will be given a set of data to analyze in order to answer the guiding question.  The TAs and instructors will collect several data sets in advance, and each group in a lab section will be assigned a different data set.  Where possible, the data will be in raw form, such as video of a mass oscillating on a spring, to allow the students to make measurements as well as decisions about what is important.

\item Students will be expected to analyze their data collaboratively and asynchronously.
\end{enumerate}

\subsection{Argumentation}

The argumentation session is the portion of the investigation that will take place synchronously.

\begin{enumerate}
\item Each group will prepare a three-slide PowerPoint (PPT) presentation.
    \begin{description} 
    \item[Slide 1:] Summary of the procedure used to collect and analyze data.  
    \item[Slide 2:] Data/analysis including graphs, calculations, and tables used to justify the argument.  
    \item[Slide 3:] Discussion/conclusion that answers the guiding question using the data as justification.
    \end{description}

\item The argumentation session will occur on WebEx. The students will access in through Canvas.  The TA will begin the argumentation session at 30 minutes after the lab start time.

\item Each group will provide one presenter, and the other students will be travellers.  Each presenter will present the group's PPT ``poster'' and take questions from the travellers. This will continue until every group has presented results.

\item The WebEx session will be recorded.  Students with excused absences will be given access to the recordeind and asked to write a paragraph about what they learned from it.

\item After the argumentation session, each group will be required to discuss what they learned on the group discussion board.  Groups may take more data if desired.
\end{enumerate}

\subsection{Peer Review and Report Submission}

The peer review and report submission phase will not be changed.

\section{Schedule}

Since we are losing one week of lab, the I-4 Pre-Lab will be an asynchronous homework assignment due at the beginning of the I-4 Proposal session.

\section{Practical Exam}

It is important that the practical exam include investigation design by the students.  This must be preserved if the students do their exams online.  One option is to video a large set of data and have the students ask the TA for the specific data they need.  The TA can then give them access to the appropriate videos or data sets.

\section{To Do}
This is a list of logistical items that we must handle before we are ready.

\begin{enumerate}
\item Communicate plan and expectations to students.
\item Devise a method to ensure student participation.
\item Have students install appropriate software to participate in WebEx.
\item Collect data sets and devise a scheme to distribute them to students.
\item Plan for students who are unable to connect or participate for various reasons (connectivity, illness, \emph{etc}.).
\item ...
\end{enumerate}

\end{document}

### 2020-11-13 readingDaySeminar/PICUP-ECULabs.tex
Adding a start to the reading day seminar we are giving at ECU.

\documentclass[aspectratio=169]{beamer}
% \usepackage{beamerthemesplit} % Activate for custom appearance
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[export]{adjustbox}
\usetheme{Boadilla}
\usecolortheme{seahorse}
\usefonttheme[stillsansseriflarge]{serif}
\title[ECU online labs]{Transition to online labs at ECU}
\author[Sprague and Wolf]{Mark W.\ Sprague and Steven F.\ Wolf}
\institute[ECU]{East Carolina University}
\date{\today}
\definecolor{ECUPurple}{RGB}{80,45,127}

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Physics labs at ECU in BC days}
\begin{center}
\only<1>{\includegraphics[page=1, height=3.in, valign=m]{PICUP1.pdf}}
\only<2>{\includegraphics[page=2, height=3in, valign=m]{PICUP1.pdf}}
\only<3>{\includegraphics[page=3, height=3in, valign=m]{PICUP1.pdf}}
\only<4>{\includegraphics[page=4, height=3in, valign=m]{PICUP1.pdf}}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Change of plans: Labs are online now.}
\begin{center}
\includegraphics[width=2in]{coronavirus.jpg}
\end{center}
\begin{itemize}
\item<1-> Preserve ADI format for last two investigations
\item<2-> How can we change our delivery while maintaining our focus on science practices?
\item<3-> What do we need to do together?
\begin{enumerate}
\item Proposal approval
\item Argumentation session
\end{enumerate}
\item<4-> What can we do apart?
\begin{enumerate}
\item Data collection (Both Prelab and Inquiry Investigation)
\item Data analysis
\item Peer review/lab report revision
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Implementing an ADI cycle--online delivery}
\begin{center}
\includegraphics[width=2in]{WebExArgumentation.png}\\
{\footnotesize Student presentation in WebEx argumentation session.}
\end{center}
\begin{itemize}
\item<+-> Students complete pre-lab before proposal session
\item<+-> Proposal session--WebEx/Discussion Boards; approval by end of class time
\item<+-> Measurements/Analysis--Group completes before next lab session
\item<+-> Argumentation--3 slide PPT on WebEx during class time
\item<+-> Peer Review--asynchronous, online (same as in BC times)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Measurements and Simulations}
\begin{center}
\includegraphics[width=2in]{Hair1_red_pattern.jpg}\\
{\footnotesize Image of diffraction pattern for student measurement.}
\end{center}
\begin{itemize}
\item Measurements online using photos and \href{run:Spring4_100g.mp4}{video}
\item Simulations on \emph{Trinket}
\end{itemize}
\end{frame}

%\begin{frame}
%\frametitle{Practical Exam and Beyond}
%
%\begin{tabular}{cc}
%\includegraphics[width=2.5in, valign=m]{TrinketCircuit.png} &
%%
%\begin{minipage}[m]{0.5\linewidth}
%\begin{itemize}
%\uncover<1->{\item Practical exam
%\begin{itemize}
%\item Canvas quiz--different versions
%\item Measurements on Trinket simulation
%\item Analyze data and write argument
%\end{itemize}
%}
%
%\uncover<2->{\item Beyond
%\begin{itemize}
%\item Summer classes online (need new labs)
%\item Online lab sections after we emerge?
%\item Online lab make-ups?
%\end{itemize}
%}
%\end{itemize}
%
%\end{minipage}
%
%\end{tabular}
%
%\end{frame}

\begin{frame}
\frametitle{Tools used in online lab delivery}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{cll}
\hline\hline
\textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
\hline
Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions }& University LMS\\
WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
Peergrade.io & \parbox[t]{2in}{\raggedright Online peer review} & \parbox[t]{2in}{\raggedright Anonymous reviews and feedback; better than Canvas}\\
Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} & Fine-grained control\\[3ex]
\hline\hline
\end{tabular}
\end{center}
\end{frame}

\end{document}

### 2020-11-13 2020fallNCSAAPT/sampleReactionTimeActivity/sampleADIactivity.tex
Uploaded the workshop that I gave to the NCS AAPT folks about ADI/Online labs.

\documentclass[11pt, oneside]{article}   	
\usepackage[letterpaper, margin=1in]{geometry}  
\usepackage[parfill]{parskip}  
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=black]{hyperref}
\thispagestyle{empty}
%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
%SetFonts

%SetFonts

\begin{document}
\begin{center}
  {\Large Investigation: Measuring and characterizing human reaction time}\\
  Joint SACS AAPT/NCS AAPT Fall meeting - Workshop
  November 7, 2020
\end{center}

\section*{Investigation Groups}
Everyone has been assigned to an investigation group of three or four people. Each group will
interact in a breakout session where they will collaborate on the investigation.

\section*{Guiding Question}
Do two people have the same reaction time?

\section*{Experiment}
Your task is to design and carry out a procedure to measure a person's reaction time using the
online reaction timer at
\href{https://nrich.maths.org/reactiontimer}{https://nrich.maths.org/reactiontimer} and compare
two measured values accounting for uncertainties in order to answer the guiding question.

\section*{Argumentation}
Each group will prepare a three-slide PowerPoint (PPT) presentation with their argument. The
presentation slides should be:
\begin{enumerate}
  \item Description of procedure.  What did you measure, and how did you measure it?
  \item Results. This can include a graph, a table, or a result from your measurements.
  \item Argument. Answer the guiding question. Use your results to justify your argument.
\end{enumerate}
Select a presenter from each group. The presenter will give the group's PowerPoint during the
argumentation session. The other members of the group will be responsible for contributing to
the discussion about the each groups' presentations.

\end{document}

### 2020-11-13 2020fallNCSAAPT/xlabsWorkshop.tex
Uploaded the workshop that I gave to the NCS AAPT folks about ADI/Online labs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Use for regular mode:
\documentclass[xcolor=dvipsnames,table]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Use for handout mode:
%\documentclass[handout,t]{beamer}
%\usepackage{pgfpages}
%\mode<handout>{
%  \usetheme{default}
%  \setbeamercolor{background canvas}{bg=black!5}
%  \pgfpagesuselayout{2 on 1}[letterpaper,border shrink=2.5mm]
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\pgfpagesuselayout{2 on 1}[letterpaper,border shrink=5mm]
%\pgfpagesuselayout{4 on 1}[letterpaper,border shrink=5mm]
%\pgfpagesuselayout{8 on 1}[letterpaper,border shrink=5mm]

\usetheme{Boadilla}
\usepackage{ecuPresentation}
\usepackage{hyperref}
\usepackage{siunitx}

% \AtBeginSection[]
%   {
%     \ifnum \value{framenumber}>2
%       \begin{frame}<beamer>
%       \frametitle{Outline}
%       \tableofcontents[currentsection]
%       \end{frame}
%     \else
%     \fi
%   }

\title[ADI Physics Labs]{Transforming Introductory Physics Labs (and doing them online) Using
  Argument Driven Inquiry}
\author[Steven F.\ Wolf]{Steven F.~Wolf}
\institute[\url{wolfs15@ecu.edu}]{East Carolina University Department of Physics}

\date{November 6, 2020}

\usepackage{pgfpages} % Need this to show notes.  Will fiddle with screens later
%\setbeameroption{show notes} % Inserts note slides after each slide
%\setbeameroption{show only notes}
%\setbeameroption{show notes on second screen}

\begin{document}

\begin{frame}
  \titlepage 
\end{frame}

\begin{frame}{Outline}
  Link to a guide to this workshop: \url{https://sfwolfphys.github.io/f2020ncsaapt.html}
  \tableofcontents
\end{frame}

\begin{frame}{XLABs Personnel}
  \noindent
  \begin{minipage}{0.48\textwidth}\scriptsize
    \begin{block}{Physics}
      \begin{itemize}
        \item Co-PI: Steven Wolf
        \item Mark Sprague
      \end{itemize}
    \end{block}
    \begin{block}{Chemistry}
      \begin{itemize}
        \item Project Lead: Joi Walker
        \item Rosa Bell
        \item Kate Hosbein
        \item Annalisa Smith-Joyner
        \item Eric Eaton
      \end{itemize}
    \end{block}
  \end{minipage}\hfill%
  \begin{minipage}{0.48\textwidth}\scriptsize
    \begin{block}{Biology}
      \begin{itemize}
        \item Co-PI: Heather Vance-Chalcraft
        \item Co-PI: Kristine Callis-Duehl
        \item Taria Crenshaw
      \end{itemize}
    \end{block}
    \begin{center}
      \includegraphics[width=0.5\textwidth,trim = 60 0 70 0, clip]{./logos/xlabsLogo.png}%
      \hfill\includegraphics[width=0.45\textwidth]{./logos/stemCoreLogoTall.pdf}
    \end{center}
  \end{minipage}

  \begin{minipage}{0.25\textwidth}
    \begin{center}\scriptsize
      \includegraphics[width=0.5\textwidth]{./logos/NSF_4-Color_bitmap_Logo.png}\\
      Award \# 1725655
    \end{center}
  \end{minipage}%
  \begin{minipage}{0.5\textwidth}\scriptsize
    \begin{block}{Project page:}
      \centering \url{https://bit.ly/3k3WoKf}
    \end{block}
  \end{minipage}
\end{frame}

\section{Introduction to ADI}
\begin{frame}{Science Practice Focused Lab curriculum}
  \begin{tabular}{cc}
    \includegraphics[height=0.6\textheight]{./clipart/p1251cover.pdf}
    &\includegraphics[height=0.6\textheight]{./clipart/p1261cover.pdf} \\
    Piloted Spring 2018 &Piloted Fall 2018 \\
  \end{tabular}
\end{frame}

\begin{frame}{What science practices?}
  \begin{block}{M.J.\ Ford, \textit{Science Education} \textbf{99}, 1041 (2015).}
    \begin{tabular}{lp{4in}} 
      \multicolumn{2}{c}{\textbf{Empirical practices:}} \\
      EP1 &Locate information relevant to a scientific problem.\\
      EP2 &Construct a relevant/appropriate scientific question for a given problem.\\
      EP3 &Design an experiment to test a scientific question.\\
      EP4 &Apply (or know when to apply) appropriate analytical methods to examine a
            scientific problem.\\
      EP5 &Appraise an experimental design to identify elements and limitations and how they
            impact scientific findings/conclusions.\\
      EP6 &Troubleshoot technical issues.\\
      EP7 &Evaluate evidence and critique experimental designs.\\
      EP8 &Interpret basic statistics (e.g., average and SD).\\
    \end{tabular}
  \end{block}
\end{frame}

\begin{frame}{What science practices?}
  \begin{block}{M.J.\ Ford, \textit{Science Education} \textbf{99}, 1041 (2015).}
    \begin{tabular}{lp{4in}} 
      \multicolumn{2}{c}{ \textbf{Representative practices:}} \\
      RP1 &Generate a hypothesis or make a prediction based on a scientific model. \\
      RP2 &Construct an argument based on evidence.\\
      RP3 &Identify additional information needed to support an argument.\\
      RP4 &Provide alternative explanations for results that may have many causes.\\
      RP5 &Integrate and apply knowledge across sub-disciplines.\\
      RP6 &Represent data in a visual form.\\
      RP7 &Interpret visual representations of data.\\
      RP8 &Construct a Data table.\\
      RP9 &Data Analysis.\\
    \end{tabular}
  \end{block}
\end{frame}

{\nologo
  \begin{frame}{Elements of ADI}
    \begin{block}{Week 1: Pre-Lab}
      \begin{minipage}{0.2\textwidth}
        \centering \includegraphics[width=0.9\textwidth]{./clipart/house.jpg}
      \end{minipage}\hfill
      \begin{minipage}{0.75\textwidth}
        \begin{itemize}
          \item Students work in pairs
          \item Learn a new measurement or analysis technique
          \item Traditional lab activity
        \end{itemize}
      \end{minipage}
    \end{block}
    \begin{block}{Week 2: Inquiry Investigation}
      \begin{minipage}{0.75\textwidth}
        \begin{itemize}
          \item Students work in groups of four
          \item Students are given a scientific question to answer
          \item Students design an investigation and carry it out
          \item Investigations must be approved by TA
        \end{itemize}
      \end{minipage}\hfill
      \begin{minipage}{0.2\textwidth}
        \centering \includegraphics[width=0.9\textwidth]{./clipart/gears.jpg}
      \end{minipage}
    \end{block}
  \end{frame}
}

{\nologo
  \begin{frame}{Elements of ADI}
    \begin{block}{Week 3: Argumentation Session}
      \begin{minipage}{0.2\textwidth}
        \centering \includegraphics[width=\textwidth]{./clipart/posterSession.jpg}
      \end{minipage}\hfill
      \begin{minipage}{0.75\textwidth}
        \begin{itemize}
          \item Students work in groups of four
          \item Students present the results of their experiment via a ``poster session''
          \item One presenter, three travelers
        \end{itemize}
      \end{minipage}
    \end{block}
    \begin{block}{After Week 3: Peer Review}
      \begin{minipage}{0.75\textwidth}
        \begin{itemize}
          \item Students turn in their first draft after the argumentation session
          \item We use peer review tools embedded in Canvas
          \item Students review 3 papers while watching a peer review calibration video
        \end{itemize}
      \end{minipage}\hfill
      \begin{minipage}{0.2\textwidth}
        \centering \includegraphics[width=0.9\textwidth]{./clipart/peerReview.jpg}
      \end{minipage}
    \end{block}
  \end{frame}
}

\begin{frame}{Implementation at scale}
  \onslide<1->{
    \begin{block}{Instructional Context}
      Labs serve both Calculus-based and Algebra-based physics lecture courses.
      \begin{description}
        \item[Physics 1] Typically about 400 students in approximately 25 sections managed by
        8-10 TAs.
        \item[Physics 2] Typically about 250 students in approximately 15 sections managed by
        5-6 TAs.
      \end{description}
    \end{block}
  }
  \onslide<2->{
    \begin{block}{Management strategies}
      \begin{itemize}
        \item Course is hosted on our LMS (Canvas) - All sections as one course
        \item Course is set up by lab manager (MWS) - assignments, due dates, syllabus, etc.
        \item All artifacts are turned in online
        \item TAs grade using rubrics\ldots\ calibration is important!
      \end{itemize}
    \end{block}
  }
\end{frame}

\section{Reaction Time Lab Activity}
\begin{frame}{Reaction Time Lab Activity -- Background}
  Plan:
  \begin{itemize}
    \item You will be split into groups of 2 or 3
    \item Your task: Complete the workshop activity on the workshop page
    \item I'm planning 15 minutes for this portion:
    \begin{itemize}
      \item Guidance we give students: 30 data points
      \item We also discuss mean, standard deviation, and standard error
    \end{itemize}
  \end{itemize}

  Link to workshop page:  \url{https://sfwolfphys.github.io/f2020ncsaapt.html}
\end{frame}

\section{Argumentation Session/Reflection}
\begin{frame}{Argumentation Session Instructions -- 15 min}
  Goal:
  \begin{itemize}
    \item Each group will prepare to share out briefly
    \item Want to give you a flavor of how this works in a class
  \end{itemize}
\end{frame}

\section{Online Adaptation}
{\nologo
\begin{frame}{Transition to Online Learning}
  \begin{block}{Spring 2020}
    We had about 2 weeks to plan to finish labs. Keys to success:
    \begin{itemize}
      \item Don't forget about the physics, and your learning goals.
      \item Adapt, don't change.
      \item Get a little lucky.  
    \end{itemize}
  \end{block}
  \begin{block}{Summer 2020 and beyond}
    We still wanted a hands on experience.
    \begin{itemize}
      \item Lab manuals were made available online
      \item Students purchased kits for a reasonable price
    \end{itemize}
    Post pandemic: We have DE students who struggle to take lab courses.
  \end{block}
\end{frame}

\begin{frame}{Online adaptation of ADI Elements}
  \begin{block}{Week 1a and 1b: Pre-Lab}
    \begin{minipage}{0.2\textwidth}
      \centering \includegraphics[width=0.9\textwidth]{./clipart/house.jpg}
    \end{minipage}\hfill
    \begin{minipage}{0.75\textwidth}
      \begin{itemize}
        \item TAs hold ``office hours'' at regular class time
        \item Students work asynchronously
      \end{itemize}
    \end{minipage}
  \end{block}
  \begin{block}{Week 2a: Inquiry Investigation}
    \begin{minipage}{0.75\textwidth}
      \begin{itemize}
        \item Students work in groups of four asynchronously
        \item Groups get proposals approved during regular class time
      \end{itemize}
    \end{minipage}\hfill
    \begin{minipage}{0.2\textwidth}
      \centering \includegraphics[width=0.9\textwidth]{./clipart/gears.jpg}
    \end{minipage}
  \end{block}
\end{frame}

\begin{frame}{Online adaptation of ADI Elements}
  \begin{block}{Week 2b: Argumentation Session}
    \begin{minipage}{0.2\textwidth}
      \centering \includegraphics[width=\textwidth]{./clipart/posterSession.jpg}
    \end{minipage}\hfill
    \begin{minipage}{0.75\textwidth}
      \begin{itemize}
        \item Posters are power points rather than whiteboard posters
        \item Argumentation occurs synchronously
      \end{itemize}
    \end{minipage}
  \end{block}
  \begin{block}{After Week 2b: Peer Review}
    \begin{minipage}{0.75\textwidth}
      \begin{itemize}
        \item Remains unchanged
      \end{itemize}
    \end{minipage}\hfill
    \begin{minipage}{0.2\textwidth}
      \centering \includegraphics[width=0.9\textwidth]{./clipart/peerReview.jpg}
    \end{minipage}
  \end{block}
\end{frame}
}

\begin{frame}{Physics 1 Online Investigations}
  \begin{center}\scriptsize
    \begin{tabular}{ccp{14em}}
      \hline\hline
      Investigation & Topic & Guiding Question\\
      \hline
      1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
      2 & 2-D collisions & Is the collision between two marbles elastic? \\
      3 & Periodic motion & What is the nut position for which the physical pendulum small-angle period is minimum, and what is the power-law regression equation for the period of the system? \\
      \hline\hline
    \end{tabular}
  \end{center}
  We have dropped a reaction time investigation due to our shortened semester.
\end{frame}

\begin{frame}{Physics 1 Kit contents}
  \begin{center}
    \begin{tabular}{clc}
      \hline\hline
      Quantity & Item & Investigation(s)\\
      \hline
      1 & Protractor & 1 \\
      2 & \SI{25}{mm} marble & 1, 2 \\
      1 & Tape measure with cm scale & 1, 2, 3\\
      1 & \SI{0.6}{m} threded rod & 3 \\
      1 & Eye nut & 3 \\
      3 & Nuts & 3 \\
      1 & Door hook & 3 \\
      1 & \SI{1}{m} string & 3 \\
      1 & \SI{16}{mm} marble & 2 \\
      \hline\hline
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}
  {Physics 2 Online Investigations}
  \begin{center}
    \begin{tabular}{ccp{12em}}
      \hline\hline
      Investigation & Topic & Guiding Question\\
      \hline
      1 & Current and resistance & Does a light bulb behave like a resistor? \\
      2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
      3 & Diffraction of light & Are hairs from different people the same diameter? \\
      \hline\hline
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}{Physics 2 kit contents}
  \begin{center}\scriptsize
    \begin{tabular}{clc}
      \hline\hline
      Quantity & Item & Investigation(s)\\
      \hline
      1 & \SI{100}{\ohm} resistor & 1 \\
      1 & \SI{330}{\ohm} resistor & 1 \\
      1 & \SI{100}{\ohm} potentiometer & 1 \\
      1 & E10 light bulb holder & 1 \\
      1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
      1 & Breadboard & 1, 2, 3 \\
      1 & Breadboard power supply & 1, 2, 3 \\
      1 & USB power supply cable & 1, 2, 3 \\
      1 & Jumper wire set & 1, 2 \\
      2 & Multimeters & 1, 2 \\
      1 & Mini screwdriver for multimeters & 1, 2 \\
      5 & \SI{500}{mA} fuses for multimeters & 1, 2 \\
      4 & Alligator clip leads & 1, 2 \\
      1 & \SI{1}{\mega\ohm} resistor & 2 \\
      2 & \SI{100}{\micro\farad} capacitor & 2 \\
      1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
      1 & Tape measure with cm scale & 3 \\            
      \hline\hline
    \end{tabular}
  \end{center}

\end{frame}

\begin{frame}{}
  \vfill \centerline{\Huge Thank You!}  \vfill \centerline{\Large Any Questions?}
  \vfill
  \begin{textblock*}{0.5\textwidth}(5mm,82mm) \textblockcolor{} {\scriptsize
      \url{wolfs15@ecu.edu} }
  \end{textblock*}
\end{frame}

% {\nologo
% % \begin{frame}[allowframebreaks]{References}
%   \begin{frame}{References}

%     {\scriptsize \bibliographystyle{apsrev} \bibliography{biblio} }
%   \end{frame}
% }

\end{document}

### 2020-11-17 readingDaySeminar/PICUP-ECULabs.tex
Updated a few files.  Getting the reading day seminar ready.

@@
-\documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=169,shadow=true]{beamer}
 % \usepackage{beamerthemesplit} % Activate for custom appearance
@@
 \usetheme{Boadilla}
-\usecolortheme{seahorse}
-\usefonttheme[stillsansseriflarge]{serif}
+\usepackage{ecuPresentation}
+
 \title[ECU online labs]{Transition to online labs at ECU}
@@
 
+{\nologo
 \begin{frame}
@@
 WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
-Peergrade.io & \parbox[t]{2in}{\raggedright Online peer review} & \parbox[t]{2in}{\raggedright Anonymous reviews and feedback; better than Canvas}\\
+Canvas & \parbox[t]{2in}{\raggedright Online peer review} & \parbox[t]{2in}{\raggedright Anonymous reviews and feedback}\\
 Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} & Fine-grained control\\[3ex]
@@
 \end{frame}
+}
 

### 2020-11-17 2020fallReadingDayECU/survivePivotADI.tex
Updated reading day seminar.  Ready for some review.

\documentclass[aspectratio=169,shadow=true]{beamer}
% \usepackage{beamerthemesplit} % Activate for custom appearance
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[export]{adjustbox}
\usetheme{Boadilla}
\usepackage{ecuPresentation}

\title[ECU online labs]{Transition to online labs at ECU}
\author[Sprague and Wolf]{Mark W.\ Sprague and Steven F.\ Wolf}
\institute[ECU]{East Carolina University}
\date{\today}

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

%\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  {Transition to online labs at ECU}
  \tableofcontents
\end{frame}

\section{Labs before Coronavirus}
\begin{frame}{ECU's Lab transformation grant -- XLABs (Awarded 2017)}
  \noindent
  \begin{minipage}{0.35\textwidth}\scriptsize
    \begin{block}{Team Members}
      Physics:
      \begin{itemize}
        \item Co-PI: Steven Wolf
        \item Mark Sprague
      \end{itemize}
      Chemistry:
      \begin{itemize}
        \item Project Lead: Joi Walker
        \item Rosa Bell
        \item Kate Hosbein
        \item Annalisa Smith-Joyner
        \item Eric Eaton
      \end{itemize}
      Biology:
      \begin{itemize}
        \item Co-PI: Heather Vance-Chalcraft
        \item Co-PI: Kristine Callis-Duehl
        \item Taria Crenshaw
      \end{itemize}
    \end{block}
  \end{minipage}\hfill%
  \begin{minipage}[b]{0.6\textwidth}\scriptsize
    \begin{block}{Project page:}
      \centering \url{http://blog.ecu.edu/sites/xlabs/}
    \end{block}
    \begin{center}
      \begin{tabular}{ccc}
        \includegraphics[width=0.25\textwidth]{./logos/NSF_4-Color_bitmap_Logo.png}
        &\includegraphics[width=0.3\textwidth,trim = 60 0 70 0, clip]{./logos/xlabsLogo.png}%
        &\includegraphics[width=0.25\textwidth]{./logos/stemCoreLogoTall.pdf}\\
          Award \# 1725655
      \end{tabular}
    \end{center}
  \end{minipage}

  \begin{minipage}{0.2\textwidth}
  \end{minipage}\hspace{0.4in}%
  \begin{minipage}{0.5\textwidth}%
  \end{minipage}
\end{frame}

{\nologo
\begin{frame}
  \frametitle{Physics labs at ECU in BC days}
  \begin{center}
    \only<1>{\includegraphics[page=1, height=3in, valign=m]{PICUP1.pdf}}
    \only<2>{\includegraphics[page=2, height=3in, valign=m]{PICUP1.pdf}}
    \only<3>{\includegraphics[page=3, height=3in, valign=m]{PICUP1.pdf}}
    \only<4>{\includegraphics[page=4, height=3in, valign=m]{PICUP1.pdf}}
  \end{center}
\end{frame}
}

\section{Spring 2020:  Adapt! (Don't change)}
\begin{frame}
  \frametitle{Spring 2020:  Adapt! (Don't change)}
  \begin{center}
    \includegraphics[width=2in]{coronavirus.jpg}
  \end{center}
  \begin{itemize}
    \item<1-> Preserve ADI format for last two investigations
    \item<1-> How can we change our delivery while maintaining our focus on science practices?
    \item<2-> What do we need to do together? (What requires active approval?)
    \begin{enumerate}
      \item Proposal approval
      \item Argumentation session
    \end{enumerate}
    \item<3-> What can we do apart? (What do we want students to solve on their own?)
    \begin{enumerate}
      \item Data collection (Both Prelab and Inquiry Investigation)
      \item Data analysis
      \item Peer review/lab report revision
    \end{enumerate}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Delivering Data}
  \begin{center}
    \includegraphics[width=2in]{Hair1_red_pattern.jpg}\\
    {\footnotesize Image of diffraction pattern for student measurement.}
  \end{center}
  \begin{itemize}
    \item Measurements online using photos and
    \href{https://ecu.instructuremedia.com/embed/7b72631f-ea1e-4c4d-a0bd-642c4a2d0356}{video}
    \item Simulations on \emph{Trinket}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Challenges with online labs}
  \begin{block}{Technology-based}
    Used university-supported solutions or open-source software
    \begin{itemize}
      \item Microsoft Office (Excel)
      \item Tracker
      \item ImageJ
    \end{itemize}
    Required students to install on their own machines.
    \begin{itemize}
      \item ECU Center for Survey research identified access to computers as an issue for a
      significant fraction of our students. (Nearly 2000)
      \item Not all computers are created equal. (Chromebooks were a problem)
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Challenges with online labs}
  \begin{block}{Curriculum-based}
    Argumentation sessions got quiet
    \begin{itemize}
      \item Participation in argumentation was more muted
      \item Fewer questions, less sharing ideas
    \end{itemize}
  \end{block}
\end{frame}

\section{Fall 2020 (and beyond?)}
{\nologo
\begin{frame}
  \frametitle{Fall 2020 plans (and beyond)?}
  \begin{block}{Goal:  We still wanted a hands on experience.}
    Adaptations for fully online labs:
    \begin{itemize}
      \item Lab manuals were made available online
      \item Students purchased kits for a reasonable price
      \item Activities/questions slightly changed
    \end{itemize}
    Post pandemic: We have DE students who struggle to take lab courses.
  \end{block}
  \begin{block}{Adaptations to challenges}
    \begin{itemize}
      \item Students are made aware of computing requirements/work-arounds
      \item Argumentation sessions became a participation grade
    \end{itemize}
  \end{block}
\end{frame}
}

\begin{frame}
  \frametitle{Fall 2020 plans (and beyond)}
  \begin{block}{New challenge:  8 week blocks}
    \begin{itemize}
      \item We dropped an investigation
      \item We added some pre-labs
    \end{itemize}
    This helped with grading.
  \end{block}
\end{frame}

{\nologo
  \begin{frame}
    \frametitle{Tools used in online lab delivery}
    \begin{center}
      \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{cll}
        \hline\hline
        \textbf{Tool} & \textbf{Use} & \textbf{Rationale} \\
        \hline
        Canvas & \parbox[t]{2in}{\raggedright Material, Assignments, Quizzes, Discussions,
                 Online Peer Review }& University LMS\\
        WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
        Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} &
                                                                                    Fine-grained
                                                                                    control\\
        ImageJ &Image processing software &Open-source \\
        Tracker &Video processing software &Open-source \\
        \hline\hline
      \end{tabular}
    \end{center}
  \end{frame}
}

\end{document}

### 2020-11-17 2020fallReadingDayECU/survivePivotADI.tex
Changed Trinket to Glowscript in reading day presentation.

@@
         WebEx & \parbox[t]{2in}{\raggedright Class introduction, argumentation, group interactions (???)} & University supported\\
-        Trinket.io & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} &
+        Glowscript.org & \parbox[t]{2in}{\raggedright Simulations embedded in Canvas} &
                                                                                     Fine-grained

### 2021-03-25 manuscript/onlineLabPaper.tex
Addressed reviewer comments 2 and 3 (mostly) in the MS.

@@
 students familiarity with the equipment they will be using.  For the investigation described
-previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  students must become familiar with a few things, such as what we mean by a cart and also obtain some tools to be able to answer this question.
-As a part of the pre-lab
+previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  students 
+must become familiar with a few things, such as what we mean by a cart and also obtain some 
+tools to be able to answer this question.  As a part of the pre-lab
 reading, students learn about linear regression---both how to run it in Excel,
@@
 During this session, students work in groups of 3-4 on the guiding question.  They develop a
-proposal, get it approved by a GTA, and then collect and analyze data.  Our proposal development format asks students to link the scientific concept being studied---in
+proposal, get it approved by a GTA, and then collect and analyze data.  Our proposal development 
+format asks students to link the scientific concept being studied---in
 this example case, Newton's Second Law---to the data that they will collect.  Students also
@@
 as friction).  Once students have an approved proposal, they begin collecting and analyzing
-their data.  This may lead them to refine or revise their method (which is encouraged).  Grading for the GTAs this week is minimal (students get full credit for getting their
+their data.  This may lead them to refine or revise their method (which is encouraged).  Grading 
+for the GTAs this week is minimal (students get full credit for getting their
 proposal approved).  However, this is the most critical week for GTA training.  GTAs have to be
@@
 
-After the session, each student submits a draft report consisting of three sections: an introduction to the
+After the session, each student submits a draft report consisting of three sections: an 
+introduction to the
 scientific concept, a description of the experimental method or procedure, and a discussion
-section laying out their results and the evidence and justification supporting their results by the end of the next day.
+section laying out their results and the evidence and justification supporting their results by the 
+end of the next day.
 The authors have created different peer review calibration videos for the students to watch so
 they can look for the same things that we will grade when we get their
-final reports.
-After watching the video, students take part in online, double-confidential peer reviews of two different lab reports using a simplified rubric based on the grading rubric for final drafts.
+final reports.  After watching the video, students take part in online, double-confidential peer 
+reviews of two different lab reports using a simplified rubric based on the grading rubric for final drafts.
 Finally, students use their feedback to revise their own lab reports.  At the end of
@@
 
-The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab intended to introduce students to data collection and analysis techniques, in-person
+The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab 
+intended to introduce students to data collection and analysis techniques, in-person
 activities were modified for online use by creating (or using) videos or simulated using
@@
 provided feedback or approval. Groups used the GTA feedback to revise their proposals until
-they were approved. Most proposals obtained approval after two or three revisions, but some
-required as many as seven revisions to obtain approval. When the GTA approved a group's
+they were approved. As with the prior face-to-face labs, the GTAs were looking for specific items in 
+the proposals such as what data the students planned to collect, how they would use the data to 
+answer the guiding question, what steps they would take to minimize errors, and how the students 
+would quantify their uncertainty. Most proposals obtained approval after two or three revisions, but 
+some required as many as seven revisions to obtain approval. When the GTA approved a group's
 proposal, they assigned the group a data set for the investigation, and the group began
-measurements and analysis. Based on our prior experience running the class, we prepared some
+measurements and analysis. Groups were encouraged to revise their methods during the the 
+measurement/analysis phase if the discovered a flaw or a better way to answer the guiding question. 
+Based on our prior experience running the class, we prepared some
 data sets appropriate to the different proposals that previous students had produced and
 provided measurements to the current students in the most raw form possible to require them to
-make decisions about data collection and analysis.
+make decisions about data collection and analysis. We provided six data sets for the third investigation 
+and 13 data sets for the fourth investigation for the Physics 1 laboratory. We provided seven data sets 
+for the third investigation (each group was assigned two data sets at random to compare) and 14 data 
+sets for the fourth investigation for the Physics 2 laboratory.
 
@@
 the week after the proposal session. Before this session, each group was required to complete
-its analysis and create a three-slide presentation for the argumentation session: (1) a description of their measurements, (2) a presentation of the
+its analysis and create a three-slide presentation for the argumentation session: (1) a description of 
+their measurements, (2) a presentation of the
 results, including a graph or table, and (3) their argument based on their
@@
 informed the students before the course began that internet connectivity was required and that
-they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}\citep{schrasetal12} (used in the course). We also included these statements in the course
+they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and 
+\emph{ImageJ}\citep{schrasetal12} (used in the course). We also included these statements in the course
 syllabus. Although we began the semester with the university open for socially distant
@@
 Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
-provide online for this course.  The online adaptation of the face-to-face ADI curriculum has
-changed slightly. Pre-labs are done in groups asynchronously.  Proposals are developed in
-groups during the lab period, and scheduled argumentation sessions occur via WebEx during the
-lab period.
+provide online for this course. Lab kit materials were used for each investigation. The two video 
+analysis investigations in the Physics 1 laboratory (comparing the accelerations of a marble 
+rolling up and down an incline and a marble collision in two dimensions) required the students to 
+record their own videos of marbles from their lab kits using their smartphone cameras. The image 
+analysis investigation in the 
+Physics 2 laboratory required students to cut their own slits in aluminum foil and also create mounts 
+for hairs to produce diffraction patterns with lab-kit lasers. The online adaptation of the face-to-face 
+ADI curriculum has changed slightly. Pre-labs are done in groups asynchronously.  Proposals are 
+developed in groups during the lab period, and scheduled argumentation sessions occur via 
+WebEx during the lab period.
 

### 2021-03-26 manuscript/rev1docs/response.tex
Wrote response letter with planned changes to manuscript.

\documentclass{letter}

\usepackage[top=1in,left=1.5in,right=1.5in]{geometry}

\makeatletter
\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
  \stopbreaks
  \noindent
  \ifx\@empty\fromaddress\else
  \hspace*{\longindentation}\fi
  \parbox{\indentedwidth}{\raggedright
       \ignorespaces #1\\[2\medskipamount]%
       \ifx\@empty\fromsig
           \fromname
       \else \fromsig \fi\strut}%
   \par}
\makeatother

\signature{The Authors of \textit{Introductory Physics Labs: A Tale of Two Transformations}}

\usepackage{xcolor}
\newcommand{\swsays}[1]{\textcolor{red}{SW says: #1}}

\begin{document}
\begin{letter}{Dr.\ Gary White \\ Editor: \textit{The Physics Teacher} \\ American Association
    of Physics Teachers \\ College Park, MD}

  \opening{Dear Dr.\ White and referee,}

  Thank you for your thoughtful review of our article entitled \textit{Introductory Physics
    Labs: A Tale of Two Transformations}. We have considered your review and are responding to
  your feedback in the following ways.

  \begin{description}
    \item[Institutional support for students needs] Dr.\ White wanted to know more about the
    ways that our institution attempted to support students during the pandemic.  Our office of
    student affairs developed programs and outreach to help support students such as
    disseminating CARES Act funding to students demonstrating exceptional need.  We do discuss
    academic measures taken by the university such as extending the withdrawal date, exempting
    withdrawals during the Spring 2020 and Fall 2020 semesters from the overall limit on
    withdrawals, and allowing students to be graded pass/fail after seeing their final grade
    (and having that grade not count toward their GPA).
    \item[Comparing ADI to Modeling Instruction] We've added a few sentences to the
    introduction comparing ADI to Modeling Instruction.  We also discuss ISLE (Investigative
    Science Learning Environment) as it is also a similar pedagogical approach driven by
    learning cycles.  Both Modeling and ISLE tend to be implemented in lecture courses, while
    ADI was designed to mimic the ways that scientists learn in the laboratory, and has been
    designed to be implemented in laboratory courses regardless of the approach used in
    lecture. We find it to be particularly useful in our context as students in each of our lab
    courses take two different intro physics lecture courses (algebra-based and calculus-based).
    \item[Clarity about proposals and proposal approvals] We've added a few sentences talking
    about how we generated datasets during Spring 2020 and approve proposals in general. We
    want to point out that we do allow some proposals to go forward even if they have a flaw
    once data is collected.  Students are free to revise their proposals and gather more
    data. Dealing with unexpected results can be a powerful teacher. As far as creating
    datasets goes, we tried to make these data as raw as possible, for example sharing videos
    of a object oscillating on a spring and the mass of that object rather than giving them
    mass and period data directly. \swsays{Mark, do you want to say something about how you
      chose what data to generate?}
    \item[Details about Fall 2020] For the Fall 2020 semester, all data were collected by the
    students.  This includes images and videos as appropriate, often collected with students'
    smartphones. \swsays{Mark, please fact-check the above statement.}
    \item[Details about the survey] The survey was conducted during the spring/early summer of
    2020.  Results were released to the faculty before the fall 2020 semester began.  This was
    intended to help the faculty better understand the difficulties that were impacting our
    students. The date of the survey has been added to the text in the conclusion.
  \end{description}

  Thank you for your time.

  \closing{Sincerely,}

\end{letter}

\end{document}

### 2021-03-30 manuscript/rev1docs/response.tex
Updated the manuscript including all changes indicated in the response letter.

@@
     student affairs developed programs and outreach to help support students such as
-    disseminating CARES Act funding to students demonstrating exceptional need.  We do discuss
-    academic measures taken by the university such as extending the withdrawal date, exempting
+    disseminating CARES Act funding to students demonstrating need.  We do discuss academic
+    measures taken by the university such as extending the withdrawal date, exempting
     withdrawals during the Spring 2020 and Fall 2020 semesters from the overall limit on
@@
     of a object oscillating on a spring and the mass of that object rather than giving them
-    mass and period data directly. \swsays{Mark, do you want to say something about how you
-      chose what data to generate?}
+    mass and period data directly. 
     \item[Details about Fall 2020] For the Fall 2020 semester, all data were collected by the
     students.  This includes images and videos as appropriate, often collected with students'
-    smartphones. \swsays{Mark, please fact-check the above statement.}
+    smartphones. Additional text has been added to Section \textrm{IV}.B.
     \item[Details about the survey] The survey was conducted during the spring/early summer of

### 2021-03-30 manuscript/onlineLabPaper.tex
Updated the manuscript including all changes indicated in the response letter.

@@
 (ADI)\citep{Sampson2011,Walker2011,Walker2016} pedagogical framework, which has been
-specifically designed to engage students in authentic science practices. In physics, we also
-utilized the AAPT Lab Recommendations to guide our transformation.\citep{kozminski2014aapt}
+specifically designed to engage students in authentic science practices. ADI is very much in
+the spirit of transformations such as Modeling Physics\cite{modelingBrewe2008} and the
+Investigative Science Learning Environment (ISLE) \cite{etkina2007investigative}. Oftentimes,
+both Modeling Physics and ISLE are implemented in studio-style or even lecture classrooms,
+whereas ADI is lab-focused. The common use of hybrid courses for Modeling and ISLE imply a
+shorter time scale, for example, an ISLE cycle should take place over the course of a week,
+whereas the cycles that we use in ADI take place over 4 weeks. For our institutional
+transformation of our physics labs with ADI, we also utilized the AAPT Lab Recommendations to
+inform our curricular choices.\citep{kozminski2014aapt}
 
@@
 format and quickly realized that many of the face-to-face activities had to be adapted to
-online use.  Going forward, we have further adapted what we are doing so that students can
-still participate in a hands-on laboratory experience in an online laboratory course.
+online use.  Going forward to Fall 2020 (and beyond), we have further adapted what we are doing
+so that students can still participate in a hands-on laboratory experience in an online
+laboratory course.
 
@@
 key factors for success in online learning environments, which were a barrier for many of our
-students.  Our institution's Center for Survey Research has published some findings that
-explain some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
-communication about proposals much more difficult online than in face-to-face classes.  About
-\SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
-after the transition to online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up
-to \SI{8}{\percent} of students did not have access to a computer once they left
-campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that some students in the course
-did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of
-which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices. We
-discovered \emph{jsTrack}\citep{jstrack}, an online Javascript web application for video
-analysis that runs on most computers including Chromebooks, but not mobile devices.
+students.  Our institution implemented a number of academic measures intended to support our
+students during the pandemic, including extending the withdrawal date and allowing students to
+be graded pass/fail after seeing their final grade during each of the Spring 2020 and Fall 2020
+semesters. There have also been technical supports put in place at the institution such as
+extended laptop loan programs and remote proctoring was paid for by a grant through the
+university system. Additionally, our institution's Center for Survey Research has published
+some findings in August 2020 that explain some of our observed
+issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found communication about proposals
+much more difficult online than in face-to-face classes.  About \SI{10}{\percent} to
+\SI{20}{\percent} of our students did not have reliable internet access after the transition to
+online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up to \SI{8}{\percent} of
+students did not have access to a computer once they left campus.\citep{ECUcovidSurveyRedacted}
+Additionally, we noticed that some students in the course did not have access to computers
+capable of running \emph{Tracker} or \emph{ImageJ}, both of which run on Windows, Macintosh, or
+Linux computers but not Chromebooks or mobile devices. We discovered
+\emph{jsTrack}\citep{jstrack}, an online Javascript web application for video analysis that
+runs on most computers including Chromebooks, but not mobile devices.
 

### 2021-03-30 manuscript/onlineLabPaper.tex
Squashed warnings thrown by bibtex
fixed a typo before I pushed.  Probably means that there are 2 more I can't find right now.

@@
 \setlist{nosep}
+
+\bibliographystyle{apsrev4-2}
 
@@
 whereas ADI is lab-focused. The common use of hybrid courses for Modeling and ISLE imply a
-shorter time scale, for example, an ISLE cycle should take place over the course of a week,
-whereas the cycles that we use in ADI take place over 4 weeks. For our institutional
-transformation of our physics labs with ADI, we also utilized the AAPT Lab Recommendations to
-inform our curricular choices.\citep{kozminski2014aapt}
+shorter time scale for their learning cycles, for example, an ISLE cycle often takes place over
+the course of a week, whereas the cycles that we use in ADI take place over 4 weeks. For our
+institutional transformation of our physics labs with ADI, we also utilized the AAPT Lab
+Recommendations to inform our curricular choices.\citep{kozminski2014aapt}
 

### 2021-03-30 manuscript/onlineLabPaper.tex
Revisions ... All small edits to older material.

@@
 proposal, they assigned the group a data set for the investigation, and the group began
-measurements and analysis. Groups were encouraged to revise their methods during the the 
-measurement/analysis phase if the discovered a flaw or a better way to answer the guiding question. 
+measurements and analysis. Groups were encouraged to revise their methods during the  
+measurement/analysis phase if they discovered a flaw or a better way to answer the guiding question. 
 Based on our prior experience running the class, we prepared some
@@
 Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
-provide online for this course. Lab kit materials were used for each investigation. The two video 
-analysis investigations in the Physics 1 laboratory (comparing the accelerations of a marble 
-rolling up and down an incline and a marble collision in two dimensions) required the students to 
-record their own videos of marbles from their lab kits using their smartphone cameras. The image 
-analysis investigation in the 
+provided online for this course. Lab kit materials were used for each investigation. The two video 
+analysis investigations in the Physics 1 laboratory (one comparing the accelerations of a marble 
+rolling up and down an incline and the other analyzing a marble collision in two dimensions) 
+required the students to record their own videos of marbles from their lab kits using their 
+smartphone cameras. The image analysis investigation in the 
 Physics 2 laboratory required students to cut their own slits in aluminum foil and also create mounts 
@@
 extended laptop loan programs and remote proctoring was paid for by a grant through the
-university system. Additionally, our institution's Center for Survey Research has published
+university system. Additionally, our institution's Center for Survey Research published
 some findings in August 2020 that explain some of our observed

### 2021-03-30 manuscript/rev1docs/response.tex
Manuscript updated, word doc generated, response to editor and referees crafted.  Will submit to TPT in the morning.

@@
 
-\usepackage[top=1in,left=1.5in,right=1.5in]{geometry}
+\usepackage[margin=1.25in]{geometry}
 
@@
     \item[Institutional support for students needs] Dr.\ White wanted to know more about the
-    ways that our institution attempted to support students during the pandemic.  Our office of
-    student affairs developed programs and outreach to help support students such as
-    disseminating CARES Act funding to students demonstrating need.  We do discuss academic
-    measures taken by the university such as extending the withdrawal date, exempting
+    ways that our institution attempted to support students during the pandemic.  We discuss
+    academic measures taken by the university such as extending the withdrawal date, exempting
     withdrawals during the Spring 2020 and Fall 2020 semesters from the overall limit on
@@
     \item[Comparing ADI to Modeling Instruction] We've added a few sentences to the
-    introduction comparing ADI to Modeling Instruction.  We also discuss ISLE (Investigative
-    Science Learning Environment) as it is also a similar pedagogical approach driven by
-    learning cycles.  Both Modeling and ISLE tend to be implemented in lecture courses, while
-    ADI was designed to mimic the ways that scientists learn in the laboratory, and has been
-    designed to be implemented in laboratory courses regardless of the approach used in
-    lecture. We find it to be particularly useful in our context as students in each of our lab
-    courses take two different intro physics lecture courses (algebra-based and calculus-based).
+    introduction discussing Modeling Instruction.  We also discuss ISLE (Investigative Science
+    Learning Environment) as it is also a similar pedagogical approach driven by learning
+    cycles.  Both Modeling and ISLE tend to be implemented in active/interactive lecture
+    courses, while ADI was designed to mimic the ways that scientists learn in the laboratory,
+    and has been designed to be implemented in laboratory courses regardless of the approach
+    used in lecture. We find it to be particularly useful in our context as students in each of
+    our lab courses take two different intro physics lecture courses (algebra-based and
+    calculus-based).
     \item[Clarity about proposals and proposal approvals] We've added a few sentences talking
@@
     \item[Details about the survey] The survey was conducted during the spring/early summer of
-    2020.  Results were released to the faculty before the fall 2020 semester began.  This was
+    2020.  Results were released to the faculty before the Fall 2020 semester began.  This was
     intended to help the faculty better understand the difficulties that were impacting our

### 2021-03-30 manuscript/onlineLabPaper.tex
Manuscript updated, word doc generated, response to editor and referees crafted.  Will submit to TPT in the morning.

@@
 Investigative Science Learning Environment (ISLE) \cite{etkina2007investigative}. Oftentimes,
-both Modeling Physics and ISLE are implemented in studio-style or even lecture classrooms,
-whereas ADI is lab-focused. The common use of hybrid courses for Modeling and ISLE imply a
-shorter time scale for their learning cycles, for example, an ISLE cycle often takes place over
-the course of a week, whereas the cycles that we use in ADI take place over 4 weeks. For our
-institutional transformation of our physics labs with ADI, we also utilized the AAPT Lab
-Recommendations to inform our curricular choices.\citep{kozminski2014aapt}
+both Modeling Physics and ISLE are implemented in studio-style or other active/interactive
+lecture classrooms, whereas ADI is lab-focused. The common use of hybrid courses for Modeling
+and ISLE imply a shorter time scale for their learning cycles, for example, an ISLE cycle often
+takes place over the course of a week, whereas the cycles that we use in ADI take place over 4
+weeks. For the institutional transformation of our physics labs with ADI, we also utilized the
+AAPT Lab Recommendations to inform our curricular choices.\citep{kozminski2014aapt}
 
@@
 manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
-Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
+Physics 2 kit cost \$39.00. Students paid for these kits in place of a lab manual, which we
 provided online for this course. Lab kit materials were used for each investigation. The two video 
@@
 be graded pass/fail after seeing their final grade during each of the Spring 2020 and Fall 2020
-semesters. There have also been technical supports put in place at the institution such as
-extended laptop loan programs and remote proctoring was paid for by a grant through the
-university system. Additionally, our institution's Center for Survey Research published
-some findings in August 2020 that explain some of our observed
-issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found communication about proposals
-much more difficult online than in face-to-face classes.  About \SI{10}{\percent} to
-\SI{20}{\percent} of our students did not have reliable internet access after the transition to
-online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up to \SI{8}{\percent} of
-students did not have access to a computer once they left campus.\citep{ECUcovidSurveyRedacted}
-Additionally, we noticed that some students in the course did not have access to computers
-capable of running \emph{Tracker} or \emph{ImageJ}, both of which run on Windows, Macintosh, or
-Linux computers but not Chromebooks or mobile devices. We discovered
-\emph{jsTrack}\citep{jstrack}, an online Javascript web application for video analysis that
-runs on most computers including Chromebooks, but not mobile devices.
+semesters. Other supports put in place at the institution included an extended laptop loan
+program. Also, remote proctoring was paid for by a grant through the university system. Our
+institution's Center for Survey Research published some findings in August 2020 that explain
+some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
+communication about proposals much more difficult online than in face-to-face classes.  About
+\SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
+after the transition to online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up
+to \SI{8}{\percent} of students did not have access to a computer once they left
+campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that some students in the course
+did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of
+which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices. We
+discovered \emph{jsTrack}\citep{jstrack}, an online Javascript web application for video
+analysis that runs on most computers including Chromebooks, but not mobile devices.
 

### 2021-03-30 manuscript/onlineLabPaper.tex
Revisions in Word file and in LaTeX file.

@@
 tools to be able to answer this question.  As a part of the pre-lab
-reading, students learn about linear regression---both how to run it in Excel,
+reading, students learn about linear regression---how to run it in Excel,
 how to interpret the output, and how we can estimate instantaneous velocity given position
@@
 During this session, the students share their results in a poster session.  Students finish analyzing
-their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
+their data during the prior week and prepare a ``poster'' on a whiteboard.  One person from
 the group stays at the whiteboard while the other group members (travelers) go to other groups.
-The travelers learn what other groups did, and compare to their results in a structured
-argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they
+The travelers learn what other groups did and compare to their results in a structured
+argumentation setting.  Groups spend about 3--5 minutes at a poster and rotate so that they
 see at least 3 other posters.  After the travelers return, critically, the groups spend time
@@
 some required as many as seven revisions to obtain approval. When the GTA approved a group's
-proposal, they assigned the group a data set for the investigation, and the group began
+proposal, they assigned the group a data set for the investigation and the group began
 measurements and analysis. Groups were encouraged to revise their methods during the  
@@
 determined by our practical assessments, and our department culture around laboratory course
-instruction is invigorated. Psychometric assessment of our students engagement with science
+instruction is invigorated. Psychometric assessment of our students' engagement with science
 practices is ongoing.

### 2021-03-30 manuscript/onlineLabPaper.tex
One tiny typo (inconsistent use of Glowscript/GlowScript. Updated Pandoc conversion document.

@@
 
-% Scientific truth is discovered through the practice of doing science.  \citeauthor{DBERreport}
-% state, ``Without [scientific] investigative practices, there would be no new scientific and
-% engineering knowledge.''\citep{DBERreport} Too often, our laboratory courses do not
-% meaningfully engage students in scientific practices, instead reproducing classical
-% experiments.\citep{PCAST12} This is part of a long-standing tradition of calling for authentic
-% engagement in scientific practices which pre-dates Lorentz transformations.\citep{AAAS1881}
-% Indeed, back in \citeyear{AAAS1881}, the AAAS stated our goals quite succinctly, ``[Typical
-% courses in t]he sciences\ldots are not made the means of cultivating the observing powers,
-% stimulating inquiry, exercising the judgment in weighing evidence, nor of forming independent
-% habits of thought.''\citep{AAAS1881}
+% Scientific truth is discovered through the practice of doing science.
+% \citeauthor{DBERreport} state, ``Without [scientific] investigative practices, there would be
+% no new scientific and engineering knowledge.''\citep{DBERreport} Too often, our laboratory
+% courses do not meaningfully engage students in scientific practices, instead reproducing
+% classical experiments.\citep{PCAST12} This is part of a long-standing tradition of calling
+% for authentic engagement in scientific practices which pre-dates Lorentz
+% transformations.\citep{AAAS1881} Indeed, back in \citeyear{AAAS1881}, the AAAS stated our
+% goals quite succinctly, ``[Typical courses in t]he sciences\ldots are not made the means of
+% cultivating the observing powers, stimulating inquiry, exercising the judgment in weighing
+% evidence, nor of forming independent habits of thought.''\citep{AAAS1881}
 
@@
 % Regional State University is a public doctoral granting university in a rural, economically
-% depressed part of our state.  The university mission is focused on regional transformation and
-% service to this region.  The total combined student population in Fall 2019 was 28,651 largely
-% comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and Physics
-% \textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These courses serve
-% both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of
-% the students who take our lab course are in (or have taken) the corresponding Algebra-based
-% physics lecture course. These labs also fulfill the general education requirement for science
-% lab courses at our university.
+% depressed part of our state.  The university mission is focused on regional transformation
+% and service to this region.  The total combined student population in Fall 2019 was 28,651
+% largely comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and
+% Physics \textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These
+% courses serve both of our Calculus-based and Algebra-based physics lecture courses.  Most
+% $(\sim 75\%)$ of the students who take our lab course are in (or have taken) the
+% corresponding Algebra-based physics lecture course. These labs also fulfill the general
+% education requirement for science lab courses at our university.
 
-Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The
-transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
-enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
-Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
-as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
-weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
-aspects of the transformation especially important for research such as curricular
-implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.
+Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The transformed
+curriculum was jointly written by both of the authors.  GTA training was also greatly enhanced
+when the new lab curriculum was put in place.  Both authors, along with colleagues in Biology
+and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics as these
+disciplines are all using the same curricular format for their labs.  Author 2 runs a weekly
+prep meeting with the GTAs, and Author 1 and the research team have supervised various aspects
+of the transformation especially important for research such as curricular implementation
+\citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.
 
 \section{Transformation \#1: Argument Driven Inquiry}
-Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs
-in school better match what transpires in authentic research settings
+Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs in school
+better match what transpires in authentic research settings
 \citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
@@
 and the semester ends with a practical exam where students engage in this process on a
-shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental materials
-with more details about each of the labs in our curriculum.
+shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental
+materials with more details about each of the labs in our curriculum.
 
@@
 must become familiar with a few things, such as what we mean by a cart and also obtain some
-tools to be able to answer this question.  As a part of the pre-lab
-reading, students learn about linear regression---how to run it in Excel,
-how to interpret the output, and how we can estimate instantaneous velocity given position
-vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
-them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
-collect position vs.\ time data.  Students work in pairs and submit a brief
-summary of this work on the learning management system (LMS). This investigation is the first
-time the students create graphs, so we set norms for graphing such as helping them decide which
-variable to put on the $x$-axis and the $y$-axis as well as including units.  Pre-lab assignments
-are designed to be graded in less than 1 minute/submission based on a rubric we provide to both
-students and GTAs.
+tools to be able to answer this question.  As a part of the pre-lab reading, students learn
+about linear regression---how to run it in Excel, how to interpret the output, and how we can
+estimate instantaneous velocity given position vs.\ time data. For this experiment, we give
+them a cart (leaving the fan off for now) and have them measure the acceleration of that cart
+down a ramp using an ultrasonic motion detector to collect position vs.\ time data.  Students
+work in pairs and submit a brief summary of this work on the learning management system
+(LMS). This investigation is the first time the students create graphs, so we set norms for
+graphing such as helping them decide which variable to put on the $x$-axis and the $y$-axis as
+well as including units.  Pre-lab assignments are designed to be graded in less than 1
+minute/submission based on a rubric we provide to both students and GTAs.
 
@@
 During this session, students work in groups of 3-4 on the guiding question.  They develop a
-proposal, get it approved by a GTA, and then collect and analyze data.  Our proposal development 
-format asks students to link the scientific concept being studied---in
-this example case, Newton's Second Law---to the data that they will collect.  Students also
-must propose a plan for analyzing their data and minimizing potential sources of error (such
-as friction).  Once students have an approved proposal, they begin collecting and analyzing
-their data.  This may lead them to refine or revise their method (which is encouraged).  Grading 
-for the GTAs this week is minimal (students get full credit for getting their
-proposal approved).  However, this is the most critical week for GTA training.  GTAs have to be
-clear that the goal is to allow a diverse number of ways of collecting/analyzing this
-data. This can be uncomfortable for the GTAs and students alike.  Students want ``the answer,''
-and GTAs want to provide one for them.  However, experimental methods certainly have an impact
-on experimental results. One of the goals of this curriculum is to get students to understand
-this and apply it as they develop their experimental procedures and evaluate their results.
+proposal, get it approved by a GTA, and then collect and analyze data.  Our proposal
+development format asks students to link the scientific concept being studied---in this example
+case, Newton's Second Law---to the data that they will collect.  Students also must propose a
+plan for analyzing their data and minimizing potential sources of error (such as friction).
+Once students have an approved proposal, they begin collecting and analyzing their data.  This
+may lead them to refine or revise their method (which is encouraged).  Grading for the GTAs
+this week is minimal (students get full credit for getting their proposal approved).  However,
+this is the most critical week for GTA training.  GTAs have to be clear that the goal is to
+allow a diverse number of ways of collecting/analyzing this data. This can be uncomfortable for
+the GTAs and students alike.  Students want ``the answer,'' and GTAs want to provide one for
+them.  However, experimental methods certainly have an impact on experimental results. One of
+the goals of this curriculum is to get students to understand this and apply it as they develop
+their experimental procedures and evaluate their results.
 
 \subsection{Session 3: Argumentation and Peer Review}
-During this session, the students share their results in a poster session.  Students finish analyzing
-their data during the prior week and prepare a ``poster'' on a whiteboard.  One person from
-the group stays at the whiteboard while the other group members (travelers) go to other groups.
-The travelers learn what other groups did and compare to their results in a structured
-argumentation setting.  Groups spend about 3--5 minutes at a poster and rotate so that they
-see at least 3 other posters.  After the travelers return, critically, the groups spend time
-discussing what they saw and reflecting on their own results.  What is exciting is that
-sometimes, these interactions actually drive groups to change their claims.\citep{Walker2019}
+During this session, the students share their results in a poster session.  Students finish
+analyzing their data during the prior week and prepare a ``poster'' on a whiteboard.  One
+person from the group stays at the whiteboard while the other group members (travelers) go to
+other groups.  The travelers learn what other groups did and compare to their results in a
+structured argumentation setting.  Groups spend about 3--5 minutes at a poster and rotate so
+that they see at least 3 other posters.  After the travelers return, critically, the groups
+spend time discussing what they saw and reflecting on their own results.  What is exciting is
+that sometimes, these interactions actually drive groups to change their
+claims.\citep{Walker2019}
 
 After the session, each student submits a draft report consisting of three sections: an
-introduction to the
-scientific concept, a description of the experimental method or procedure, and a discussion
-section laying out their results and the evidence and justification supporting their results by the 
-end of the next day.
-The authors have created different peer review calibration videos for the students to watch so
-they can look for the same things that we will grade when we get their
-final reports.  After watching the video, students take part in online, double-confidential peer 
-reviews of two different lab reports using a simplified rubric based on the grading rubric for final drafts.
-Finally, students use their feedback to revise their own lab reports.  At the end of
-this week, students turn in their revised, peer-reviewed final lab report.  This is the
-heaviest week of GTA grading, each lab report generally takes about 3-5 minutes to grade.
+introduction to the scientific concept, a description of the experimental method or procedure,
+and a discussion section laying out their results and the evidence and justification supporting
+their results by the end of the next day.  The authors have created different peer review
+calibration videos for the students to watch so they can look for the same things that we will
+grade when we get their final reports.  After watching the video, students take part in online,
+double-confidential peer reviews of two different lab reports using a simplified rubric based
+on the grading rubric for final drafts.  Finally, students use their feedback to revise their
+own lab reports.  At the end of this week, students turn in their revised, peer-reviewed final
+lab report.  This is the heaviest week of GTA grading, each lab report generally takes about
+3-5 minutes to grade.
 
@@
 In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all
-classes online. Our Physics 1 and 2 laboratories had completed two out of
-four full investigations and the pre-lab for the third investigation face-to-face. We were
-forced to find a way to engage students in an online format while preserving the nature of the
-ADI laboratory experience. In addition, we gave the laboratory practical exam online. We
-required student investigation groups to find a method for online collaboration in which
-everyone in the group could participate. Tools students used were the LMS (Canvas)
-communication tools, WebEx (video interaction platform licensed by our university),
-and other online communication applications not managed by the university (\emph{e.g.}, group
-chats). We have detailed the adaptations we made to the curriculum in the supplementary
-materials.  One of the principles that we used while making these adaptations is that students
-should exclusively use university-supported (Microsoft Office) or open source resources.
+classes online. Our Physics 1 and 2 laboratories had completed two out of four full
+investigations and the pre-lab for the third investigation face-to-face. We were forced to find
+a way to engage students in an online format while preserving the nature of the ADI laboratory
+experience. In addition, we gave the laboratory practical exam online. We required student
+investigation groups to find a method for online collaboration in which everyone in the group
+could participate. Tools students used were the LMS (Canvas) communication tools, WebEx (video
+interaction platform licensed by our university), and other online communication applications
+not managed by the university (\emph{e.g.}, group chats). We have detailed the adaptations we
+made to the curriculum in the supplementary materials.  One of the principles that we used
+while making these adaptations is that students should exclusively use university-supported
+(Microsoft Office) or open source resources.
 
-The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab 
-intended to introduce students to data collection and analysis techniques, in-person
+The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the
+lab intended to introduce students to data collection and analysis techniques, in-person
 activities were modified for online use by creating (or using) videos or simulated using
@@
 provided feedback or approval. Groups used the GTA feedback to revise their proposals until
-they were approved. As with the prior face-to-face labs, the GTAs were looking for specific items in 
-the proposals such as what data the students planned to collect, how they would use the data to 
-answer the guiding question, what steps they would take to minimize errors, and how the students 
-would quantify their uncertainty. Most proposals obtained approval after two or three revisions, but 
-some required as many as seven revisions to obtain approval. When the GTA approved a group's
-proposal, they assigned the group a data set for the investigation and the group began
-measurements and analysis. Groups were encouraged to revise their methods during the  
-measurement/analysis phase if they discovered a flaw or a better way to answer the guiding question. 
-Based on our prior experience running the class, we prepared some
-data sets appropriate to the different proposals that previous students had produced and
-provided measurements to the current students in the most raw form possible to require them to
-make decisions about data collection and analysis. We provided six data sets for the third investigation 
-and 13 data sets for the fourth investigation for the Physics 1 laboratory. We provided seven data sets 
-for the third investigation (each group was assigned two data sets at random to compare) and 14 data 
-sets for the fourth investigation for the Physics 2 laboratory.
+they were approved. As with the prior face-to-face labs, the GTAs were looking for specific
+items in the proposals such as what data the students planned to collect, how they would use
+the data to answer the guiding question, what steps they would take to minimize errors, and how
+the students would quantify their uncertainty. Most proposals obtained approval after two or
+three revisions, but some required as many as seven revisions to obtain approval. When the GTA
+approved a group's proposal, they assigned the group a data set for the investigation and the
+group began measurements and analysis. Groups were encouraged to revise their methods during
+the measurement/analysis phase if they discovered a flaw or a better way to answer the guiding
+question.  Based on our prior experience running the class, we prepared some data sets
+appropriate to the different proposals that previous students had produced and provided
+measurements to the current students in the most raw form possible to require them to make
+decisions about data collection and analysis. We provided six data sets for the third
+investigation and 13 data sets for the fourth investigation for the Physics 1 laboratory. We
+provided seven data sets for the third investigation (each group was assigned two data sets at
+random to compare) and 14 data sets for the fourth investigation for the Physics 2 laboratory.
 
-The argumentation session was held in a scheduled WebEx session
-the week after the proposal session. Before this session, each group was required to complete
-its analysis and create a three-slide presentation for the argumentation session: (1) a description of 
-their measurements, (2) a presentation of the
-results, including a graph or table, and (3) their argument based on their
-results.  One member of each group gave the presentation, which was followed by
-questions. Students received credit for giving presentations, asking meaningful questions, and
-responding to questions.  Following the argumentation session, students submitted individual
-draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
-manner used for the face-to-face investigations.
+The argumentation session was held in a scheduled WebEx session the week after the proposal
+session. Before this session, each group was required to complete its analysis and create a
+three-slide presentation for the argumentation session: (1) a description of their
+measurements, (2) a presentation of the results, including a graph or table, and (3) their
+argument based on their results.  One member of each group gave the presentation, which was
+followed by questions. Students received credit for giving presentations, asking meaningful
+questions, and responding to questions.  Following the argumentation session, students
+submitted individual draft reports, peer-reviewed each other's drafts, and submitted final
+reports in the same manner used for the face-to-face investigations.
 
-We administered the lab practical exams for both courses in the LMS using GlowScript simulations
-embedded in LMS assignments. Students made measurements on the simulation and used their
-results to make an argument answering a guiding question.
+We administered the lab practical exams for both courses in the LMS using Glowscript
+simulations embedded in LMS assignments. Students made measurements on the simulation and used
+their results to make an argument answering a guiding question.
 
@@
 Early on, we decided to hold our introductory physics laboratory courses online in the Fall
-2020 semester to preserve the group class interaction aspects of ADI, which would be
-difficult under social distancing requirements in place due to the
-pandemic.\citep{mclber20} Learning from some of the challenges we faced in the Spring, we
-informed the students before the course began that internet connectivity was required and that
-they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and 
-\emph{ImageJ}\citep{schrasetal12} (used in the course). We also included these statements in the course
-syllabus. Although we began the semester with the university open for socially distant
-face-to-face learning, that has since ended, and we have pivoted to online instruction only for
-our undergraduate students.
+2020 semester to preserve the group class interaction aspects of ADI, which would be difficult
+under social distancing requirements in place due to the pandemic.\citep{mclber20} Learning
+from some of the challenges we faced in the Spring, we informed the students before the course
+began that internet connectivity was required and that they must have access to a computer
+capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}\citep{schrasetal12} (used in
+the course). We also included these statements in the course syllabus. Although we began the
+semester with the university open for socially distant face-to-face learning, that has since
+ended, and we have pivoted to online instruction only for our undergraduate students.
 
@@
 the lab kit items in collaboration with our campus bookstore, and the students purchased the
-lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly from
-manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
+lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly
+from manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
 Physics 2 kit cost \$39.00. Students paid for these kits in place of a lab manual, which we
-provided online for this course. Lab kit materials were used for each investigation. The two video 
-analysis investigations in the Physics 1 laboratory (one comparing the accelerations of a marble 
-rolling up and down an incline and the other analyzing a marble collision in two dimensions) 
-required the students to record their own videos of marbles from their lab kits using their 
-smartphone cameras. The image analysis investigation in the 
-Physics 2 laboratory required students to cut their own slits in aluminum foil and also create mounts 
-for hairs to produce diffraction patterns with lab-kit lasers. The online adaptation of the face-to-face 
-ADI curriculum has changed slightly. Pre-labs are done in groups asynchronously.  Proposals are 
-developed in groups during the lab period, and scheduled argumentation sessions occur via 
-WebEx during the lab period.
+provided online for this course. Lab kit materials were used for each investigation. The two
+video analysis investigations in the Physics 1 laboratory (one comparing the accelerations of a
+marble rolling up and down an incline and the other analyzing a marble collision in two
+dimensions) required the students to record their own videos of marbles from their lab kits
+using their smartphone cameras. The image analysis investigation in the Physics 2 laboratory
+required students to cut their own slits in aluminum foil and also create mounts for hairs to
+produce diffraction patterns with lab-kit lasers. The online adaptation of the face-to-face ADI
+curriculum has changed slightly. Pre-labs are done in groups asynchronously.  Proposals are
+developed in groups during the lab period, and scheduled argumentation sessions occur via WebEx
+during the lab period.
 

### 2021-05-05 manuscript/onlineLabPaper.tex
I unmasked the manuscript and created the word doc.  Still need to tweak a few things.

@@
 
-% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
-% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
-% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
-% street, Greenville, NC 27858 USA}
+\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
+  5\textsuperscript{th} street, Greenville, NC 27858 USA}
 
-\author{First Author} \affiliation{Masked Institution}
-
-\author{Second Author} \affiliation{Masked Institution}
+\author{Mark W.\ Sprague}
+\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
+street, Greenville, NC 27858 USA}
 
@@
 
-Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The transformed
+Labs are supervised by MWS, but sections are run by Graduate TAs (GTAs). The transformed
 curriculum was jointly written by both of the authors.  GTA training was also greatly enhanced
@@
 and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics as these
-disciplines are all using the same curricular format for their labs.  Author 2 runs a weekly
-prep meeting with the GTAs, and Author 1 and the research team have supervised various aspects
-of the transformation especially important for research such as curricular implementation
-\citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.
+disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
+meeting with the GTAs, and SFW and the research team have supervised various aspects of the
+transformation especially important for research such as curricular implementation
+\citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.
 
@@
 and the semester ends with a practical exam where students engage in this process on a
-shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental
+shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental
 materials with more details about each of the labs in our curriculum.
@@
 responsibilities (\SI{42.1}{\percent}) or additional family responsibilities
-(\SI{59.0}{\percent}).\citep{ECUcovidSurveyRedacted} We removed non-participating students from
+(\SI{59.0}{\percent}).\citep{ECUcovidSurvey} We removed non-participating students from
 groups and gave them an opportunity to make up their missed work asynchronously. Less than
@@
 \begin{acknowledgments}
-  Redacted for review.% This work has been supported by the NSF (Award \# 1725655). We would
-  % also like to thank the Physics GTAs who have helped us develop
-  % resources and tutorials for students during this transition.
+  This work has been supported by the NSF (Award \# 1725655). We would
+  also like to thank the Physics GTAs who have helped us develop
+  resources and tutorials for students during this transition.
 \end{acknowledgments}

### 2021-05-05 manuscript/onlineLabPaper.tex
Missed a citation when I unmasked.  Have fixed this and re-made the word doc.

@@
 
-\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
-  5\textsuperscript{th} street, Greenville, NC 27858 USA}
+\author{Steven F.\ Wolf}
+\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th} street, Greenville, NC 27858 USA}
 
 \author{Mark W.\ Sprague}
-\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
-street, Greenville, NC 27858 USA}
+\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th} street, Greenville, NC 27858 USA}
 
@@
 institution's Center for Survey Research published some findings in August 2020 that explain
-some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
+some of our observed issues.\citep{ECUcovidSurvey} The GTAs and students found
 communication about proposals much more difficult online than in face-to-face classes.  About
 \SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
-after the transition to online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up
+after the transition to online learning in the spring.\citep{ECUcovidSurvey} Also, up
 to \SI{8}{\percent} of students did not have access to a computer once they left
-campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that some students in the course
+campus.\citep{ECUcovidSurvey} Additionally, we noticed that some students in the course
 did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of

### 2022-04-13 supplement/supplement.tex
Unmasked the supplement for the TPT article.

@@
 
-% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
-% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
-% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
-% street, Greenville, NC 27858 USA}
+\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
+  5\textsuperscript{th} street, Greenville, NC 27858 USA}
 
-\author{First Author} \affiliation{Masked Institution}
+\author{Mark W.\ Sprague} \affiliation{East Carolina University Department of Physics 1000 E.\
+  5\textsuperscript{th} street, Greenville, NC 27858 USA}
 
-\author{Second Author} \affiliation{Masked Institution}
+% \author{First Author} \affiliation{Masked Institution}
+
+% \author{Second Author} \affiliation{Masked Institution}
 
@@
 aspects of the transformation especially important for research such as curricular
-implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.
+implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.
 
